---
title: "Sexual identity and mental health outcomes among adolescents and young adults in Stockholm County, pooled sample"
author: Willi Zhang
email: willi.zhang@ki.se
output: html_notebook
editor_options: 
  chunk_output_type: console
---

### 1. Load Packages
```{r}
library(haven)
library(tidyverse)
library(finalfit)
library(lubridate)
library(ggalluvial)
library(ggrepel)
library(ggbreak)
library(lemon)
library(scales)
library(naniar)
library(survey)
library(jomo)
library(mitml)
library(mitools)
library(UpSetR)
library(here)
source('helper_functions.R') # helper function
```

### 2. The Stockholm Public Health Cohort, 2002-2021
#### 2.1. Prepare datasets
```{r}
variable_list <- c( "lopnr", "sexual_identity_2010", "sexual_identity_2014", "sexual_identity_2021", "birth_year", "sex", "country_of_birth" )

### SPHC-B 2002 ### 

d_2002 <- read_sas("/Volumes/projects/LGBT Project data/sphc02_07_10_14_21.sas7bdat")

summary( d_2002$lopnr ) # 7,411 missing

# sexual identity in 2010
table( d_2002$F10F103, useNA = "always" )
d_2002$F10F103[ d_2002$F10F103 == 9 ] <- NA
d_2002$sexual_identity_2010 <- factor( ifelse( d_2002$F10F103 == 1, "Heterosexual",
                                                  ifelse( d_2002$F10F103 == 2, "Homosexual",
                                                          ifelse( d_2002$F10F103 == 3, "Bisexual", "Other" ) ) ),
                                          levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other" ) )
table( d_2002$sexual_identity_2010, useNA = "always" )

# sexual identity in 2014
table( d_2002$F14F103, useNA = "always" )
d_2002$sexual_identity_2014 <- factor( ifelse( d_2002$F14F103 == 1, "Heterosexual",
                                                  ifelse( d_2002$F14F103 == 2, "Homosexual",
                                                          ifelse( d_2002$F14F103 == 3, "Bisexual", "Other" ) ) ),
                                          levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other" ) )
table( d_2002$sexual_identity_2014, useNA = "always" )

# sexual identity in 2021
table( d_2002$F21F91, useNA = "always" )
d_2002$sexual_identity_2021 <- factor( ifelse( d_2002$F21F91 == 1, "Heterosexual",
                                                  ifelse( d_2002$F21F91 == 2, "Homosexual",
                                                          ifelse( d_2002$F21F91 == 3, "Bisexual", "Other" ) ) ),
                                          levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other" ) )
table( d_2002$sexual_identity_2021, useNA = "always" )

# birth year
summary( d_2002$F2alder )
d_2002$birth_year <- 2002 - d_2002$F2alder
summary( d_2002$birth_year )

# sex
table( d_2002$kon, useNA = "always" )
d_2002$sex <- factor( ifelse( d_2002$kon == 1, "Male", "Female" ),
                      levels = c( "Male", "Female" ) )
table( d_2002$sex, useNA = "always" )

# country of birth
table( d_2002$fodelseland, useNA = "always" )
d_2002$fodelseland[ d_2002$fodelseland == "" ] <- NA
d_2002$country_of_birth <- factor( ifelse( d_2002$fodelseland == "Sverige", "Sweden",
                                           ifelse( d_2002$fodelseland == "Europa", "Europe", "Outside Europe" ) ),
                                   levels = c( "Sweden", "Europe", "Outside Europe" ) )
table( d_2002$country_of_birth, useNA = "always" )

d_2002 <- d_2002 %>% 
  filter( !is.na( lopnr) ) # 7,411 in SPHC-B 2002 did not participate in follow-up surveys and therefore excluded

summary( d_2002 %>% select( all_of( variable_list ) ) )


### SPHC-B 2006 ###

d_2006 <- read_sas("/Volumes/projects/LGBT Project data/sphc06_10_14_21.sas7bdat")

summary( d_2006$lopnr )

# sexual identity in 2010
table( d_2006$F10F103, useNA = "always" )
d_2006$F10F103[ d_2006$F10F103 == 9 ] <- NA
d_2006$sexual_identity_2010 <- factor( ifelse( d_2006$F10F103 == 1, "Heterosexual",
                                                  ifelse( d_2006$F10F103 == 2, "Homosexual",
                                                          ifelse( d_2006$F10F103 == 3, "Bisexual", "Other" ) ) ),
                                          levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other" ) )
table( d_2006$sexual_identity_2010, useNA = "always" )

# sexual identity in 2014
table( d_2006$F14F103, useNA = "always" )
d_2006$sexual_identity_2014 <- factor( ifelse( d_2006$F14F103 == 1, "Heterosexual",
                                                  ifelse( d_2006$F14F103 == 2, "Homosexual",
                                                          ifelse( d_2006$F14F103 == 3, "Bisexual", "Other" ) ) ),
                                          levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other" ) )
table( d_2006$sexual_identity_2014, useNA = "always" )

# sexual identity in 2021
table( d_2006$F21F91, useNA = "always" )
d_2006$sexual_identity_2021 <- factor( ifelse( d_2006$F21F91 == 1, "Heterosexual",
                                                  ifelse( d_2006$F21F91 == 2, "Homosexual",
                                                          ifelse( d_2006$F21F91 == 3, "Bisexual", "Other" ) ) ),
                                          levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other" ) )
table( d_2006$sexual_identity_2021, useNA = "always" )

# birth year
summary( d_2006$F6alder )
d_2006$birth_year <- 2006 - d_2006$F6alder
summary( d_2006$birth_year )

# sex
table( d_2006$kon, useNA = "always" )
d_2006$sex <- factor( ifelse( d_2006$kon == 1, "Male", "Female" ),
                      levels = c( "Male", "Female" ) )
table( d_2006$sex, useNA = "always" )

# country of birth
table( d_2006$fodelseland, useNA = "always" )
d_2006$country_of_birth <- factor( ifelse( d_2006$fodelseland == "Sverige", "Sweden",
                                           ifelse( d_2006$fodelseland == "Europa", "Europe", "Outside Europe" ) ),
                                   levels = c( "Sweden", "Europe", "Outside Europe" ) )
table( d_2006$country_of_birth, useNA = "always" )

summary( d_2006 %>% select( all_of( variable_list ) ) )


### SPHC-B 2010 ###

d_2010 <- read_sas('/Volumes/projects/LGBT Project data/sphc10_14_21_updated.sas7bdat')

summary( d_2010$lopnr )

# sexual identity in 2010
table( d_2010$F10U87G78, useNA = "always" )
d_2010$F10U87G78[ d_2010$F10U87G78 == 9 ] <- NA
d_2010$sexual_identity_2010 <- factor( ifelse( d_2010$F10U87G78 == 1, "Heterosexual",
                                                  ifelse( d_2010$F10U87G78 == 2, "Homosexual",
                                                          ifelse( d_2010$F10U87G78 == 3, "Bisexual", "Other" ) ) ),
                                          levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other" ) )
table( d_2010$sexual_identity_2010, useNA = "always" )

# sexual identity in 2014
table( d_2010$F14F103, useNA = "always" )
d_2010$sexual_identity_2014 <- factor( ifelse( d_2010$F14F103 == 1, "Heterosexual",
                                                  ifelse( d_2010$F14F103 == 2, "Homosexual",
                                                          ifelse( d_2010$F14F103 == 3, "Bisexual", "Other" ) ) ),
                                          levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other" ) )
table( d_2010$sexual_identity_2014, useNA = "always" )

# sexual identity in 2021
table( d_2010$F21F91, useNA = "always" )
d_2010$sexual_identity_2021 <- factor( ifelse( d_2010$F21F91 == 1, "Heterosexual",
                                                  ifelse( d_2010$F21F91 == 2, "Homosexual",
                                                          ifelse( d_2010$F21F91 == 3, "Bisexual", "Other" ) ) ),
                                          levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other" ) )
table( d_2010$sexual_identity_2021, useNA = "always" )

# birth year
summary( d_2010$F10alder )
d_2010$birth_year <- 2010 - d_2010$F10alder
summary( d_2010$birth_year )

# sex
table( d_2010$kon, useNA = "always" )
d_2010$sex <- factor( ifelse( d_2010$kon == 1, "Male", "Female" ),
                      levels = c( "Male", "Female" ) )
table( d_2010$sex, useNA = "always" )

# country of birth
table( d_2010$fodelseland, useNA = "always" )
d_2010$country_of_birth <- factor( ifelse( d_2010$fodelseland == "Sverige", "Sweden",
                                           ifelse( d_2010$fodelseland == "Europa", "Europe", "Outside Europe" ) ),
                                   levels = c( "Sweden", "Europe", "Outside Europe" ) )
table( d_2010$country_of_birth, useNA = "always" )

summary( d_2010 %>% select( all_of( variable_list ) ) )


### SPHC-B 2014 ###

load("/Volumes/projects/LGBT Project data/d_2014.RData")

summary( d_2014$lopnr )

# sexual identity in 2014
table( d_2014$F14U90G82, useNA = "always" )
d_2014$sexual_identity_2014 <- factor( ifelse( d_2014$F14U90G82 == 1, "Heterosexual",
                                                  ifelse( d_2014$F14U90G82 == 2, "Homosexual",
                                                          ifelse( d_2014$F14U90G82 == 3, "Bisexual", "Other" ) ) ),
                                          levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other" ) )
table( d_2014$sexual_identity_2014, useNA = "always" )

# sexual identity in 2021
table( d_2014$F21F91, useNA = "always" )
d_2014$sexual_identity_2021 <- factor( ifelse( d_2014$F21F91 == 1, "Heterosexual",
                                                  ifelse( d_2014$F21F91 == 2, "Homosexual",
                                                          ifelse( d_2014$F21F91 == 3, "Bisexual", "Other" ) ) ),
                                          levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other" ) )
table( d_2014$sexual_identity_2021, useNA = "always" )

# birth year
summary( d_2014$F14alder )
d_2014$birth_year <- 2014 - d_2014$F14alder
summary( d_2014$birth_year )

# sex
table( d_2014$kon, useNA = "always" )
d_2014$sex <- factor( ifelse( d_2014$kon == 1, "Male", "Female" ),
                      levels = c( "Male", "Female" ) )
table( d_2014$sex, useNA = "always" )

# country of birth
table( d_2014$fodelseland, useNA = "always" )
d_2014$country_of_birth <- factor( ifelse( d_2014$fodelseland == "Sverige", "Sweden",
                                           ifelse( d_2014$fodelseland == "Europa", "Europe", "Outside Europe" ) ),
                                   levels = c( "Sweden", "Europe", "Outside Europe" ) )
table( d_2014$country_of_birth, useNA = "always" )

summary( d_2014 %>% select( any_of( variable_list ) ) )


### SPHC-B 2021 ###

load("/Volumes/projects/LGBT Project data/d_2021.RData")

d_2021 <- d_2021 %>%
  rename( lopnr = lopnr2 ) %>%
  mutate( lopnr = lopnr + 600000 )
summary( d_2021$lopnr )

# sexual identity in 2021
table( d_2021$F21F45_Q57, useNA = "always" )
d_2021$sexual_identity_2021 <- factor( ifelse( d_2021$F21F45_Q57 == 1, "Heterosexual", 
                                          ifelse( d_2021$F21F45_Q57 == 2, "Homosexual",
                                                  ifelse( d_2021$F21F45_Q57 == 3, "Bisexual", "Other" ) ) ),
                                  levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other" ) )
table( d_2021$sexual_identity_2021, useNA = "always" )

# birth year
summary( d_2021$F21alder )
d_2021$birth_year <- 2021 - d_2021$F21alder
summary( d_2021$birth_year )

# sex
table( d_2021$kon, useNA = "always" )
d_2021$sex <- factor( ifelse( d_2021$kon == 1, "Male", "Female" ), 
                      levels = c( "Male", "Female" ) )
table( d_2021$sex, useNA = "always" )

# country of birth
table( d_2021$fodelseland, useNA = "always" )
d_2021$country_of_birth <- factor( ifelse( d_2021$fodelseland == "Sverige", "Sweden",
                                           ifelse( d_2021$fodelseland == "Europa", "Europe", "Outside Europe" ) ),
                                   levels = c( "Sweden", "Europe", "Outside Europe" ) )
table( d_2021$country_of_birth, useNA = "always" )

summary( d_2021 %>% select( any_of( variable_list ) ) )


### CLEAN DATA ###

# SPHC 2002 to 2014
d_2002_selected <- d_2002 %>%
  select( any_of( variable_list ) ) %>%
  mutate( survey_year = "SPHC 2002" )

d_2006_selected <- d_2006 %>%
  select( any_of( variable_list ) ) %>%
  mutate( survey_year = "SPHC 2006" )

d_2010_selected <- d_2010 %>%
  select( any_of( variable_list ) ) %>%
  mutate( survey_year = "SPHC 2010" )

d_2014_selected <- d_2014 %>%
  select( any_of( variable_list ) ) %>%
  mutate( survey_year = "SPHC 2014" )

pre2021 <- bind_rows(
  d_2002_selected,
  d_2006_selected,
  d_2010_selected,
  d_2014_selected ) %>%
  mutate( survey_year = as.factor( survey_year ) )

summary( pre2021 )

# check for overlapping participants across SPHC-B 2002 to 2014
# unable to check for SPHC-B 2021, because of its independent lopnr number system
length( intersect( d_2002_selected$lopnr, d_2006_selected$lopnr ) ) # 999 individuals participated in both SPHC-B 2002 and 2006
length( intersect( d_2002_selected$lopnr, d_2010_selected$lopnr ) ) # 0
length( intersect( d_2002_selected$lopnr, d_2014_selected$lopnr ) ) # 62
length( intersect( d_2006_selected$lopnr, d_2010_selected$lopnr ) ) # 0
length( intersect( d_2006_selected$lopnr, d_2014_selected$lopnr ) ) # 83
length( intersect( d_2010_selected$lopnr, d_2014_selected$lopnr ) ) # 0
length( Reduce( intersect, list( d_2002_selected$lopnr, d_2006_selected$lopnr, d_2014_selected$lopnr ) ) ) # two individuals participated in SPHC-B 2002, 2006, and 2014

sum( duplicated( pre2021$lopnr ) ) # 1,142 duplicates in total
id_with_overlap <- pre2021 %>% count( lopnr ) %>% filter( n > 1 ) %>% pull( lopnr )
levels( pre2021$survey_year )

# pre2021 %>%
#   group_by( lopnr ) %>%
#   filter( n() > 1 ) %>%
#   mutate( row_count = n() ) %>%
#   ungroup() %>%
#   arrange( desc( row_count ), lopnr ) %>%
#   View()

non_matching_lopnr <- pre2021 %>%
  select( -survey_year ) %>%
  group_by( lopnr ) %>%
  filter( n() > 1 ) %>%
  filter( n_distinct( across( everything() ) ) > 1 ) %>%
  ungroup() %>%
  distinct( lopnr ) %>%
  pull()

pre2021_diff <- pre2021 %>%
  filter( lopnr %in% non_matching_lopnr ) %>%
  group_by( lopnr ) %>%
  mutate( row_count = n() ) %>%
  ungroup() %>%
  arrange( desc( row_count ), lopnr, survey_year )

# View( pre2021_diff )

pre2021_selected <- pre2021 %>%
  arrange( lopnr, survey_year ) %>%
  group_by( lopnr ) %>%
  slice_tail( n = 1 ) %>% # remove duplicates and retain data for the latest year
  ungroup()

sum( duplicated( pre2021_selected$lopnr ) ) # 0
nrow( pre2021_selected ) # 110,353
summary( pre2021_selected )

# define variables
pre2021_selected <- pre2021_selected %>%
  mutate(
    
    # sexual identity
    sexual_identity_baseline = case_when(
      survey_year %in% c( "SPHC 2002", "SPHC 2006", "SPHC 2010" ) ~ sexual_identity_2010,
      survey_year == "SPHC 2014" ~ sexual_identity_2014 ),
    
    # generation
    generation = factor(
      case_when(
        birth_year >= 1997 & birth_year <= 2012 ~ "Generation Z (1997–2012)",
        birth_year >= 1981 & birth_year <= 1996 ~ "Millennials (1981–1996)",
        birth_year >= 1965 & birth_year <= 1980 ~ "Generation X (1965–1980)",
        birth_year >= 1946 & birth_year <= 1964 ~ "Baby Boomers (1946–1964)",
        birth_year >= 1928 & birth_year <= 1945 ~ "Silent Generation (1928–1945)",
        birth_year >= 1901 & birth_year <= 1927 ~ "Greatest Generation (1901–1927)" ),
      levels = c( "Generation Z (1997–2012)", "Millennials (1981–1996)", "Generation X (1965–1980)", "Baby Boomers (1946–1964)", "Silent Generation (1928–1945)", "Greatest Generation (1901–1927)" ) ) 
    )

table( pre2021_selected$survey_year, pre2021_selected$sexual_identity_baseline, useNA = "always" )
summary( pre2021_selected )

# SPHC 2021
d_2021_selected <- d_2021 %>%
  select( any_of( variable_list ) ) %>%
  mutate( 
    
    sexual_identity_baseline = sexual_identity_2021,
    
    survey_year = "SPHC 2021",
          
    # generation
    generation = factor(
      case_when(
        birth_year >= 1997 & birth_year <= 2012 ~ "Generation Z (1997–2012)",
        birth_year >= 1981 & birth_year <= 1996 ~ "Millennials (1981–1996)",
        birth_year >= 1965 & birth_year <= 1980 ~ "Generation X (1965–1980)",
        birth_year >= 1946 & birth_year <= 1964 ~ "Baby Boomers (1946–1964)",
        birth_year >= 1928 & birth_year <= 1945 ~ "Silent Generation (1928–1945)",
        birth_year >= 1901 & birth_year <= 1927 ~ "Greatest Generation (1901–1927)" ), 
      levels = c( "Generation Z (1997–2012)", "Millennials (1981–1996)", "Generation X (1965–1980)", "Baby Boomers (1946–1964)", "Silent Generation (1928–1945)", "Greatest Generation (1901–1927)" ) ) 
    )

summary( d_2021_selected )
sum( duplicated( d_2021_selected$lopnr ) ) # 0
table( d_2021_selected$sexual_identity_baseline, useNA = "always" )
nrow( d_2021_selected ) # 23,066

# merge cohorts
d_all_selected <- bind_rows( pre2021_selected, d_2021_selected ) %>%
  mutate( survey_year = as.factor( survey_year ),
          age_2005 = 2005 - birth_year )
summary( d_all_selected )
sum( duplicated( d_all_selected$lopnr ) ) # 0
nrow( d_all_selected ) # 133,419
```

#### 2.2. Birth year distribution
```{r}
# the overall pooled cohort
# include those with missing sexual identity data
# include those who reported other sexual identity

p_birth_year <- 
  ggplot( d_all_selected, aes( x = "", y = birth_year ) ) +
  geom_violin( fill = "#69b3a2", trim = TRUE ) +
  scale_y_continuous(
    name = "Birth Year",
    breaks = c( 2005, 1995, 1985, 1975, 1965, 1955, 1945, 1935, 1925, 1915, 1905 ) ) +
  scale_x_discrete( position = "top" ) +
  labs( x = paste0( "N = ", format( nrow( d_all_selected ), big.mark = "," ) ) ) +
  theme_classic() +
  theme( axis.ticks.x = element_blank(),
         axis.line.x = element_blank(),
         axis.line.y = element_blank(),
         axis.text = element_text( family = "Arial", size = 11 ),
         axis.title = element_text( family = "Arial", size = 11 ) )

p_birth_year
ggsave( "results_output/plots_general/birth_year_distribution.svg", plot = p_birth_year, width = 7, height = 8 )


p_birth_year_by_survey_year <- 
  ggplot( d_all_selected %>% 
            group_by( survey_year ) %>% 
            mutate( survey_label = paste0( survey_year, "\n(N = ", format( n(), big.mark = "," ), ")" ) ) %>% 
            ungroup(),
  aes( x = survey_label, y = birth_year, fill = survey_label ) ) +
  geom_violin( scale = "count", trim = TRUE ) +
  scale_y_continuous(
    name = "Birth Year",
    breaks = c( 2005, 1995, 1985, 1975, 1965, 1955, 1945, 1935, 1925, 1915, 1905 ) ) +
  labs( x = NULL ) +
  coord_flip() +
  theme_classic() +
  theme( axis.text = element_text( family = "Arial", size = 11 ),
         axis.title = element_text( family = "Arial", size = 11 ),
         legend.position = "none" )

p_birth_year_by_survey_year
ggsave( "results_output/plots_general/birth_year_distribution_by_year.svg", plot = p_birth_year_by_survey_year, width = 9, height = 7 )
```

#### 2.3. Follow-up period through registry
```{r}
### SPHC 2002 to 2014 ###

# migration dates
migration_date_2002_2014 <- read_sas('/Volumes/projects/LGBT Project data/Swedish Registers/migration_all_2002_2014.sas7bdat')
summary( migration_date_2002_2014 )
table( migration_date_2002_2014$Posttyp, useNA = "always" )

migration_date_2002_2014 <- migration_date_2002_2014 %>%
  rename( date = migrationdate, event_type = Posttyp ) %>%
  mutate( event_type = as.factor( recode( event_type,
                                          "Inv" = "move-in",
                                          "Utv" = "move-out" ) ) )
summary( migration_date_2002_2014 )
length( unique( migration_date_2002_2014$lopnr ) ) # 12,409 had any moving-in and/or moving-out between 1990 and 2021
length( intersect( unique( migration_date_2002_2014$lopnr ), d_all_selected$lopnr ) ) # 12,409

# death dates
date_2002_2014 <- read_sas('/Volumes/projects/LGBT Project data/Swedish Registers/dates_2002_2014.sas7bdat')
summary( date_2002_2014 )
length( unique( date_2002_2014$lopnr ) ) # 15,117
length( unique( date_2002_2014$lopnr ) ) == nrow( date_2002_2014 ) # TRUE
length( intersect( unique( date_2002_2014$lopnr ), d_all_selected$lopnr ) ) # 15,117

date_2002_2014 %>%
  filter( death_date != "" ) %>%
  mutate( lengths = nchar( death_date ) ) %>%
  count( lengths )

death_date_2002_2014 <- date_2002_2014 %>%
  select( "lopnr", "death_date" ) %>%
  filter( death_date != "" ) %>%
  mutate( death_date = as.Date( death_date, format = "%Y%m%d" ),
          event_type = "death" ) %>%
  rename( date = death_date )

summary( death_date_2002_2014 )
length( unique( death_date_2002_2014$lopnr ) ) # 8,614
length( unique( death_date_2002_2014$lopnr ) ) == nrow( death_date_2002_2014 ) # TRUE
length( intersect( unique( death_date_2002_2014$lopnr ), d_all_selected$lopnr ) ) # 8,614

# merge dates
dates_all_2002_2014 <- bind_rows( migration_date_2002_2014, death_date_2002_2014 ) %>%
  mutate( event_type = factor( event_type, levels = c( "move-in", "move-out", "death" ) ) ) %>%
  arrange( lopnr, date )
summary( dates_all_2002_2014 )
length( unique( dates_all_2002_2014$lopnr ) ) # 20,831
length( intersect( unique( dates_all_2002_2014$lopnr ), d_all_selected$lopnr ) ) # 20,831


### SPHC 2021 ###

# migration dates
migration_date_2021 <- read_sas('/Volumes/projects/LGBT Project data/Swedish Registers/migration_all_2021.sas7bdat') %>%
  rename( lopnr = lopnr2 ) %>%
  mutate( lopnr = lopnr + 600000 )
summary( migration_date_2021 )
table( migration_date_2021$Posttyp, useNA = "always" )

migration_date_2021 <- migration_date_2021 %>%
  rename( date = migrationdate, event_type = Posttyp ) %>%
  mutate( event_type = as.factor( recode( event_type,
                                          "Inv" = "move-in",
                                          "Utv" = "move-out" ) ) )
summary( migration_date_2021 )
length( unique( migration_date_2021$lopnr ) ) # 4,313 had any moving-in and/or moving-out between 1990 and 2021
length( intersect( unique( migration_date_2021$lopnr ), d_all_selected$lopnr ) ) # 4,313

# death dates
date_2021 <- read_sas('/Volumes/projects/LGBT Project data/Swedish Registers/dates_2021.sas7bdat') %>%
  rename( lopnr = lopnr2 ) %>%
  mutate( lopnr = lopnr + 600000 )
summary( date_2021 )
length( unique( date_2021$lopnr ) ) # 14
length( unique( date_2021$lopnr ) ) == nrow( date_2021 ) # TRUE
length( intersect( unique( date_2021$lopnr ), d_all_selected$lopnr ) ) # 14

date_2021 %>%
  filter( death_date != "" ) %>%
  mutate( lengths = nchar( death_date ) ) %>%
  count( lengths )

death_date_2021 <- date_2021 %>%
  select( "lopnr", "death_date" ) %>%
  filter( death_date != "" ) %>%
  mutate( death_date = as.Date( death_date, format = "%Y%m%d" ),
          event_type = "death" ) %>%
  rename( date = death_date )

summary( death_date_2021 )
length( unique( death_date_2021$lopnr ) ) # 14
length( unique( death_date_2021$lopnr ) ) == nrow( death_date_2021 ) # TRUE
length( intersect( unique( death_date_2021$lopnr ), d_all_selected$lopnr ) ) # 14

# merge dates
dates_all_2021 <- bind_rows( migration_date_2021, death_date_2021 ) %>%
  mutate( event_type = factor( event_type, levels = c( "move-in", "move-out", "death" ) ) ) %>%
  arrange( lopnr, date )
summary( dates_all_2021 )
length( unique( dates_all_2021$lopnr ) ) # 4,327
length( intersect( unique( dates_all_2021$lopnr ), d_all_selected$lopnr ) ) # 4,327


### CHECK DATES ###

dates_all <- bind_rows( dates_all_2002_2014, dates_all_2021 )
summary( dates_all )
nrow( dates_all ) # 33,039
length( unique( dates_all$lopnr ) ) # 25,158
length( intersect( d_all_selected$lopnr, unique( dates_all$lopnr ) ) ) # 25,158

# check if there are duplicate events
id_with_duplicate_events <- dates_all %>%
  arrange( lopnr, date ) %>%
  group_by( lopnr ) %>%
  filter( event_type == lead( event_type ) ) %>%
  pull( lopnr ) %>%
  unique() # 7

#View(
#  dates_all %>%
#  filter( lopnr %in% id_with_duplicate_events ) %>%
#  left_join( d_all_selected %>% select( lopnr, survey_year ),
#             by = "lopnr" ) %>%
#  arrange( lopnr, date )
#  )

dates_with_dups <- dates_all %>%
  filter( lopnr %in% id_with_duplicate_events ) %>%
  arrange( lopnr, date ) %>%
  group_by( lopnr ) %>%
  filter(
    # keep first of repeated "move-in"
    ( event_type == "move-in" & ( event_type != lag( event_type ) | is.na( lag( event_type ) ) ) ) |
    
    # keep last of repeated "move-out"
    ( event_type == "move-out" & ( event_type != lead( event_type ) | is.na( lead( event_type ) ) ) ) ) %>%
  ungroup()

dates_all <- dates_all %>%
  filter( !lopnr %in% id_with_duplicate_events ) %>%
  bind_rows( dates_with_dups ) %>%
  arrange( lopnr, date )

# check if death appears more than once
dates_all %>%
  filter( event_type == "death" ) %>%
  count( lopnr ) %>%
  filter( n > 1 ) # 0

# check if there is move-out before death
id_move_out_before_death <- dates_all %>%
  arrange( lopnr, date ) %>%
  group_by( lopnr ) %>%
  mutate( prev_event = lag( event_type ) ) %>%
  filter( event_type == "death" & prev_event == "move-out" ) %>%
  pull( lopnr ) %>%
  unique() # 2

#View(
#  dates_all %>%
#  filter( lopnr %in% id_move_out_before_death ) %>%
#  left_join( d_all_selected %>% select( lopnr, survey_year ),
#             by = "lopnr" ) %>%
#  arrange( lopnr, date ) 
#  )

dates_all <- dates_all %>%
  filter( !( lopnr %in% id_move_out_before_death & event_type == "move-out" ) ) # exclude two move-out events

# check if there is any event after death
id_with_death <- dates_all %>%
  filter( event_type == "death" ) %>%
  pull( lopnr )

dates_all %>%
  filter( lopnr %in% id_with_death ) %>%
  arrange( lopnr, date ) %>%
  group_by( lopnr ) %>%
  mutate( aft_event = lead( event_type ) ) %>%
  filter( event_type == "death" & !is.na( aft_event ) ) %>%
  ungroup() # 0

# check for duplicate id-event-date combinations
dates_all %>%
  count( lopnr, event_type, date ) %>%
  filter( n > 1 ) # 0

# check for reused personal number
reusedpnr_2002_2014 <- read_sas('/Volumes/projects/LGBT Project data/Swedish Registers/reusedpnr_2002_2014.sas7bdat')
reusedpnr_2021 <- read_sas('/Volumes/projects/LGBT Project data/Swedish Registers/reusedpnr_2021.sas7bdat') %>%
  rename( lopnr = lopnr2 ) %>%
  mutate( lopnr = lopnr + 600000 )

reusedpnr_all <- bind_rows( reusedpnr_2002_2014, reusedpnr_2021 )
nrow( reusedpnr_all ) # 130 reused personal numbers
length( unique( reusedpnr_all$lopnr ) )
length( intersect( reusedpnr_all$lopnr, d_all_selected$lopnr ) )

intersect( reusedpnr_all$lopnr, id_with_duplicate_events ) # 0
intersect( reusedpnr_all$lopnr, id_with_death ) # 0
intersect( reusedpnr_all$lopnr, id_move_out_before_death ) # 0

reusedpnr_all_dates <- reusedpnr_all %>%
  left_join( dates_all, by = "lopnr" ) %>%
  left_join( d_all_selected %>%
               select( lopnr, survey_year, birth_year, country_of_birth ),
             by = "lopnr" ) %>%
  mutate( event_age = year( date ) - birth_year,
          baseline_year = str_extract( survey_year, "\\d{4}" ) %>% as.numeric(),
          baseline_age = baseline_year - birth_year,
          age_2006 = 2006 - birth_year ) %>%
  arrange( country_of_birth, survey_year, lopnr, date )

nrow( reusedpnr_all_dates ) # 144
length( unique( reusedpnr_all_dates$lopnr ) ) == length( reusedpnr_all$lopnr ) # 130
summary( reusedpnr_all_dates )

sampling_date <- data.frame(
  survey_year = c( "SPHC 2002", "SPHC 2006", "SPHC 2010", "SPHC 2014", "SPHC 2021" ),
  sampling_date = as.Date( c( "2002-10-08", "2006-08-09", "2009-12-31", "2014-08-31", "2021-04-08" ) ) )

reusedpnr_all_dates <- reusedpnr_all_dates %>%
  left_join( sampling_date, by = "survey_year" )

id_no_events <- reusedpnr_all_dates %>%
  filter( is.na( event_type ) ) %>% # those without events
  pull( lopnr ) # 70 have remained in registry since 1990
nrow( dates_all %>% filter( lopnr %in% id_no_events ) ) # already excluded

reusedpnr_all_dates <- reusedpnr_all_dates %>%
  filter( !lopnr %in% id_no_events )

sweden_dates <- reusedpnr_all_dates %>% 
  filter( country_of_birth == "Sweden" )
dates_all %>% filter( lopnr %in% sweden_dates$lopnr ) # already included

single_non_sweden_dates <- reusedpnr_all_dates %>%
  filter( country_of_birth != "Sweden" ) %>%
  group_by( lopnr ) %>%
  filter( n() == 1 ) %>%
  ungroup()
table( single_non_sweden_dates$event_type, useNA = "always" ) # 50 move-in, 1 move-out
single_non_sweden_dates %>% filter( date >= sampling_date  ) # 1 move-out

identical(
  single_non_sweden_dates %>% select( lopnr, event_type, date ) %>% arrange( lopnr, date ),
  dates_all %>% filter( lopnr %in% single_non_sweden_dates$lopnr ) %>% arrange( lopnr, date )
) # already included

multiple_non_sweden_dates <- reusedpnr_all_dates %>%
  filter( country_of_birth != "Sweden" ) %>%
  group_by( lopnr ) %>%
  filter( n() > 1 ) %>%
  ungroup()
table( multiple_non_sweden_dates$event_type, useNA = "always" )

multiple_non_sweden_dates_1 <- multiple_non_sweden_dates %>%
  arrange( lopnr, date ) %>%
  group_by( lopnr ) %>%
  filter( first( event_type ) == "move-out" ) %>%
  ungroup()
dates_all %>% filter( lopnr %in% multiple_non_sweden_dates_1$lopnr ) # already included

multiple_non_sweden_dates_2 <- multiple_non_sweden_dates %>%
  filter( !lopnr %in% multiple_non_sweden_dates_1$lopnr ) %>%
  group_by( lopnr ) %>%
  mutate( latest_move_in_date = max( date[ event_type == "move-in" & date < sampling_date ] ) ) %>% # only start follow-up from the latest move-in date before sampling date among those born outside Sweden
  filter( date >= latest_move_in_date ) %>%
  ungroup() %>%
  select( lopnr, event_type, date ) %>%
  arrange( lopnr, date )
length( unique( multiple_non_sweden_dates_2$lopnr ) ) # 7

dates_all <- dates_all %>%
  filter( !lopnr %in% multiple_non_sweden_dates_2$lopnr ) %>%
  bind_rows( multiple_non_sweden_dates_2 ) # any move-in/move-out/death events between 1990 and 2021

dates_all <- dates_all %>%
  left_join( 
    d_all_selected %>%
      select( lopnr, birth_year, survey_year ),
    by = "lopnr" ) %>% 
  mutate( event_age = year( date ) - birth_year ) %>%
  group_by( survey_year ) %>%
  mutate( individual_id = dense_rank( lopnr ) ) %>% # generate continuous pseudo ID number
  ungroup() %>%
  arrange( lopnr, date )

summary( dates_all )

length( unique( dates_all[ dates_all$survey_year == "SPHC 2002", ]$lopnr ) ) # 5,503 in SPHC 2002
max( dates_all[ dates_all$survey_year == "SPHC 2002", ]$individual_id )
length( unique( dates_all[ dates_all$survey_year == "SPHC 2006", ]$lopnr ) ) # 6,938 in SPHC 2006
max( dates_all[ dates_all$survey_year == "SPHC 2006", ]$individual_id )
length( unique( dates_all[ dates_all$survey_year == "SPHC 2010", ]$lopnr ) ) # 5,208 in SPHC 2010
max( dates_all[ dates_all$survey_year == "SPHC 2010", ]$individual_id )
length( unique( dates_all[ dates_all$survey_year == "SPHC 2014", ]$lopnr ) ) # 3,182 in SPHC 2014
max( dates_all[ dates_all$survey_year == "SPHC 2014", ]$individual_id )
length( unique( dates_all[ dates_all$survey_year == "SPHC 2021", ]$lopnr ) ) # 4,327 in SPHC 2021
max( dates_all[ dates_all$survey_year == "SPHC 2021", ]$individual_id )

sampling_date <- sampling_date %>%
  rowwise() %>%
  mutate(
    yend = max( dates_all$individual_id[ dates_all$survey_year == survey_year ] ) + 40 ) %>%
  ungroup() %>%
  rename( sampling_dt = sampling_date )

closest_events <- dates_all %>% # check the closet event before sampling date
  left_join( sampling_date %>% select( survey_year, sampling_dt ), by = "survey_year" ) %>%
  mutate( days_before_sampling = as.numeric( sampling_dt - date ) ) %>%
  filter( days_before_sampling >= 0 )
summary( closest_events$days_before_sampling ) # range from 1 to 11,413 days
table( closest_events$event_type, useNA = "always" ) # confirm that no death event before sampling

id_move_out_before_sampling <- 
  closest_events %>%
  arrange( lopnr, days_before_sampling ) %>%
  group_by( lopnr ) %>%
  slice( 1 ) %>%
  ungroup() %>%
  filter( event_type == "move-out" ) %>%
  pull( lopnr ) # 28 had move-out before sampling date, likely due to technical errors

intersect( id_move_out_before_sampling, reusedpnr_all$lopnr ) # 0
intersect( id_move_out_before_sampling, id_with_overlap ) # 1 (moved out on 1994-02-21)
dates_all %>% filter( lopnr %in% id_move_out_before_sampling ) %>% count( survey_year )

#dates_all %>%
#  filter( lopnr %in% id_move_out_before_sampling ) %>%
#  left_join( sampling_date %>% select( survey_year, sampling_dt ), by = "survey_year" ) %>%
#  arrange( lopnr, date ) %>%
#  View()

# plotting
p_registry_dates <- 
  ggplot( dates_all,
          aes( x = date, y = individual_id, color = event_type ) ) +
  
  geom_point( size = 1.5 ) +
  
  geom_segment(
     data = sampling_date,
     aes( x = sampling_dt, xend = sampling_dt, y = -Inf, yend = yend ),
     inherit.aes = FALSE,
     linetype = "dashed",
     color = "grey20",
     linewidth = 0.5
   ) +
  
  scale_color_manual(
    values = c( "move-in" = "green", "move-out" = "blue", "death" = "red" ),
    labels = c( "move-in" = "Move to Sweden", "move-out" = "Move outside Sweden", "death" = "Death" ) ) +

  scale_x_date(
    limits = as.Date( c( "1990-01-01", NA ) ),
    breaks = seq( as.Date( "1990-01-01" ), as.Date( "2022-01-01" ), by = "2 years" ),
    date_labels = "%Y",
    expand = c( 0.02, 0 ) ) +
  
  labs( x = "Calendar Year", y = "Number of Participants" ) +
  
  theme_classic() +
  theme(
    axis.text = element_text( family = "Arial", size = 11 ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.line.y = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11, margin = margin( b = 5 ) ),
    panel.spacing = unit( 1.5, "lines" ),
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ) ) +
  
  facet_wrap( ~ survey_year,
              ncol = 1,
              scales = "free_y",
              labeller = labeller(
                survey_year = c(
                  "SPHC 2002" = paste0( "SPHC 2002 (N = ", format( max( dates_all$individual_id[ dates_all$survey_year == "SPHC 2002" ] ), big.mark = "," ), ")" ),
                  "SPHC 2006" = paste0( "SPHC 2006 (N = ", format( max( dates_all$individual_id[ dates_all$survey_year == "SPHC 2006" ] ), big.mark = "," ), ")" ),
                  "SPHC 2010" = paste0( "SPHC 2010 (N = ", format( max( dates_all$individual_id[ dates_all$survey_year == "SPHC 2010" ] ), big.mark = "," ), ")" ),
                  "SPHC 2014" = paste0( "SPHC 2014 (N = ", format( max( dates_all$individual_id[ dates_all$survey_year == "SPHC 2014" ] ), big.mark = "," ), ")" ),
                  "SPHC 2021" = paste0( "SPHC 2021 (N = ", format( max( dates_all$individual_id[ dates_all$survey_year == "SPHC 2021" ] ), big.mark = "," ), ")" )
                  ) ) ) +
  
  ggh4x::facetted_pos_scales( y = list(
    survey_year == "SPHC 2002" ~ scale_y_continuous( expand = c( 0.02, 0 ), breaks = c( 1, 1000, 3000, 5000 ) ),
    survey_year == "SPHC 2006" ~ scale_y_continuous( expand = c( 0.02, 0 ), breaks = c( 1, 1000, 3000, 5000, 7000 ) ),
    survey_year == "SPHC 2010" ~ scale_y_continuous( expand = c( 0.02, 0 ), breaks = c( 1, 1000, 3000, 5000 ) ),
    survey_year == "SPHC 2014" ~ scale_y_continuous( expand = c( 0.02, 0 ), breaks = c( 1, 1000, 2000, 3000 ) ),
    survey_year == "SPHC 2021" ~ scale_y_continuous( expand = c( 0.02, 0 ), breaks = c( 1, 1000, 2000, 3000, 4000 ) ) )
    )

p_registry_dates
ggsave( "results_output/plots_general/registry_dates.svg", plot = p_registry_dates, width = 15, height = 12 )

# age at death
p_death_age_year <- 
  ggplot( dates_all %>% filter( event_type == "death" ),
          aes( x = event_age, fill = factor( year( date ) ) ) ) +
  
  geom_bar( position = "stack", alpha = 0.8 ) +
  
  scale_fill_viridis_d( name = "Year at Death", option = "mako" ) +
  
  scale_x_continuous(
    limits = c( 20, 110 ),
    breaks = seq( 20, 110, by = 10 ),
    expand = expansion( mult = c( 0.02, 0 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 450 ),
    breaks = seq( 0, 450, by = 50 ),
    expand = expansion( mult = c( 0, 0 ) ) ) +
  
  labs( x = "Age (y) at Death",
        y = "Number of Participants" ) +
  
  theme_classic() +
  theme(
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.position = "right",
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ) )

p_death_age_year
ggsave( "results_output/plots_general/age_at_death.svg", plot = p_death_age_year, width = 10, height = 8 )
```

### 3. Register-Based Outcomes
#### 3.1. Register diagnosis
```{r}
##### SPHC 2002 to 2014 #####

# outpatient care
outpatient_2002_2014 <- read_dta('/Volumes/projects/LGBT Project data/Swedish Registers/mental_diagnoses_outpatient.dta')
summary( outpatient_2002_2014 )

outpatient_2002_2014 %>%
  mutate( lengths = nchar( indatuma ) ) %>%
  count( lengths )

# outpatient_2002_2014 %>%
#   mutate( lengths = nchar( indatuma ) ) %>%
#   filter( lengths == 4 ) %>%
#   View()
# 
# outpatient_2002_2014 %>%
#   mutate( lengths = nchar( indatuma ) ) %>%
#   filter( lengths == 6 ) %>%
#   View()
# 
# outpatient_2002_2014 %>%
#   mutate( lengths = nchar( indatuma ) ) %>%
#   filter( lengths == 8 ) %>%
#   View()

outpatient_2002_2014 <- outpatient_2002_2014 %>%
  mutate( diagnosis_year = as.integer( substr( indatuma, 1, 4 ) ) ) # the first four digits represent year
summary( outpatient_2002_2014 )

outpatient_2002_2014 %>%
  filter(
    is.na( depression ),
    is.na( anxiety ),
    is.na( stress_related ) ) # 0

outpatient_2002_2014 %>%
  filter(
    is.na( socialstyrelsen_outpatient ),
    is.na( val_outpatient ),
    is.na( val_kon ) ) # 0

setdiff( 2001:2021, outpatient_2002_2014$diagnosis_year[ !is.na( outpatient_2002_2014$socialstyrelsen_outpatient ) ] )
setdiff( 2001:2021, outpatient_2002_2014$diagnosis_year[ !is.na( outpatient_2002_2014$val_outpatient ) ] ) # val_outpatient includes both specialist outpatient care during 2001-2019 and primary care during 2013-2019
setdiff( 2001:2021, outpatient_2002_2014$diagnosis_year[ !is.na( outpatient_2002_2014$val_kon ) ] ) # val_kon includes primary care data during 2003-2012

# check indicator variable
table( outpatient_2002_2014$vardniva, useNA = "always" )
str( outpatient_2002_2014$vardniva )

outpatient_2002_2014 <- outpatient_2002_2014 %>%
  mutate( vardniva = na_if( vardniva, "" ) )

outpatient_2002_2014 %>%
  filter( vardniva == "01" ) %>%
  distinct( diagnosis_year ) %>%
  arrange( diagnosis_year ) # 2013-2019

outpatient_2002_2014 %>%
  filter( vardniva == "02" ) %>%
  distinct( diagnosis_year ) %>%
  arrange( diagnosis_year ) # 2003-2019


missing_pattern( outpatient_2002_2014 %>%
                   select( val_outpatient, vardniva ))

outpatient_2002_2014 %>%
  filter( is.na( vardniva ) ) %>%
  distinct( diagnosis_year ) %>%
  arrange( diagnosis_year ) # 2003-2019


table( outpatient_2002_2014$diagnosis_year, outpatient_2002_2014$vardniva )
table( outpatient_2002_2014$val_outpatient, useNA = "always" )

outpatient_2002_2014 %>%
  filter(val_outpatient == 1,
         vardniva != "",
         !is.na( vardniva )) %>%
   mutate( lengths = nchar( indatuma ) ) %>%
  count( lengths )
  
  
  
  group_by(lopnr, indatuma) %>%
  filter(n() > 1) %>%
  arrange(lopnr, indatuma)

outpatient_2002_2014 %>%
  filter( diagnosis_year >= 2013,
          diagnosis_year <= 2019,
          !is.na( val_outpatient ) ) %>%
  count( vardniva )
  



# inpatient care
inpatient_2002_2014 <- read_dta('/Volumes/projects/LGBT Project data/Swedish Registers/mental_diagnoses_inpatient.dta')
summary( inpatient_2002_2014 )

inpatient_2002_2014 %>%
  mutate( lengths = nchar( indatuma ) ) %>%
  count( lengths )

inpatient_2002_2014 <- inpatient_2002_2014 %>%
  mutate( diagnosis_year = as.integer( substr( indatuma, 1, 4 ) ) ) # the first four digits represent year
summary( inpatient_2002_2014 )

inpatient_2002_2014 %>%
  filter(
    is.na( depression ),
    is.na( anxiety ),
    is.na( stress_related ) ) # 0

inpatient_2002_2014 %>%
  filter(
    is.na( socialstyrelsen_inpatient ),
    is.na( val_inpatient ) ) # 0

setdiff( 2001:2021, inpatient_2002_2014$diagnosis_year[ !is.na( inpatient_2002_2014$socialstyrelsen_inpatient ) ] )
setdiff( 2001:2021, inpatient_2002_2014$diagnosis_year[ !is.na( inpatient_2002_2014$val_inpatient ) ] )


# merge data
d_diagnosis_2002_2014 <- bind_rows( outpatient_2002_2014 %>% 
                                      select( lopnr, diagnosis_year, depression, anxiety, stress_related ), 
                                    inpatient_2002_2014 %>%
                                      select( lopnr, diagnosis_year, depression, anxiety, stress_related ) )
summary( d_diagnosis_2002_2014 )

n_distinct( d_diagnosis_2002_2014$lopnr ) == 
  length( intersect( unique( d_diagnosis_2002_2014$lopnr ),
                     d_all_selected$lopnr[ d_all_selected$survey_year != "SPHC 2021" ] ) ) # TRUE


##### SPHC 2021 #####

outpatient_2021 <- read_dta('/Volumes/projects/LGBT Project data/Swedish Registers/mental_diagnoses_outpatient_2021.dta')
inpatient_2021 <- read_dta('/Volumes/projects/LGBT Project data/Swedish Registers/mental_diagnoses_inpatient_2021.dta')

summary( outpatient_2021 )
summary( inpatient_2021 )

outpatient_2021 %>%
  filter(
    is.na( depression ),
    is.na( anxiety ),
    is.na( stress_related ) ) # 0

inpatient_2021 %>%
  filter(
    is.na( depression ),
    is.na( anxiety ),
    is.na( stress_related ) ) # 0

outpatient_2021 %>%
  mutate( lengths = nchar( indatuma ) ) %>%
  count( lengths )

inpatient_2021 %>%
  mutate( lengths = nchar( indatuma ) ) %>%
  count( lengths )

outpatient_2021 <- outpatient_2021 %>%
  rename( lopnr = lopnr2  ) %>%
  mutate( lopnr = lopnr + 600000,
          diagnosis_year = as.integer( substr( indatuma, 1, 4 ) ) )

inpatient_2021 <- inpatient_2021 %>%
  rename( lopnr = lopnr2  ) %>%
  mutate( lopnr = lopnr + 600000,
          diagnosis_year = as.integer( substr( indatuma, 1, 4 ) ) )

d_diagnosis_2021 <- bind_rows( outpatient_2021 %>%
                                 select( lopnr, diagnosis_year, depression, anxiety, stress_related ), 
                               inpatient_2021 %>%
                                 select( lopnr, diagnosis_year, depression, anxiety, stress_related ) )
summary( d_diagnosis_2021 )

n_distinct( d_diagnosis_2021$lopnr ) == 
  length( intersect( unique( d_diagnosis_2021$lopnr ),
                     d_all_selected$lopnr[ d_all_selected$survey_year == "SPHC 2021" ] ) ) # TRUE


##### merge data #####

d_all_diagnosis <- bind_rows( d_diagnosis_2002_2014, d_diagnosis_2021 )
summary( d_all_diagnosis )

d_all_diagnosis %>%
  filter(
    is.na( depression ),
    is.na( anxiety ),
    is.na( stress_related ) ) # 0

d_all_diagnosis_summary <- d_all_diagnosis %>%
  mutate( across( c( depression, anxiety, stress_related ), 
                  ~ replace_na( .x, 0 ) ) ) %>%
  group_by( lopnr, diagnosis_year ) %>%
  summarise(
    depression = if_else( any( depression == 1 ), "Yes", "No" ),
    anxiety = if_else( any( anxiety == 1 ), "Yes", "No" ),
    stress_related = if_else( any( stress_related == 1 ), "Yes", "No" ),
    .groups = "drop" ) %>%
  mutate(
    depression = factor( depression, levels = c( "Yes", "No" ) ),
    anxiety = factor( anxiety, levels = c( "Yes", "No" ) ),
    stress_related = factor( stress_related, levels = c( "Yes", "No" ) ) )

summary( d_all_diagnosis_summary )


# plot register coverage
coverage_df <- tibble(
  registry = c( "NPR: Inpatient care", 
                "NPR: Specialist outpatient care", 
                "VAL: Inpatient care", 
                "VAL: Specialist outpatient care", 
                "VAL: Primary care",
                "Prescribed Drug Register" ),
  start = c( 2001, 2001, 2001, 2001, 2003, 2005 ),
  end   = c( 2021, 2021, 2019, 2019, 2019, 2021 ) ) %>%
  
  mutate(
    care_type = case_when(
      grepl( "Inpatient", registry ) ~ "Inpatient",
      grepl( "Specialist", registry ) ~ "Specialist outpatient",
      grepl( "Primary", registry ) ~ "Primary care",
      registry == "Prescribed Drug Register" ~ "Dispensed prescription" ),
    
    registry = factor( registry, levels = c( "Prescribed Drug Register", "NPR: Inpatient care", "VAL: Inpatient care", "NPR: Specialist outpatient care", "VAL: Specialist outpatient care", "VAL: Primary care" ) ),
    care_type = factor( care_type, levels =  c( "Primary care", "Specialist outpatient", "Inpatient", "Dispensed prescription" ) ) )

p_register_coverage <- 
  ggplot( coverage_df, aes( y = registry, color = care_type ) ) +
  
  geom_segment(
    aes( x = start, xend = end, yend = registry ),
    linewidth = 4.5 ) +
  
  geom_text(
    aes( x = ( start + end )/2, label = paste0( start, "–", end ) ),
    color = "black",
    size = 3.7,
    vjust = -1 ) +
  
  scale_x_continuous(
    breaks = seq( 2001, 2021, 2 ),
    limits = c( 2001, 2021 ),
    expand = expansion( mult = c( 0.05, 0.02 ) ) ) +
  
  scale_color_manual( values = c(
    "Primary care" = "#F8766D",
    "Specialist outpatient" = "#C77CFF",
    "Inpatient" = "#00BFC4",
    "Dispensed prescription" = "#7CAE00" ) ) +
  
  labs(
    x = "Calendar Year",
    y = NULL,
    color = NULL ) +
  
  theme_classic() +
  theme(
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_register_coverage
ggsave( "results_output/plots_general/p_register_coverage.svg", plot = p_register_coverage, width = 12, height = 6 )


# plot data sources
diagnosis_source_summary <- d_diagnosis_2002_2014 %>%
  
  filter( diagnosis_year >= 2003, 
          diagnosis_year <= 2019 ) %>%
  
  pivot_longer(
    cols = c( depression, anxiety, stress_related ),
    names_to = "outcome",
    values_to = "value" ) %>%
  
  filter( value == 1 ) %>%
  
  # reshape ALL sources (outpatient + inpatient)
  pivot_longer(
    cols = c(
      socialstyrelsen_outpatient,
      socialstyrelsen_inpatient,
      val_outpatient,
      val_inpatient,
      val_kon
    ),
    names_to = "source",
    values_to = "has_record"
  ) %>%
  
  # keep only present sources
  filter(!is.na(has_record)) %>%
  
  # harmonise source labels
  mutate(
    source = case_when(
      source %in% c("socialstyrelsen_outpatient", "socialstyrelsen_inpatient") ~ "NPR",
      source %in% c("val_outpatient", "val_inpatient") ~ "VAL",
      source == "val_kon" ~ "VAL primary"
    ),
    
    outcome = recode(outcome,
                     depression = "Depression",
                     anxiety = "Anxiety Disorders",
                     stress_related = "Stress-Related Disorders"
    )
  ) %>%
  
  distinct(lopnr, diagnosis_year, outcome, source) %>%
  
  # count individuals (not visits)
  count(diagnosis_year, outcome, source) %>%
  
  group_by(diagnosis_year, outcome) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()

p_source <- ggplot(
  diagnosis_source_summary,
  aes(x = diagnosis_year, y = prop, fill = source)
) +
  
  geom_area(alpha = 0.8) +
  
  facet_wrap(~ outcome, ncol = 1) +
  
  scale_y_continuous(labels = scales::percent_format()) +
  
  scale_x_continuous(
    breaks = seq(2003, 2019, 4),
    expand = expansion(mult = c(0.02, 0.02))
  ) +
  
  scale_fill_manual(values = c(
    "NPR" = "#F8766D",
    "VAL" = "#00BFC4",
    "VAL primary" = "#7CAE00"
  )) +
  
  labs(
    x = "Year",
    y = "Proportion of Diagnoses",
    fill = "Data Source"
  ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text(size = 11),
    legend.position = "bottom"
  )

p_source
```

#### 3.2. Use of antidepressants and anxiolytics
```{r}
# dispensed prescription: antidepressants (N06A) and anxiolytics (N05B)
# between 2005-06-30/2005-07-01 and 2021-12-31
# the year 2005 only covers 6 months

atc_2002_2014 <- read_sas('/Volumes/projects/LGBT Project data/Swedish Registers/atc_pdr_2002_2014.sas7bdat') %>%
  filter( !grepl( "^N05CD", ATC ) ) %>%
  rename( dispense_date = EDATUM )
summary( atc_2002_2014 )
unique( atc_2002_2014$ATC )

atc_2021 <- read_sas('/Volumes/projects/LGBT Project data/Swedish Registers/atc_pdr_2021.sas7bdat') %>%
  filter( !grepl( "^N05CD", ATC ) ) %>%
  rename( lopnr = lopnr2, dispense_date = EDATUM ) %>%
  mutate( lopnr = lopnr + 600000 ) %>%
  select( lopnr, ATC, dispense_date )
summary( atc_2021 )
unique( atc_2021$ATC )
  
atc_all <- bind_rows( atc_2002_2014, atc_2021 ) %>%
  mutate( 
    drug_class = as.factor( 
      case_when(
        grepl( "^N06A", ATC ) ~ "N06A",
        grepl( "^N05B", ATC ) ~ "N05B" ) ),
    year = year( dispense_date ) )
summary( atc_all )
unique( atc_all$ATC )

atc_all_summary <- atc_all %>%
  group_by( lopnr, year ) %>%
  summarise(
    used_N05B = if_else( any( drug_class == "N05B" ), "Yes", "No" ),
    used_N06A = if_else( any( drug_class == "N06A" ), "Yes", "No" ),
    .groups = "drop" ) %>%
  mutate(
    used_N05B = factor( used_N05B, levels = c( "Yes", "No" ) ),
    used_N06A = factor( used_N06A, levels = c( "Yes", "No" ) ) )
summary( atc_all_summary )
```

### 4. Series of Cross-Sectional Analysis
#### 4.1. Construct study samples
```{r}
# include death dates
death_df <- dates_all %>%
  filter( event_type == "death" ) %>%
  select( lopnr, date ) %>%
  rename( death_date = date )
n_distinct( death_df$lopnr )

# death_df %>%
#   filter( format( death_date, "%m-%d" ) == "01-01" )

d_all_selected_death <- d_all_selected %>%
  left_join( death_df, by = "lopnr" )
summary( d_all_selected_death$death_date )
nrow( d_all_selected_death[ !is.na( d_all_selected_death$death_date ), ] )

# create study samples
yearly_sample <- list()

for ( yr in 2001:2021 ) {
  
  followup_start <- as.Date( paste0( yr, "-01-01" ) )

  study_sample <- d_all_selected_death %>%
    filter( birth_year >= yr - 29,
            birth_year <= yr - 16,
            is.na( death_date ) | death_date > followup_start ) %>%
    mutate( age = yr - birth_year )
    
  yearly_sample[[ as.character( yr ) ]] <- study_sample
}

pooled_sample_cs <- bind_rows( yearly_sample, .id = "sample_year" ) %>%
  mutate( sample_year = as.integer( sample_year ) ) %>%
  select( sample_year, lopnr, sex, age, country_of_birth, sexual_identity_baseline, survey_year, death_date ) %>%
  mutate( death_same_year = factor( year( death_date ) == sample_year,
                                    levels = c( FALSE, TRUE ),
                                    labels = c( "No", "Yes" ) ) )

summary( pooled_sample_cs )
n_distinct( pooled_sample_cs$lopnr ) # total sample size = 38,675
print( pooled_sample_cs %>% count( sample_year ),
       n = Inf )

pooled_sample_cs %>%
  filter( death_same_year == "Yes" ) %>%
  pull( lopnr ) # five died

pooled_sample_cs %>%
  filter( death_same_year == "Yes" ) %>%
  count( sample_year, death_same_year )

# pooled_sample_cs %>%
#   filter( !is.na( death_date ) ) %>%
#   View()

pooled_sample_cs <- pooled_sample_cs %>%
  select( - death_date ) %>%
  rename( death = death_same_year ) %>%
  mutate( death = if_else( is.na( death ), "No", death ),
          death = factor( death, levels = c( "Yes", "No" ) ) )

summary( pooled_sample_cs )
```

#### 4.2. Plot samples
```{r}
plot_sample_cs <- pooled_sample_cs %>%
  mutate( sexual_identity_baseline = fct_na_value_to_level( sexual_identity_baseline, level = "Missing" ) ) %>%
  group_by( sample_year, sexual_identity_baseline ) %>%
  summarise( n = n(), .groups = "drop" ) %>%
  mutate( identity_group = case_when( 
            sexual_identity_baseline %in% c( "Heterosexual" ) ~ "Heterosexual",
            sexual_identity_baseline %in% c( "Homosexual", "Bisexual", "Other", "Missing" ) ~ "Sexual Minority or Missing" ) ) %>%
  arrange( identity_group, n )

# plot sample size by year
p_pooled_sample_cs <- ggplot(
  plot_sample_cs,
  aes( x = sample_year,
       y = n,
       color = sexual_identity_baseline,
       group = sexual_identity_baseline ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2001, 2021 ),
    breaks = seq( 2001, 2021, 4 ),
    expand = expansion( mult = c( 0.05, 0.05 ) ) ) +
  
  scale_color_manual( values = c(
    "Heterosexual" = "#F8766D",
    "Homosexual"   = "#00BFC4",
    "Bisexual"     = "#C77CFF",
    "Other"        = "#7CAE00",
    "Missing"      = "#7f7f7f" ) ) +
  
  labs( x = "Cross-Sectional Sample Year",
        y = "Number of Participants",
        color = NULL ) +
  
  facet_wrap( ~ identity_group, scales = "free_y" ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_blank(),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  ggh4x::facetted_pos_scales( y = list(
    identity_group == "Heterosexual" ~ scale_y_continuous( limits = c( 4000, 22000 ), breaks = c( seq( 4000, 22000, 2000 ) ), labels = scales::label_comma(), expand = expansion( mult = c( 0.05, 0.01 ) ) ),
    identity_group == "Sexual Minority or Missing" ~ scale_y_continuous( limits = c( 0, 4500 ), breaks = c( seq( 0, 4500, 500 ) ), labels = scales::label_comma(), expand = expansion( mult = c( 0.05, 0.01 ) ) ) ) ) +
  
  coord_capped_cart( left = "top", bottom = 'right', gap = 0 )

p_pooled_sample_cs
ggsave( "results_output/plots_general/p_pooled_sample_cs.svg", plot = p_pooled_sample_cs, width = 11, height = 6 )

# check overlapping participants
lopnr_years <- pooled_sample_cs %>%
  select( lopnr, sample_year ) %>%
  mutate( value = 1 ) %>%
  pivot_wider( names_from = sample_year, 
               values_from = value, 
               values_fill = 0 ) %>%
  as.data.frame()

pdf( "results_output/plots_general/p_overlap_upset_cs.pdf", width = 11, height = 9, onefile = FALSE ) # upset plot
upset(
  data = lopnr_years,
  nsets = length( colnames( lopnr_years )[-1] ),
  sets = colnames( lopnr_years )[-1],
  keep.order = TRUE,
  order.by = "freq",
  mainbar.y.label = "Intersection Size",
  sets.x.label = "Sample Size",
  sets.bar.color = "#A32214",
  point.size = 2.5,
  line.size = 1,
  text.scale = c( 1.3, 1.3, 1.3, 1.3, 1.3, 1 ),
  number.angles = 30
  )
dev.off()

lopnr_years_alluvial <- lopnr_years %>% # prepare for alluvial plot
  select( c( seq( 2, 22, by = 2 ) ) ) %>%
  mutate( across( everything(),
                  ~ factor( ifelse( .x == 1, "Included", "Excluded" ),
                            levels = c( "Excluded", "Included" ) ) ) 
          ) %>%
  count( across( everything() ) ) %>%
  rename( number = n ) %>%
  mutate( percent = number / sum( number ) )

sum( lopnr_years_alluvial$number ) == nrow( lopnr_years ) # TRUE
sum( lopnr_years_alluvial$percent )

lopnr_years_alluvial_long <- to_lodes_form( lopnr_years_alluvial, # convert to long format
                                            axes = 1:11, 
                                            key = "year", 
                                            value = "inclusion_status", 
                                            id = "cohort", 
                                            diffuse = `2011` ) 

p_overlap_alluvial_cs <- 
  ggplot( lopnr_years_alluvial_long,
          aes( x = year,
               stratum = inclusion_status, 
               alluvium = cohort,
               y = percent ) ) +
  geom_alluvium( aes( fill = `2011` ), curve_type = "cubic" ) +
  geom_stratum( aes( fill = `2011` ) ) +
  geom_text( stat = "stratum", 
             aes( label = ifelse( after_stat( stratum ) == "Included", "Incl.", "Excl." ) ), 
             family = "Arial", 
             size = 11 / .pt ) +
  scale_fill_manual( values = c( "#00BFC4", "#F8766D" ),
                     breaks = c( "Included", "Excluded" ),
                     na.value = NA ) +
  scale_x_discrete( expand = expansion( mult = c( 0, 0.02 ) ) ) +
  scale_y_continuous( labels = scales::percent, breaks = c( 0, 0.25, 0.5, 0.75, 1 ) ) +
  labs( x = "Cross-Sectional Sample Year", y = "Percentage" ) +
  theme_classic() +
  theme( axis.text = element_text( family = "Arial", size = 11 ),
         axis.title = element_text( family = "Arial", size = 11 ),
         legend.title = element_blank(),
         legend.text = element_text( family = "Arial", size = 10 ), 
         legend.key = element_rect( colour = "white" ),
         legend.position = "bottom",
         axis.ticks.x.bottom = element_blank(),
         axis.line.x.bottom = element_blank()
         )

p_overlap_alluvial_cs
ggsave( "results_output/plots_general/p_overlap_alluvial_cs.svg", plot = p_overlap_alluvial_cs, width = 14, height = 8 )
```

#### 4.3. Add outcomes
```{r}
pooled_sample_cs <- pooled_sample_cs %>%
  left_join( atc_all_summary, by = c( "sample_year" = "year", "lopnr" ) ) %>%
  left_join( d_all_diagnosis_summary, by = c( "sample_year" = "diagnosis_year", "lopnr" ) ) %>%
  mutate(
    # assuming absence of outcome when no records; migration data was later used to determine missing outcome data
    across( c( used_N05B, used_N06A ),
            ~ if_else( sample_year >= 2005 & is.na( .x ), "No", .x ) ),
    across( c( depression, anxiety, stress_related ),
            ~ replace_na( .x, "No" ) ),
    
    used_N05B = factor( used_N05B, levels = c( "Yes", "No" ) ),
    used_N06A = factor( used_N06A, levels = c( "Yes", "No" ) ) 
    ) %>%
  arrange( lopnr, sample_year )

summary( pooled_sample_cs )

# sanity check
summary(
  pooled_sample_cs %>%
    filter( sample_year < 2005 ) )

summary(
  pooled_sample_cs %>%
    filter( sample_year >= 2005 ) )
```

#### 4.4. Add follow-up data
```{r}
# dates_all %>%
#   filter( lopnr %in% pooled_sample_cs$lopnr[ pooled_sample_cs$death == "Yes" ] ) %>%
#   View() # for individuals who died, they did not have any migration events during the same year; thus, their register status for the year when they died was treated as TRUE

# check migration events
yearly_sample <- list()

for ( yr in 2001:2021 ) {
  
  followup_start <- as.Date( paste0( yr, "-01-01" ) )
  followup_end <- as.Date( paste0( yr, "-12-31" ) )
  
  ids_year <- pooled_sample_cs$lopnr[ pooled_sample_cs$sample_year == yr ]
  
  eligible_dates <- dates_all %>% filter( lopnr %in% ids_year )
  
  move_in_ids <- eligible_dates %>%
    filter( date < followup_start ) %>%
    arrange( lopnr, date ) %>%
    group_by( lopnr ) %>%
    slice_tail( n = 1 ) %>%
    ungroup() %>%
    filter( event_type == "move-in" ) %>%
    pull( lopnr )

  had_event_ids <- eligible_dates %>%
    filter( lopnr %in% move_in_ids, 
            date >= followup_start, 
            date <= followup_end ) %>%
    pull( lopnr ) %>%
    unique()
  
  move_in_before_year_ids <- setdiff( move_in_ids, had_event_ids )
    
  move_out_after_year_ids <- eligible_dates %>%
    arrange( lopnr, date ) %>%
    group_by( lopnr ) %>%
    slice( 1 ) %>%
    ungroup() %>%
    filter( date > followup_end,
            event_type %in% c( "move-out", "death" ) ) %>%
    pull( lopnr )
  
  death_ids <- pooled_sample_cs %>%
    filter( sample_year == yr,
            death == "Yes" ) %>%
    pull( lopnr )

  included_year_ids <- union( union( move_in_before_year_ids, move_out_after_year_ids ), 
                              death_ids )
  
  excluded_year_ids <- eligible_dates %>%
    filter( !lopnr %in% included_year_ids ) %>%
    pull( lopnr ) %>%
    unique()
  
  study_sample <- pooled_sample_cs %>%
    filter( sample_year == yr ) %>%
    mutate( registered_year = if_else( lopnr %in% excluded_year_ids, FALSE, TRUE ) )
  
  yearly_sample[[ as.character( yr ) ]] <- study_sample
  }

pooled_sample_cs_final <- bind_rows( yearly_sample, .id = "sample_year" ) %>%
  mutate( sample_year = as.numeric( sample_year ) )

summary( pooled_sample_cs_final )
str( pooled_sample_cs_final )

identical(
  pooled_sample_cs_final %>% select( -registered_year ) %>% arrange( lopnr, sample_year ),
  pooled_sample_cs %>% mutate( sample_year = as.numeric( sample_year ) ) %>% arrange( lopnr, sample_year )
) # TRUE


# prescription data only have a half year of coverage in 2005
# check register status during this period
{  
  followup_start <- as.Date( "2005-07-01" )
  followup_end <- as.Date( "2005-12-31" )
  
  ids_year <- pooled_sample_cs$lopnr[ pooled_sample_cs$sample_year == 2005 ]
  
  eligible_dates <- dates_all %>% filter( lopnr %in% ids_year )
  
  move_in_ids <- eligible_dates %>%
    filter( date < followup_start ) %>%
    arrange( lopnr, date ) %>%
    group_by( lopnr ) %>%
    slice_tail( n = 1 ) %>%
    ungroup() %>%
    filter( event_type == "move-in" ) %>%
    pull( lopnr )

  had_event_ids <- eligible_dates %>%
    filter( lopnr %in% move_in_ids, 
            date >= followup_start, 
            date <= followup_end ) %>%
    pull( lopnr ) %>%
    unique()
  
  move_in_before_year_ids <- setdiff( move_in_ids, had_event_ids )
    
  move_out_after_year_ids <- eligible_dates %>%
    arrange( lopnr, date ) %>%
    group_by( lopnr ) %>%
    slice( 1 ) %>%
    ungroup() %>%
    filter( date > followup_end,
            event_type %in% c( "move-out", "death" ) ) %>%
    pull( lopnr )

  included_year_ids <- union( move_in_before_year_ids, move_out_after_year_ids )
  
  excluded_year_ids <- eligible_dates %>%
    filter( !lopnr %in% included_year_ids ) %>%
    pull( lopnr ) %>%
    unique()
}

pooled_sample_cs_final <- pooled_sample_cs_final %>%
  mutate(
    registered_half_2005 = case_when(
      sample_year != 2005 ~ NA,
      lopnr %in% excluded_year_ids ~ FALSE,
      TRUE ~ TRUE ) )

table( pooled_sample_cs_final$registered_half_2005, useNA = "always" )
pooled_sample_cs_final %>%
  filter( sample_year != 2005 ) %>%
  count( registered_half_2005 )

pooled_sample_cs_final %>%
  filter( sample_year == 2005 ) %>%
  count( registered_year, registered_half_2005 )

# introduce missing data
pooled_sample_cs_final <- pooled_sample_cs_final %>%
  mutate( across( c( used_N05B, used_N06A ),
                  ~ case_when( sample_year == 2005 & registered_half_2005 == FALSE & .x == "No" ~ NA,
                               sample_year >= 2006 & registered_year == FALSE & .x == "No" ~ NA,
                               TRUE ~ .x ) ),
          
          across( c( depression, anxiety, stress_related ),
                  ~ if_else( registered_year == FALSE & .x == "No", NA, .x ) ) ) %>%
  select( -c( registered_year, registered_half_2005, death ) )

summary( pooled_sample_cs_final )

# random check incomplete variables
miss_var_summary( pooled_sample_cs_final %>% filter( sample_year == 2002 ) ) %>% filter( n_miss > 0 ) %>% print( n = Inf )
miss_var_summary( pooled_sample_cs_final %>% filter( sample_year == 2006 ) ) %>% filter( n_miss > 0 ) %>% print( n = Inf )
miss_var_summary( pooled_sample_cs_final %>% filter( sample_year == 2010 ) ) %>% filter( n_miss > 0 ) %>% print( n = Inf )
miss_var_summary( pooled_sample_cs_final %>% filter( sample_year == 2014 ) ) %>% filter( n_miss > 0 ) %>% print( n = Inf )
miss_var_summary( pooled_sample_cs_final %>% filter( sample_year == 2021 ) ) %>% filter( n_miss > 0 ) %>% print( n = Inf )

# check missing pattern
missing_pattern( pooled_sample_cs_final %>% filter( sample_year == 2006 ) )
missing_pattern( pooled_sample_cs_final %>% filter( sample_year == 2010 ) )
missing_pattern( pooled_sample_cs_final %>% filter( sample_year == 2014 ) )
missing_pattern( pooled_sample_cs_final %>% filter( sample_year == 2021 ) )

# plot missing variables
missing_summary_cs <- pooled_sample_cs_final %>%
  select( sample_year, sexual_identity_baseline, used_N05B, used_N06A, depression, anxiety, stress_related ) %>%
  group_by( sample_year ) %>%
  summarise( across( everything(),
                     ~ mean( is.na( .x ) ),
                     .names = "{.col}" ) ) %>%
  pivot_longer( cols = - sample_year,
                names_to = "variable",
                values_to = "percent_missing" ) %>%
  mutate( variable = factor( variable, 
                             levels = c( "sexual_identity_baseline", "depression", "anxiety", "stress_related", "used_N06A", "used_N05B" ) ) )

p_missing_cs <- ggplot( 
  missing_summary_cs %>%
    filter( !( sample_year < 2005 & variable %in% c( "used_N05B", "used_N06A" ) ) ),
  aes( x = sample_year, y = percent_missing ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  labs(
    x = "Cross-Sectional Sample Year",
    y = "Percentage of Missingness" ) +
  
  facet_wrap( ~ variable,
              ncol = 3,
              axes = "all",
              scales = "free",
              labeller = labeller( variable = c(
                depression = "Depression",
                anxiety = "Anxiety Disorders",
                stress_related = "Stress-Related Disorders",
                used_N05B = "Anxiolytic Use",
                used_N06A = "Antidepressant Use",
                sexual_identity_baseline = "Sexual Identity" ) ) ) +
  
  ggh4x::facetted_pos_scales( 
    x = list(
      variable %in% c( "sexual_identity_baseline", "depression", "anxiety", "stress_related" ) ~
        scale_x_continuous( breaks = seq( 2001, 2021, 4 ),
                            limits = c( 2001, 2021 ),
                            expand = expansion( mult = c( 0.08, 0.02 ) ) ),
      
      variable %in% c( "used_N05B", "used_N06A" ) ~
        scale_x_continuous( breaks = seq( 2005, 2021, 4 ),
                            limits = c( 2005, 2021 ),
                            expand = expansion( mult = c( 0.08, 0.02 ) ) ) ),
    
    y = list(
      variable == "sexual_identity_baseline" ~ 
        scale_y_continuous( limits = c( 0, 0.2 ),
                            breaks = c( seq( 0, 0.2, 0.05 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
      
      variable == "depression" ~ 
        scale_y_continuous( limits = c( 0, 0.15 ),
                            breaks = c( seq( 0, 0.15, 0.05 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
      
      variable == "anxiety" ~ 
        scale_y_continuous( limits = c( 0, 0.15 ),
                            breaks = c( seq( 0, 0.15, 0.05 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
      
      variable == "stress_related" ~ 
        scale_y_continuous( limits = c( 0, 0.15 ),
                            breaks = c( seq( 0, 0.15, 0.05 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
    
      variable == "used_N06A" ~ 
        scale_y_continuous( limits = c( 0, 0.1 ),
                            breaks = c( seq( 0, 0.1, 0.05 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
    
      variable == "used_N05B" ~ 
        scale_y_continuous( limits = c( 0, 0.1 ),
                            breaks = c( seq( 0, 0.1, 0.05 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_missing_cs
ggsave( "results_output/plots_general/p_missing_cs.svg", plot = p_missing_cs, width = 14, height = 9 )
```

#### 4.5. Complete-case analysis
```{r}
outcome_list_1 <- list(
  list( variable = "depression", condition = "Yes", name = "depression" ),
  list( variable = "anxiety", condition = "Yes", name = "anxiety" ),
  list( variable = "stress_related", condition = "Yes", name = "stress_related" ) )

outcome_list_2 <- list(
  list( variable = "used_N06A", condition = "Yes", name = "antidepressant_use" ),
  list( variable = "used_N05B", condition = "Yes", name = "anxiolytic_use" ) )


########## Prevalence ##########

# by sexual identity
results_list_1 <- cal_prev_poo_cc( year_start = 2001, 
                                   year_end = 2021,
                                   data = pooled_sample_cs_final,
                                   variables_list = outcome_list_1,
                                   group_var = "sexual_identity_baseline" )

results_list_2 <- cal_prev_poo_cc( year_start = 2005, 
                                   year_end = 2021,
                                   data = pooled_sample_cs_final,
                                   variables_list = outcome_list_2,
                                   group_var = "sexual_identity_baseline" )

prevalence_poo <- bind_rows( bind_rows( results_list_1 ), 
                             bind_rows( results_list_2 ) )
writexl::write_xlsx( prevalence_poo, "results_output/results_cc/prevalence_poo_cs_cc.xlsx" )

# by sex
results_list_by_sex_1 <- cal_prev_poo_cc( year_start = 2001, 
                                          year_end = 2021,
                                          data = pooled_sample_cs_final,
                                          variables_list = outcome_list_1,
                                          group_var = "sexual_identity_baseline + sex",
                                          subgroup = TRUE )

results_list_by_sex_2 <- cal_prev_poo_cc( year_start = 2005, 
                                          year_end = 2021,
                                          data = pooled_sample_cs_final,
                                          variables_list = outcome_list_2,
                                          group_var = "sexual_identity_baseline + sex",
                                          subgroup = TRUE )

prevalence_poo_by_sex <- bind_rows( bind_rows( results_list_by_sex_1 ),
                                    bind_rows( results_list_by_sex_2 ) )
writexl::write_xlsx( prevalence_poo_by_sex, "results_output/results_cc/prevalence_poo_cs_by_sex_cc.xlsx" )


########## Prevalence Ratio ##########

str( pooled_sample_cs_final )

# crude analysis
pr_models_list_crude_1 <- cal_pr_poo_cc( year_start = 2001,
                                         year_end = 2021,
                                         data = pooled_sample_cs_final %>%
                                           mutate( depression = ifelse( depression == "Yes", 1, 0 ),
                                                   anxiety = ifelse( anxiety == "Yes", 1, 0 ),
                                                   stress_related = ifelse( stress_related == "Yes", 1, 0 ) ),
                                         exposure = "sexual_identity_baseline",
                                         outcome_list = outcome_list_1 )

pr_models_list_crude_2 <- cal_pr_poo_cc( year_start = 2005,
                                         year_end = 2021,
                                         data = pooled_sample_cs_final %>%
                                           mutate( used_N06A = ifelse( used_N06A == "Yes", 1, 0 ),
                                                   used_N05B = ifelse( used_N05B == "Yes", 1, 0 ) ),
                                         exposure = "sexual_identity_baseline",
                                         outcome_list = outcome_list_2 )

# adjusted analysis
pr_models_list_adjusted_1 <- cal_pr_poo_cc( year_start = 2001,
                                            year_end = 2021,
                                            data = pooled_sample_cs_final %>%
                                              mutate( depression = ifelse( depression == "Yes", 1, 0 ),
                                                      anxiety = ifelse( anxiety == "Yes", 1, 0 ),
                                                      stress_related = ifelse( stress_related == "Yes", 1, 0 ) ),
                                            exposure = "sexual_identity_baseline",
                                            outcome_list = outcome_list_1,
                                            covariates = "age + sex + country_of_birth" )

pr_models_list_adjusted_2 <- cal_pr_poo_cc( year_start = 2005,
                                            year_end = 2021,
                                            data = pooled_sample_cs_final %>%
                                              mutate( used_N06A = ifelse( used_N06A == "Yes", 1, 0 ),
                                                      used_N05B = ifelse( used_N05B == "Yes", 1, 0 ) ),
                                            exposure = "sexual_identity_baseline",
                                            outcome_list = outcome_list_2,
                                            covariates = "age + sex + country_of_birth" )


pr_crude_cc_1 <- extract_pr_cc(
  model_list = pr_models_list_crude_1,
  exposure_var = "sexual_identity_baseline" ) %>%
  mutate( model_type = "crude" )

pr_crude_cc_2 <- extract_pr_cc(
  model_list = pr_models_list_crude_2,
  exposure_var = "sexual_identity_baseline" ) %>%
  mutate( model_type = "crude" )

pr_adjusted_cc_1 <- extract_pr_cc(
  model_list = pr_models_list_adjusted_1,
  exposure_var = "sexual_identity_baseline" ) %>%
  mutate( model_type = "adjusted" )

pr_adjusted_cc_2 <- extract_pr_cc(
  model_list = pr_models_list_adjusted_2,
  exposure_var = "sexual_identity_baseline" ) %>%
  mutate( model_type = "adjusted" )

pr_poo_cc <- bind_rows( pr_crude_cc_1, pr_crude_cc_2, pr_adjusted_cc_1, pr_adjusted_cc_2 )
writexl::write_xlsx( pr_poo_cc, "results_output/results_cc/pr_poo_cs_cc.xlsx" )


########## Prevalence Difference ##########

# crude analysis
pd_models_list_crude_1 <- cal_pd_poo_cc( year_start = 2001,
                                         year_end = 2021,
                                         data = pooled_sample_cs_final %>%
                                           mutate( depression = ifelse( depression == "Yes", 1, 0 ),
                                                   anxiety = ifelse( anxiety == "Yes", 1, 0 ),
                                                   stress_related = ifelse( stress_related == "Yes", 1, 0 ) ),
                                         exposure = "sexual_identity_baseline",
                                         outcome_list = outcome_list_1 )

pd_models_list_crude_2 <- cal_pd_poo_cc( year_start = 2005,
                                         year_end = 2021,
                                         data = pooled_sample_cs_final %>%
                                           mutate( used_N06A = ifelse( used_N06A == "Yes", 1, 0 ),
                                                   used_N05B = ifelse( used_N05B == "Yes", 1, 0 ) ),
                                         exposure = "sexual_identity_baseline",
                                         outcome_list = outcome_list_2 )

# adjusted analysis
pd_models_list_adjusted_1 <- cal_pd_poo_cc( year_start = 2001,
                                            year_end = 2021,
                                            data = pooled_sample_cs_final %>%
                                              mutate( depression = ifelse( depression == "Yes", 1, 0 ),
                                                      anxiety = ifelse( anxiety == "Yes", 1, 0 ),
                                                      stress_related = ifelse( stress_related == "Yes", 1, 0 ) ),
                                            exposure = "sexual_identity_baseline",
                                            outcome_list = outcome_list_1,
                                            covariates = "age + sex + country_of_birth" )

pd_models_list_adjusted_2 <- cal_pd_poo_cc( year_start = 2005,
                                            year_end = 2021,
                                            data = pooled_sample_cs_final %>%
                                              mutate( used_N06A = ifelse( used_N06A == "Yes", 1, 0 ),
                                                      used_N05B = ifelse( used_N05B == "Yes", 1, 0 ) ),
                                            exposure = "sexual_identity_baseline",
                                            outcome_list = outcome_list_2,
                                            covariates = "age + sex + country_of_birth" )


pd_crude_cc_1 <- extract_pd_cc(
  model_list = pd_models_list_crude_1,
  exposure_var = "sexual_identity_baseline" ) %>%
  mutate( model_type = "crude" )

pd_crude_cc_2 <- extract_pd_cc(
  model_list = pd_models_list_crude_2,
  exposure_var = "sexual_identity_baseline" ) %>%
  mutate( model_type = "crude" )

pd_adjusted_cc_1 <- extract_pd_cc(
  model_list = pd_models_list_adjusted_1,
  exposure_var = "sexual_identity_baseline" ) %>%
  mutate( model_type = "adjusted" )

pd_adjusted_cc_2 <- extract_pd_cc(
  model_list = pd_models_list_adjusted_2,
  exposure_var = "sexual_identity_baseline" ) %>%
  mutate( model_type = "adjusted" )

pd_poo_cc <- bind_rows( pd_crude_cc_1, pd_crude_cc_2, pd_adjusted_cc_1, pd_adjusted_cc_2 )
writexl::write_xlsx( pd_poo_cc, "results_output/results_cc/pd_poo_cs_cc.xlsx" )
```

### 5. Series of Cohort Analysis
#### 5.1. Complete-case analysis
```{r}
drug_codes <- c( "N06A", "N05B" )

yearly_summaries <- list()

for ( drug_code in drug_codes ) {
  
  for ( yr in 2006:2021 ) {
    
    followup_start <- as.Date( paste0( yr, "-01-01" ) )
    followup_end <- as.Date( "2021-12-31" )
    birth_year_cutoff <- yr - 16

    eligible_dates <- dates_all %>%
      filter( birth_year <= birth_year_cutoff )

    move_in_ids <- eligible_dates %>%
      filter( date < followup_start ) %>%
      arrange( lopnr, date ) %>%
      group_by( lopnr ) %>%
      slice_tail( n = 1 ) %>%
      ungroup() %>%
      filter( event_type == "move-in" ) %>%
      pull( lopnr )

    had_event_ids <- eligible_dates %>%
      filter( lopnr %in% move_in_ids, 
              date >= followup_start, 
              date <= followup_end ) %>%
      pull( lopnr ) %>%
      unique()

    included_year_ids <- setdiff( move_in_ids, had_event_ids )
    
    excluded_year_ids <- eligible_dates %>%
      filter( !lopnr %in% included_year_ids ) %>%
      pull( lopnr ) %>%
      unique()
    
    study_sample <- d_all_selected %>%
      filter( birth_year <= birth_year_cutoff, # 16 years or older
              !lopnr %in% excluded_year_ids )
    
    # ATC data
    atc_yearly_summary <- atc_all %>%
      filter( year >= yr,
              drug_class == drug_code ) %>%
      group_by( lopnr, year ) %>%
      summarise( prescription_count = n(),
                 .groups = "drop" )
    
    all_combos <- expand.grid( lopnr = study_sample$lopnr,
                               year = year( followup_start ):year( followup_end ) )
    
    sample_atc <- all_combos %>%
      left_join( study_sample, by = "lopnr" ) %>%
      left_join( atc_yearly_summary, by = c( "lopnr", "year" ) ) %>%
      mutate(
        prescription_count = replace_na( prescription_count, 0 ),
        prescription_use = as.factor( ifelse( prescription_count > 0, "Yes", "No" ) ),
        age = yr - birth_year,
        age_group = categorize_age_group( age )
        )
    
    yearly_summaries[[ paste0( drug_code, "_", yr ) ]] <- sample_atc
    }
  }

# convert to long format
summary_long_co <- bind_rows( yearly_summaries, .id = "cohort" ) %>%
  select( - age_2005 )
summary( summary_long_co )

N06A_co <- summary_long_co %>%
  filter( grepl( "^N06A", cohort ) ) %>%
  mutate( cohort_year = as.numeric( str_extract( cohort, "\\d{4}$" ) ) ) %>%
  select( -1 ) %>%
  rename(
    prescription_use_N06A = prescription_use,
    prescription_count_N06A = prescription_count
  )

N05B_co <- summary_long_co %>%
  filter( grepl( "^N05B", cohort ) ) %>%
  mutate( cohort_year = as.numeric( str_extract( cohort, "\\d{4}$" ) ) ) %>%
  select( -1 ) %>%
  rename(
    prescription_use_N05B = prescription_use,
    prescription_count_N05B = prescription_count
  )

pooled_data_co <- left_join(
  N06A_co, N05B_co,
  by = c( "cohort_year", "year", "lopnr", "sexual_identity_2010", "sexual_identity_2014", "sexual_identity_2021", "birth_year", "sex", "country_of_birth", "survey_year", "sexual_identity_baseline", "generation", "age", "age_group" ) ) %>%
  mutate( age_sex = interaction( age_group, sex ) ) %>%
  select( cohort_year, lopnr, year, age, age_group, sex, age_sex, birth_year, generation, country_of_birth, sexual_identity_baseline, sexual_identity_2010, sexual_identity_2014, sexual_identity_2021, survey_year, everything() ) %>%
  filter( age >= 16, age <= 59 )

summary( pooled_data_co )

# random check incomplete variables
miss_var_summary( pooled_data_co %>% filter( cohort_year == 2006 ) ) %>% filter( n_miss > 0 ) %>% print( n = Inf )
miss_var_summary( pooled_data_co %>% filter( cohort_year == 2010 ) ) %>% filter( n_miss > 0 ) %>% print( n = Inf )
miss_var_summary( pooled_data_co %>% filter( cohort_year == 2014 ) ) %>% filter( n_miss > 0 ) %>% print( n = Inf )
miss_var_summary( pooled_data_co %>% filter( cohort_year == 2021 ) ) %>% filter( n_miss > 0 ) %>% print( n = Inf )

sample_summary_co <- pooled_data_co %>%
  distinct( cohort_year, lopnr, sexual_identity_baseline ) %>%
  group_by( cohort_year, sexual_identity_baseline ) %>%
  summarise( n = n(), .groups = "drop" ) %>%
  mutate( sexual_identity_baseline = fct_na_value_to_level( sexual_identity_baseline, level = "Missing" ),
          identity_group = case_when( sexual_identity_baseline %in% c( "Heterosexual", "Missing" ) ~ "Heterosexual or Missing",
                                      sexual_identity_baseline %in% c( "Homosexual", "Bisexual", "Other" ) ~ "Sexual Minority" ) ) %>%
  arrange( cohort_year, sexual_identity_baseline )

p_sample_co <- ggplot(
  sample_summary_co,
  aes( x = cohort_year,
       y = n,
       color = sexual_identity_baseline,
       group = sexual_identity_baseline ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2006, 2021 ),
    breaks = seq( 2006, 2021, 3 ),
    expand = expansion( mult = c( 0.05, 0.05 ) ) ) +
  
  scale_color_manual( values = c(
    "Heterosexual" = "#F8766D",
    "Homosexual"   = "#00BFC4",
    "Bisexual"     = "#C77CFF",
    "Other"        = "#7CAE00",
    "Missing"      = "#7f7f7f" ) ) +
  
  labs( x =  "Year of Cohort Sample",
        y = "Number of Participants",
        color = NULL ) +
  
  facet_wrap( ~ identity_group, scales = "free_y" ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_blank(),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  ggh4x::facetted_pos_scales( y = list(
    identity_group == "Heterosexual or Missing" ~ scale_y_continuous( limits = c( 9000, 70000 ), breaks = c( seq( 10000, 70000, 10000 ) ), labels = scales::label_comma(), expand = expansion( mult = c( 0.05, 0 ) ) ),
    identity_group == "Sexual Minority" ~ scale_y_continuous( limits = c( 900, 2000 ), breaks = c( seq( 1000, 2000, 500 ) ), labels = scales::label_comma(), expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( bottom = 'right', gap = 0 )

p_sample_co
ggsave( "results_output/plots_general/p_sample_co.svg", plot = p_sample_co, width = 11, height = 6 )
```

##### 3.3.2. Check overlapping participants
```{r}
# among all participants
lopnr_years_all <- pooled_data_co %>%
  select( cohort_year, lopnr ) %>%
  distinct( cohort_year, lopnr, .keep_all = TRUE ) %>%
  mutate( value = 1 ) %>%
  pivot_wider( names_from = cohort_year, 
               values_from = value, 
               values_fill = 0 ) %>%
  as.data.frame()

pdf( "results_output/plots_general/p_overlap_co_upset_all.pdf", width = 11, height = 9, onefile = FALSE )
upset(
  data = lopnr_years_all,
  nsets = length( colnames( lopnr_years_all )[-1] ),
  sets = colnames( lopnr_years_all )[-1],
  keep.order = TRUE,
  order.by = "freq",
  mainbar.y.label = "Intersection Size",
  sets.x.label = "Sample Size",
  sets.bar.color = "#A32214",
  point.size = 2.5,
  line.size = 1,
  text.scale = c( 1.3, 1.3, 1.3, 1.3, 1.3, 1 ),
  number.angles = 30
)
dev.off()

# among 16-29 years
lopnr_years_1 <- pooled_data_co %>%
  filter( age <= 29 ) %>%
  select( cohort_year, lopnr ) %>%
  distinct( cohort_year, lopnr, .keep_all = TRUE ) %>%
  mutate( value = 1 ) %>%
  pivot_wider( names_from = cohort_year, 
               values_from = value, 
               values_fill = 0 ) %>%
  as.data.frame()

pdf( "results_output/plots_general/p_overlap_co_upset_age_16_29.pdf", width = 11, height = 9, onefile = FALSE )
upset(
  data = lopnr_years_1,
  nsets = length( colnames( lopnr_years_1 )[-1] ),
  sets = colnames( lopnr_years_1 )[-1],
  keep.order = TRUE,
  order.by = "freq",
  mainbar.y.label = "Intersection Size",
  sets.x.label = "Sample Size",
  sets.bar.color = "#A32214",
  point.size = 2.5,
  line.size = 1,
  text.scale = c( 1.3, 1.3, 1.3, 1.3, 1.3, 1 ),
  number.angles = 30
)
dev.off()

lopnr_years_alluvial_1 <- lopnr_years_1 %>% # prepare for alluvial plot
  select( c( seq( 2, 14, by = 2 ), 17 ) ) %>%
  mutate( across( everything(),
                  ~ factor( ifelse( .x == 1, "Included", "Excluded" ),
                            levels = c( "Excluded", "Included" ) ) ) 
  ) %>%
  count( across( everything() ) ) %>%
  rename( number = n ) %>%
  mutate( percent = number / sum( number ) )
sum( lopnr_years_alluvial_1$number ) == nrow( lopnr_years_1 ) # TRUE

lopnr_years_alluvial_long_1 <- to_lodes_form( lopnr_years_alluvial_1, # convert to long format
                                              axes = 1:8,
                                              key = "year", 
                                              value = "inclusion_status", 
                                              id = "cohort", 
                                              diffuse = `2006` ) 

p_overlap_co_alluvial_1 <- 
  ggplot( lopnr_years_alluvial_long_1,
          aes( x = year,
               stratum = inclusion_status, 
               alluvium = cohort,
               y = percent ) ) +
  geom_alluvium( aes( fill = `2006` ), curve_type = "cubic" ) +
  geom_stratum( aes( fill = `2006` ) ) +
  geom_text( stat = "stratum", 
             aes( label = ifelse( after_stat( stratum ) == "Included", "Incl.", "Excl." ) ), 
             family = "Arial", 
             size = 11 / .pt ) +
  scale_fill_manual( values = c( "#00BFC4", "#F8766D" ),
                     breaks = c( "Included", "Excluded" ),
                     na.value = NA ) +
  scale_x_discrete( expand = expansion( mult = c( 0, 0.05 ) ) ) +
  scale_y_continuous( labels = scales::percent, breaks = c( 0, 0.25, 0.5, 0.75, 1 ) ) +
  labs( x = "Year of Cohort Sample", y = "Percentage" ) +
  theme_classic() +
  theme( axis.text = element_text( family = "Arial", size = 11 ),
         axis.title = element_text( family = "Arial", size = 11 ),
         legend.title = element_blank(),
         legend.text = element_text( family = "Arial", size = 10 ), 
         legend.key = element_rect( colour = "white" ),
         legend.position = "bottom",
         axis.ticks.x.bottom = element_blank(),
         axis.line.x.bottom = element_blank()
  )

p_overlap_co_alluvial_1
ggsave( "results_output/plots_general/p_overlap_co_alluvial_age_16_29.svg", plot = p_overlap_co_alluvial_1, width = 12, height = 9 )

# among 30-44 years
lopnr_years_2 <- pooled_data_co %>%
  filter( age >= 30,
          age <= 44 ) %>%
  select( cohort_year, lopnr ) %>%
  distinct( cohort_year, lopnr, .keep_all = TRUE ) %>%
  mutate( value = 1 ) %>%
  pivot_wider( names_from = cohort_year, 
               values_from = value, 
               values_fill = 0 ) %>%
  as.data.frame()

pdf( "results_output/plots_general/p_overlap_co_upset_age_30_44.pdf", width = 11, height = 9, onefile = FALSE )
upset(
  data = lopnr_years_2,
  nsets = length( colnames( lopnr_years_2 )[-1] ),
  sets = colnames( lopnr_years_2 )[-1],
  keep.order = TRUE,
  order.by = "freq",
  mainbar.y.label = "Intersection Size",
  sets.x.label = "Sample Size",
  sets.bar.color = "#A32214",
  point.size = 2.5,
  line.size = 1,
  text.scale = c( 1.3, 1.3, 1.3, 1.3, 1.3, 1 ),
  number.angles = 30
)
dev.off()

lopnr_years_alluvial_2 <- lopnr_years_2 %>% # prepare for alluvial plot
  select( c( seq( 2, 14, by = 2 ), 17 ) ) %>%
  mutate( across( everything(),
                  ~ factor( ifelse( .x == 1, "Included", "Excluded" ),
                            levels = c( "Excluded", "Included" ) ) ) 
  ) %>%
  count( across( everything() ) ) %>%
  rename( number = n ) %>%
  mutate( percent = number / sum( number ) )
sum( lopnr_years_alluvial_2$number ) == nrow( lopnr_years_2 ) # TRUE

lopnr_years_alluvial_long_2 <- to_lodes_form( lopnr_years_alluvial_2, # convert to long format
                                              axes = 1:8, 
                                              key = "year", 
                                              value = "inclusion_status", 
                                              id = "cohort", 
                                              diffuse = `2006` ) 

p_overlap_co_alluvial_2 <- 
  ggplot( lopnr_years_alluvial_long_2,
          aes( x = year,
               stratum = inclusion_status, 
               alluvium = cohort,
               y = percent ) ) +
  geom_alluvium( aes( fill = `2006` ), curve_type = "cubic" ) +
  geom_stratum( aes( fill = `2006` ) ) +
  geom_text( stat = "stratum", 
             aes( label = ifelse( after_stat( stratum ) == "Included", "Incl.", "Excl." ) ), 
             family = "Arial", 
             size = 11 / .pt ) +
  scale_fill_manual( values = c( "#00BFC4", "#F8766D" ),
                     breaks = c( "Included", "Excluded" ),
                     na.value = NA ) +
  scale_x_discrete( expand = expansion( mult = c( 0, 0.05 ) ) ) +
  scale_y_continuous( labels = scales::percent, breaks = c( 0, 0.25, 0.5, 0.75, 1 ) ) +
  labs( x = "Year of Cohort Sample", y = "Percentage" ) +
  theme_classic() +
  theme( axis.text = element_text( family = "Arial", size = 11 ),
         axis.title = element_text( family = "Arial", size = 11 ),
         legend.title = element_blank(),
         legend.text = element_text( family = "Arial", size = 10 ), 
         legend.key = element_rect( colour = "white" ),
         legend.position = "bottom",
         axis.ticks.x.bottom = element_blank(),
         axis.line.x.bottom = element_blank()
  )

p_overlap_co_alluvial_2
ggsave( "results_output/plots_general/p_overlap_co_alluvial_age_30_44.svg", plot = p_overlap_co_alluvial_2, width = 12, height = 9 )

# among 45-59 years
lopnr_years_3 <- pooled_data_co %>%
  filter( age >= 45,
          age <= 59 ) %>%
  select( cohort_year, lopnr ) %>%
  distinct( cohort_year, lopnr, .keep_all = TRUE ) %>%
  mutate( value = 1 ) %>%
  pivot_wider( names_from = cohort_year, 
               values_from = value, 
               values_fill = 0 ) %>%
  as.data.frame()

pdf( "results_output/plots_general/p_overlap_co_upset_age_45_59.pdf", width = 11, height = 9, onefile = FALSE )
upset(
  data = lopnr_years_3,
  nsets = length( colnames( lopnr_years_3 )[-1] ),
  sets = colnames( lopnr_years_3 )[-1],
  keep.order = TRUE,
  order.by = "freq",
  mainbar.y.label = "Intersection Size",
  sets.x.label = "Sample Size",
  sets.bar.color = "#A32214",
  point.size = 2.5,
  line.size = 1,
  text.scale = c( 1.3, 1.3, 1.3, 1.3, 1.3, 1 ),
  number.angles = 30
)
dev.off()

lopnr_years_alluvial_3 <- lopnr_years_3 %>% # prepare for alluvial plot
  select( c( seq( 2, 14, by = 2 ), 17 ) ) %>%
  mutate( across( everything(),
                  ~ factor( ifelse( .x == 1, "Included", "Excluded" ),
                            levels = c( "Excluded", "Included" ) ) ) 
  ) %>%
  count( across( everything() ) ) %>%
  rename( number = n ) %>%
  mutate( percent = number / sum( number ) )
sum( lopnr_years_alluvial_3$number ) == nrow( lopnr_years_3 ) # TRUE

lopnr_years_alluvial_long_3 <- to_lodes_form( lopnr_years_alluvial_3, # convert to long format
                                              axes = 1:8,
                                              key = "year", 
                                              value = "inclusion_status", 
                                              id = "cohort", 
                                              diffuse = `2006` ) 

p_overlap_co_alluvial_3 <- 
  ggplot( lopnr_years_alluvial_long_3,
          aes( x = year,
               stratum = inclusion_status, 
               alluvium = cohort,
               y = percent ) ) +
  geom_alluvium( aes( fill = `2006` ), curve_type = "cubic" ) +
  geom_stratum( aes( fill = `2006` ) ) +
  geom_text( stat = "stratum", 
             aes( label = ifelse( after_stat( stratum ) == "Included", "Incl.", "Excl." ) ), 
             family = "Arial", 
             size = 11 / .pt ) +
  scale_fill_manual( values = c( "#00BFC4", "#F8766D" ),
                     breaks = c( "Included", "Excluded" ),
                     na.value = NA ) +
  scale_x_discrete( expand = expansion( mult = c( 0, 0.05 ) ) ) +
  scale_y_continuous( labels = scales::percent, breaks = c( 0, 0.25, 0.5, 0.75, 1 ) ) +
  labs( x = "Year of Cohort Sample", y = "Percentage" ) +
  theme_classic() +
  theme( axis.text = element_text( family = "Arial", size = 11 ),
         axis.title = element_text( family = "Arial", size = 11 ),
         legend.title = element_blank(),
         legend.text = element_text( family = "Arial", size = 10 ), 
         legend.key = element_rect( colour = "white" ),
         legend.position = "bottom",
         axis.ticks.x.bottom = element_blank(),
         axis.line.x.bottom = element_blank()
  )

p_overlap_co_alluvial_3
ggsave( "results_output/plots_general/p_overlap_co_alluvial_age_45_59.svg", plot = p_overlap_co_alluvial_3, width = 12, height = 9 )
```

##### 3.3.3. Complete-case analysis
```{r}
outcome_list <- list(
  list( variable = "prescription_use_N06A", condition = "Yes", name = "antidepressant_use" ),
  list( variable = "prescription_use_N05B", condition = "Yes", name = "anxiolytic_use" )
  )

########## Prevalence ##########

# by sexual identity
results_list <- lapply( sort( unique( pooled_data_co$cohort_year ) ), function( coh_year ) {
  
  results <- cal_prev_poo_cc( year_start = coh_year,
                              year_end = 2021,
                              data = pooled_data_co %>% filter( cohort_year == coh_year ),
                              variables_list = outcome_list,
                              group_var = "sexual_identity_baseline" )
  
  bind_rows( results ) %>% mutate( cohort_year = coh_year )
  }
  )

prevalence_poo <- bind_rows( results_list )
writexl::write_xlsx( prevalence_poo, "results_output/results_cc/prevalence_poo_co_cc.xlsx" )

# by sex
results_list_by_sex <- lapply( sort( unique( pooled_data_co$cohort_year ) ), function( coh_year ) {
  
  results <- cal_prev_poo_cc( year_start = coh_year,
                              year_end = 2021,
                              data = pooled_data_co %>% filter( cohort_year == coh_year ),
                              variables_list = outcome_list,
                              group_var = "sexual_identity_baseline + sex",
                              subgroup = TRUE )
  
  bind_rows( results ) %>% mutate( cohort_year = coh_year )
  }
  )

prevalence_poo_by_sex <- bind_rows( results_list_by_sex )
writexl::write_xlsx( prevalence_poo_by_sex, "results_output/results_cc/prevalence_poo_co_by_sex_cc.xlsx" )

# by age
results_list_by_age <- lapply( sort( unique( pooled_data_co$cohort_year ) ), function( coh_year ) {
  
  results <- cal_prev_poo_cc( year_start = coh_year,
                              year_end = 2021,
                              data = pooled_data_co %>% filter( cohort_year == coh_year ),
                              variables_list = outcome_list,
                              group_var = "sexual_identity_baseline + age_group",
                              subgroup = TRUE )
  
  bind_rows( results ) %>% mutate( cohort_year = coh_year )
  }
  )

prevalence_poo_by_age <- bind_rows( results_list_by_age )
writexl::write_xlsx( prevalence_poo_by_age, "results_output/results_cc/prevalence_poo_co_by_age_cc.xlsx" )

# by age and sex
results_list_by_age_sex <- lapply( sort( unique( pooled_data_co$cohort_year ) ), function( coh_year ) {
  
  results <- cal_prev_poo_cc( year_start = coh_year,
                              year_end = 2021,
                              data = pooled_data_co %>% filter( cohort_year == coh_year ),
                              variables_list = outcome_list,
                              group_var = "sexual_identity_baseline + age_sex",
                              subgroup = TRUE )
  
  bind_rows( results ) %>% mutate( cohort_year = coh_year )
  }
  )

prevalence_poo_by_age_sex <- bind_rows( results_list_by_age_sex )
writexl::write_xlsx( prevalence_poo_by_age_sex, "results_output/results_cc/prevalence_poo_co_by_age_sex_cc.xlsx" )

# by generation
results_list_by_generation <- lapply( sort( unique( pooled_data_co$cohort_year ) ), function( coh_year ) {
  
  results <- cal_prev_poo_cc( year_start = coh_year,
                              year_end = 2021,
                              data = pooled_data_co %>% filter( cohort_year == coh_year ),
                              variables_list = outcome_list,
                              group_var = "sexual_identity_baseline + generation",
                              subgroup = TRUE )
  
  bind_rows( results ) %>% mutate( cohort_year = coh_year )
  }
  )

prevalence_poo_by_generation <- bind_rows( results_list_by_generation )
writexl::write_xlsx( prevalence_poo_by_generation, "results_output/results_cc/prevalence_poo_co_by_generation_cc.xlsx" )
```