---
title: "Summary plots of multiple imputation analyses among 16-29 years"
author: Willi Zhang
email: willi.zhang@ki.se
output: html_notebook
editor_options: 
  chunk_output_type: console
---

# Note: For SPHC-B 2002 and 2006, complete-case analyses were plotted (see Supplement 2 for reasons).

### 1. Load Packages and Color Settings
```{r}
library(forestploter)
library(grid)
library(readxl)
library(here)
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(colorspace)
library(naniar)
library(ggh4x)
library(scales)
library(lemon)
library(stringr)
library(patchwork)

exposure_colors <- c(
  "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
  "Bisexual_Adjusted"   = "#C77CFF",
  "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ),
  "Homosexual_Adjusted" = "#00BFC4"
  )

exposure_labels <- c(
  "Bisexual_Crude"      = "Bisexual (Crude)",
  "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
  "Homosexual_Crude"    = "Homosexual (Crude)",
  "Homosexual_Adjusted" = "Homosexual (Adjusted)"
  )
```

### 2. Prepare Data
#### 2.1. By sexual identity
```{r}
##### prevalence #####

# survey samples
prevalence_2002_by_identity_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2002_by_identity_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -sexual_identity,
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

prevalence_2006_by_identity_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2006_by_identity_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -sexual_identity,
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

overall_prevalence_2010_imp <- read_xlsx( here( "results_output/results_mi/overall_prevalence_2010_imp.xlsx" ) ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

overall_prevalence_2014_imp <- read_xlsx( here( "results_output/results_mi/overall_prevalence_2014_imp.xlsx" ) ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

overall_prevalence_2021_imp <- read_xlsx( here( "results_output/results_mi/overall_prevalence_2021_imp.xlsx" ) ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

# cross-sectional samples
prevalence_poo_cs_imp <- read_xlsx( here( "results_output/results_mi/prevalence_poo_cs_imp.xlsx" ) ) %>%
  mutate( sample_type = "CS",
          outcome = recode( 
            outcome,
            antidepressant_use = "antidepressant",
            anxiolytic_use = "anxiolytic"
            ) 
          )

str( prevalence_poo_cs_imp )

# merge prevalence data
setequal( colnames( prevalence_2002_by_identity_cc ), colnames( overall_prevalence_2010_imp ) )
setequal( colnames( prevalence_2002_by_identity_cc ), colnames( prevalence_poo_cs_imp ) )

prevalence_imp <- bind_rows( 
  prevalence_2002_by_identity_cc,
  prevalence_2006_by_identity_cc,
  overall_prevalence_2010_imp,
  overall_prevalence_2014_imp,
  overall_prevalence_2021_imp,
  prevalence_poo_cs_imp
  ) %>%
  filter( 
    sexual_identity != "Other"
    ) %>%
  mutate( 
    sexual_identity = factor( 
      sexual_identity,
      levels = c( "Heterosexual", "Homosexual", "Bisexual" ) 
      ),
    
    outcome = as.factor( outcome ),
    sample_type = as.factor( sample_type )
    )

summary( prevalence_imp )


##### prevalence ratio and difference #####

# prevalence ratio
pr_2002_cc <- read_xlsx( here( 'results_output/results_cc/pr_2002_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_2006_cc <- read_xlsx( here( 'results_output/results_cc/pr_2006_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_2010_imp <- read_xlsx( here( 'results_output/results_mi/pr_2010_imp.xlsx' ) ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_2014_imp <- read_xlsx( here( 'results_output/results_mi/pr_2014_imp.xlsx' ) ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_2021_imp <- read_xlsx( here( 'results_output/results_mi/pr_2021_imp.xlsx' ) ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pr_poo_cs_imp.xlsx' ) ) %>%
  mutate( 
    estimate_type = "Prevalence Ratio",
    sample_type = "CS",
    outcome = recode( outcome,
                      antidepressant_use = "antidepressant",
                      anxiolytic_use = "anxiolytic"
                      ) 
    )

setequal( colnames( pr_2002_cc ), colnames( pr_2010_imp ) )
setequal( colnames( pr_2002_cc ), colnames( pr_poo_cs_imp ) )

# prevalence difference
pd_2002_cc <- read_xlsx( here( 'results_output/results_cc/pd_2002_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    across(
      c( point_estimate, lower_ci, upper_ci ),
      ~ .x * 100
      ),
    sample_type = "survey",
    estimate_type = "Prevalence Difference"
    )

pd_2006_cc <- read_xlsx( here( 'results_output/results_cc/pd_2006_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    across(
      c( point_estimate, lower_ci, upper_ci ),
      ~ .x * 100
      ),
    sample_type = "survey",
    estimate_type = "Prevalence Difference"
    )

pd_2010_imp <- read_xlsx( here( 'results_output/results_mi/pd_2010_imp.xlsx' ) ) %>%
  mutate( 
    sample_type = "survey",
    estimate_type = "Prevalence Difference" 
    )

pd_2014_imp <- read_xlsx( here( 'results_output/results_mi/pd_2014_imp.xlsx' ) ) %>%
  mutate( 
    sample_type = "survey",
    estimate_type = "Prevalence Difference" 
    )

pd_2021_imp <- read_xlsx( here( 'results_output/results_mi/pd_2021_imp.xlsx' ) ) %>%
  mutate( 
    sample_type = "survey",
    estimate_type = "Prevalence Difference" 
    )

pd_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pd_poo_cs_imp.xlsx' ) ) %>%
  mutate( 
    estimate_type = "Prevalence Difference",
    sample_type = "CS",
    outcome = recode( 
      outcome,
      antidepressant_use = "antidepressant",
      anxiolytic_use = "anxiolytic"
      ) 
    )

setequal( colnames( pd_2002_cc ), colnames( pd_2010_imp ) )
setequal( colnames( pd_2002_cc ), colnames( pd_poo_cs_imp ) )

# merge prevalence difference and ratio
setequal( colnames( pr_2002_cc ), colnames( pd_2002_cc ) )

pr_pd_imp <- bind_rows( 
  pr_2002_cc,
  pr_2006_cc,
  pr_2010_imp,
  pr_2014_imp,
  pr_2021_imp,
  pr_poo_cs_imp,
  
  pd_2002_cc,
  pd_2006_cc,
  pd_2010_imp,
  pd_2014_imp,
  pd_2021_imp,
  pd_poo_cs_imp 
  ) %>%
  filter( 
    sexual_identity != "Other" 
    ) %>%
  mutate( 
    outcome = as.factor( outcome ),
    year = as.integer( year ),
    sample_type = as.factor( sample_type ),
    estimate_type = factor( estimate_type, levels = c( "Prevalence Difference", "Prevalence Ratio" ) ),
    sexual_identity = as.factor( sexual_identity ),
    model_type = recode_factor( model_type, "crude" = "Crude", "adjusted" = "Adjusted" ),
    exposure_model = interaction( sexual_identity, model_type, sep = "_" ),
    exposure_model = factor( 
      exposure_model, 
      levels = c(
        "Bisexual_Crude",
        "Homosexual_Crude",
        "Bisexual_Adjusted",
        "Homosexual_Adjusted" 
        ) 
      ) 
    )
summary( pr_pd_imp )

pr_pd_imp <- pr_pd_imp %>%
  mutate(
    across(
      c( point_estimate, lower_ci, upper_ci ),
      ~ if_else(
        (
          outcome == "anxiety" &
          year == 2014 &
          sexual_identity == "Homosexual" &
          sample_type == "survey"
        ) |
        (
          outcome == "stress_related" &
          year == 2006 &
          sexual_identity == "Bisexual" &
          sample_type == "survey"
        ),
        NA_real_,
        .
      )
    ),
    
    across(
      c( lower_ci, upper_ci ),
      ~ if_else(
        sample_type == "CS",
        NA_real_,
        .
        )
      )
    )
```

#### 2.2. By sex
```{r}
##### prevalence #####

# survey samples
prevalence_2002_by_sex_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2002_by_sex_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

prevalence_2006_by_sex_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2006_by_sex_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

prevalence_2010_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_2010_by_sex_imp.xlsx" ) ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

prevalence_2014_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_2014_by_sex_imp.xlsx" ) ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

prevalence_2021_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_2021_by_sex_imp.xlsx" ) ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

# cross-sectional samples
prevalence_poo_cs_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_poo_cs_by_sex_imp.xlsx" ) ) %>%
  mutate( sample_type = "CS",
          outcome = recode( 
            outcome,
            antidepressant_use = "antidepressant",
            anxiolytic_use = "anxiolytic"
            ) 
          )

str( prevalence_poo_cs_by_sex_imp )

# merge prevalence data
setequal( colnames( prevalence_2002_by_sex_cc ), colnames( prevalence_2010_by_sex_imp ) )
setequal( colnames( prevalence_2002_by_sex_cc ), colnames( prevalence_poo_cs_by_sex_imp ) )

prevalence_by_sex_imp <- bind_rows( 
  prevalence_2002_by_sex_cc,
  prevalence_2006_by_sex_cc,
  prevalence_2010_by_sex_imp,
  prevalence_2014_by_sex_imp,
  prevalence_2021_by_sex_imp,
  prevalence_poo_cs_by_sex_imp
  ) %>%
  filter( 
    sexual_identity != "Other"
    ) %>%
  mutate( 
    sexual_identity = factor( 
      sexual_identity,
      levels = c( "Heterosexual", "Homosexual", "Bisexual" ) 
      ),
    outcome = as.factor( outcome ),
    sample_type = as.factor( sample_type )
    )

summary( prevalence_by_sex_imp )


##### prevalence ratio and difference #####

# prevalence ratio
pr_female_2002_cc <- read_xlsx( here( 'results_output/results_cc/pr_female_2002_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_male_2002_cc <- read_xlsx( here( 'results_output/results_cc/pr_male_2002_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_female_2006_cc <- read_xlsx( here( 'results_output/results_cc/pr_female_2006_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_male_2006_cc <- read_xlsx( here( 'results_output/results_cc/pr_male_2006_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_2010_by_sex_imp <- read_xlsx( here( 'results_output/results_mi/pr_2010_by_sex_imp.xlsx' ) ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_2014_by_sex_imp <- read_xlsx( here( 'results_output/results_mi/pr_2014_by_sex_imp.xlsx' ) ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_2021_by_sex_imp <- read_xlsx( here( 'results_output/results_mi/pr_2021_by_sex_imp.xlsx' ) ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

setequal( colnames( pr_female_2002_cc ), colnames( pr_2021_by_sex_imp ) )

# prevalence difference
pd_female_2002_cc <- read_xlsx( here( 'results_output/results_cc/pd_female_2002_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    across(
      c( point_estimate, lower_ci, upper_ci ),
      ~ .x * 100
      ),
    sample_type = "survey",
    estimate_type = "Prevalence Difference"
    )

pd_male_2002_cc <- read_xlsx( here( 'results_output/results_cc/pd_male_2002_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    across(
      c( point_estimate, lower_ci, upper_ci ),
      ~ .x * 100
      ),
    sample_type = "survey",
    estimate_type = "Prevalence Difference"
    )

pd_female_2006_cc <- read_xlsx( here( 'results_output/results_cc/pd_female_2006_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    across(
      c( point_estimate, lower_ci, upper_ci ),
      ~ .x * 100
      ),
    sample_type = "survey",
    estimate_type = "Prevalence Difference"
    )

pd_male_2006_cc <- read_xlsx( here( 'results_output/results_cc/pd_male_2006_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    across(
      c( point_estimate, lower_ci, upper_ci ),
      ~ .x * 100
      ),
    sample_type = "survey",
    estimate_type = "Prevalence Difference"
    )

pd_2010_by_sex_imp <- read_xlsx( here( 'results_output/results_mi/pd_2010_by_sex_imp.xlsx' ) ) %>%
  mutate( 
    sample_type = "survey",
    estimate_type = "Prevalence Difference" 
    )

pd_2014_by_sex_imp <- read_xlsx( here( 'results_output/results_mi/pd_2014_by_sex_imp.xlsx' ) ) %>%
  mutate( 
    sample_type = "survey",
    estimate_type = "Prevalence Difference" 
    )

pd_2021_by_sex_imp <- read_xlsx( here( 'results_output/results_mi/pd_2021_by_sex_imp.xlsx' ) ) %>%
  mutate( 
    sample_type = "survey",
    estimate_type = "Prevalence Difference" 
    )

setequal( colnames( pd_female_2002_cc ), colnames( pd_2021_by_sex_imp ) )

# merge prevalence difference and ratio
setequal( colnames( pr_female_2002_cc ), colnames( pd_female_2002_cc ) )

pr_pd_by_sex_imp <- bind_rows( 
  pr_female_2002_cc,
  pr_male_2002_cc,
  pr_female_2006_cc,
  pr_male_2006_cc,
  pr_2010_by_sex_imp,
  pr_2014_by_sex_imp,
  pr_2021_by_sex_imp,

  pd_female_2002_cc,
  pd_male_2002_cc,
  pd_female_2006_cc,
  pd_male_2006_cc,
  pd_2010_by_sex_imp,
  pd_2014_by_sex_imp,
  pd_2021_by_sex_imp 
  ) %>%
  filter( 
    sexual_identity != "Other",
    outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts", "antidepressant" )
    ) %>%
  mutate( 
    outcome = as.factor( outcome ),
    year = as.factor( year ),
    sample_type = as.factor( sample_type ),
    estimate_type = factor( estimate_type, levels = c( "Prevalence Difference", "Prevalence Ratio" ) ),
    sexual_identity = as.factor( sexual_identity ),
    model_type = recode_factor( model_type, "crude" = "Crude", "adjusted" = "Adjusted" ),
    sex = factor( sex, levels = c( "Female", "Male" ) ),
    exposure_model = interaction( sexual_identity, model_type, sep = "_" ),
    exposure_model = factor( 
      exposure_model, 
      levels = c(
        "Bisexual_Crude",
        "Homosexual_Crude",
        "Bisexual_Adjusted",
        "Homosexual_Adjusted" 
        ) 
      ) 
    )
summary( pr_pd_by_sex_imp )

pr_pd_by_sex_imp <- pr_pd_by_sex_imp %>%
  mutate(
    across(
      c( point_estimate, lower_ci, upper_ci ),
      ~ ifelse(
        outcome == "suicide_attempts" &
          sex == "Male" &
          (
            ( year == 2002 & sexual_identity == "Bisexual" ) | # four PR data points were not estimable due to zero events
            ( year == 2014 & sexual_identity == "Homosexual" )
            ),
        NA_real_,
          .
        )
      )
    )

# sanity check
pr_pd_by_sex_imp %>%
  filter( is.na( point_estimate ) )
summary( pr_pd_by_sex_imp )
```

### 3. Psychological Distress
#### 3.1. Prevalence by sexual identity
```{r}
plot_data <- prevalence_imp %>% 
  filter( 
    outcome == "psychological_distress"
    ) %>%
  mutate(
    year = as.factor( year )
  )

summary( plot_data )

p_prevalence <- ggplot( 
  plot_data,
  
  aes( 
    x = year, 
    y = point_estimate, 
    color = sexual_identity, 
    group = sexual_identity 
    ) 
  ) +
  
  geom_errorbar( 
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.14 
    ) +
  
  geom_line( 
    linewidth = 0.8 
    ) +
  
  geom_point( 
    size = 2 
    ) +
  
  scale_x_discrete( 
    expand = expansion( 
      mult = c( 
        0.08, 0.05 
        ) 
      ) 
    ) +
  
# plot_data %>% 
#   group_by( outcome ) %>%
#   summarise(
#     min_lower_ci = min( lower_ci ),
#     max_upper_ci = max( upper_ci )
#   )
  
  scale_y_continuous( 
    limits = c( 0, 0.75 ),
    breaks = seq( 
      0, 0.75, 0.15 
      ),
    labels = scales::percent_format( 
      accuracy = 1 
      ),
    expand = expansion( 
      mult = c( 
        0.05, 0 
        ) 
      ) 
    ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  labs(
    x = "Survey Year",
    y = "Prevalence (95% CI)",
    color = NULL 
    ) +
  
  theme_classic() +
  theme(
    axis.title = element_text( 
      family = "Arial", size = 11 
      ),
    axis.text = element_text( 
      family = "Arial", size = 11 
      ),
    legend.title = element_blank(),
    legend.text = element_text( 
      family = "Arial", size = 10 
      ),
    legend.position = "bottom" 
    ) +
  
  coord_capped_cart( 
    left = 'both', 
    bottom = 'both' 
    ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_psychological_distress_imp.svg", plot = p_prevalence, width = 5, height = 5 )
```

#### 3.2. Prevalence by sex
```{r}
plot_data <- prevalence_by_sex_imp %>% 
  filter( 
    outcome == "psychological_distress"
    ) %>%
  mutate(
    year = as.factor( year ),
    sex = factor(
      sex,
      levels = c( "Female", "Male" )
    )
  )

summary( plot_data )

p_prevalence <- ggplot( 
  plot_data,
  
  aes( 
    x = year, 
    y = point_estimate, 
    color = sexual_identity, 
    group = sexual_identity 
    ) 
  ) +
  
  geom_errorbar( 
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.14 
    ) +
  
  geom_line( 
    linewidth = 0.8 
    ) +
  
  geom_point( 
    size = 2 
    ) +
  
  scale_x_discrete( 
    expand = expansion( 
      mult = c( 0.08, 0.05 ) 
      ) 
    ) +
  
  scale_y_continuous( 
    limits = c( 0, 1 ),
    breaks = seq( 0, 1, 0.2 ),
    labels = scales::percent_format( accuracy = 1 ),
    expand = expansion( 
      mult = c( 0.05, 0 ) 
      ) 
    ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" 
      ) 
    ) +
  
  labs(
    x = "Survey Year",
    y = "Prevalence of Psychological Distress (95% CI)",
    color = NULL 
    ) +
  
  facet_wrap(
    ~ sex,
    ncol = 2,
    scales = "free_x" 
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom"
    ) +
  
  coord_capped_cart( 
    left = 'both', 
    bottom = 'both' 
    ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_psychological_distress_by_sex_imp.svg", plot = p_prevalence, width = 9, height = 6 )
```

#### 3.3. PR/PD by sexual identity
```{r}
plot_data <- pr_pd_imp %>%
  filter( outcome == "psychological_distress" ) %>%
    mutate(
    year = as.factor( year )
  )

summary( plot_data )

plot_data %>%
  filter( estimate_type == "Prevalence Difference" ) %>%
  summary()

plot_data %>% 
  filter( estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd <- ggplot(
  plot_data,
  
  aes( 
    x = year,
    y = point_estimate,
    color = exposure_model,
    group = exposure_model 
    ) 
  ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Ratio" 
      ),
    aes( 
      yintercept = 1 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Difference" 
      ),
    aes( 
      yintercept = 0 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_errorbar( 
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.14
    ) +
  
  geom_line( 
    linewidth = 0.8
    ) +
  
  geom_point(
    shape = 15,
    size = 2.5
    ) +
  
  scale_color_manual( 
    values = exposure_colors,
    labels = exposure_labels
    ) +
  
  labs( 
    x = "Survey Year",
    y = "Association Estimate (95% CI)",
    color = NULL
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom"
    ) +
  
  facet_wrap(
    ~ estimate_type,
    ncol = 2,
    scales = "free" 
    ) +
  
  scale_x_discrete(
    limits = c( "2021", "2014", "2010", "2006", "2002" ),
    expand = expansion( 
      mult = c( 0.05, 0.05 ) 
      )
    ) +
  
  # plot_data %>%
  # group_by( estimate_type ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci ),
  #   max_upper_ci = max( upper_ci )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( 
          limits = c( 0.5, 3 ),
          breaks = seq( 0.5, 3, 0.5 ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( 
          limits = c( -20, 40 ),
          breaks = seq( -20, 40, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_flip()
  
p_pr_pd
ggsave( "results_output/plots_mi/p_pr_pd_psychological_distress_imp.svg", plot = p_pr_pd, width = 9, height = 6 )
```

### 4. Suicidal Thoughts and Attempts
#### 4.1. Prevalence by sexual identity
```{r}
plot_data <- prevalence_imp %>% 
  filter( 
    outcome %in% c( "suicidal_thoughts", "suicide_attempts" )
    ) %>%
  mutate(
    year = as.factor( year ),
    lower_ci = if_else( 
      lower_ci < 0, 
      0, 
      lower_ci 
      )
    )

summary( plot_data )

p_prevalence <- ggplot( 
  plot_data,
  
  aes( 
    x = year, 
    y = point_estimate, 
    color = sexual_identity, 
    group = sexual_identity 
    ) 
  ) +
  
  geom_errorbar( 
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.14 
    ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 2 ) +
  
  scale_x_discrete( 
    expand = expansion( 
      mult = c( 0.08, 0.05 ) 
      ) 
    ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" 
      ) 
    ) +
  
  labs(
    x = "Survey Year",
    y = "Prevalence (95% CI)",
    color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom"
    ) +
  
  facet_wrap(
    ~ outcome,
    ncol = 2,
    scales = "free",
    labeller = labeller(
      outcome = c(
        "suicidal_thoughts" = "Suicidal Thoughts",
        "suicide_attempts" = "Suicide Attempts" 
        ) 
      )
    ) +
  
  # plot_data %>%
  # group_by( outcome ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci ),
  #   max_upper_ci = max( upper_ci )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      outcome == "suicidal_thoughts" ~ 
        scale_y_continuous( 
          limits = c( 0, 0.75 ),
          breaks = seq( 0, 0.75, 0.15 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion( 
            mult = c( 0.05, 0.01 ) 
            )
          ),
      
      outcome == "suicide_attempts" ~ 
        scale_y_continuous( 
          limits = c( 0, 0.4 ),
          breaks = seq( 0, 0.4, 0.1 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion( 
            mult = c( 0.05, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_capped_cart( 
    left = 'both', 
    bottom = 'both' 
    ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_suicide_imp.svg", plot = p_prevalence, width = 9.5, height = 5 )
```

#### 4.2. Prevalence by sex
```{r}
plot_data <- prevalence_by_sex_imp %>% 
  filter( 
    outcome %in% c( "suicidal_thoughts", "suicide_attempts" )
    ) %>%
  mutate(
    year = as.factor( year ),
    sex = factor(
      sex,
      levels = c( "Female", "Male" )
    ),
    
    lower_ci = if_else( 
      lower_ci < 0, 
      0, 
      lower_ci 
      ),
    
    across(
      c( lower_ci, upper_ci ),
      ~ ifelse(
        outcome == "suicide_attempts" &
          year == 2014 & 
          sexual_identity == "Homosexual" &
          sex == "Male",
        NA_real_,
          .
        )
      )
    )

summary( plot_data )

p_prevalence <- ggplot( 
  plot_data,
  
  aes( 
    x = year, 
    y = point_estimate, 
    color = sexual_identity, 
    group = sexual_identity 
    ) 
  ) +
  
  geom_errorbar( 
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.14 
    ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 2 ) +
  
  scale_x_discrete( 
    expand = expansion( 
      mult = c( 0.08, 0.05 ) 
      ) 
    ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" 
      ) 
    ) +
  
  labs(
    x = "Survey Year",
    y = "Prevalence (95% CI)",
    color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom"
    ) +
  
  facet_grid(
    outcome ~ sex,
    scales = "free",
    switch = "y",
    labeller = labeller(
      outcome = c(
        "suicidal_thoughts" = "Suicidal Thoughts",
        "suicide_attempts" = "Suicide Attempts"
        )
      )
    ) +
  
  # plot_data %>%
  # group_by( outcome ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci, na.rm = TRUE ),
  #   max_upper_ci = max( upper_ci, na.rm = TRUE )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      outcome == "suicidal_thoughts" ~ 
        scale_y_continuous( 
          limits = c( 0, 1 ),
          breaks = seq( 0, 1, 0.2 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion( 
            mult = c( 0.05, 0.01 ) 
            )
          ),
      
      outcome == "suicide_attempts" ~ 
        scale_y_continuous( 
          limits = c( 0, 0.5 ),
          breaks = seq( 0, 0.5, 0.1 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion( 
            mult = c( 0.05, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_capped_cart( 
    left = 'both', 
    bottom = 'both' 
    ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_suicide_by_sex_imp.svg", plot = p_prevalence, width = 9, height = 7 )
```

#### 4.3. PR/PD by sexual identity
```{r}
# suicidal thoughts
plot_data <- pr_pd_imp %>%
  filter( 
    outcome == "suicidal_thoughts"
    ) %>%
  mutate(
    year = as.factor( year )
  )

summary( plot_data )

plot_data %>%
  filter( 
    estimate_type == "Prevalence Difference" 
    ) %>%
  summary()

plot_data %>% 
  filter( 
    estimate_type == "Prevalence Ratio" 
    ) %>%
  summary()

p_pr_pd_thought <- ggplot(
  plot_data,
  
  aes( 
    x = year,
    y = point_estimate,
    color = exposure_model,
    group = exposure_model 
    ) 
  ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Ratio" 
      ),
    aes( 
      yintercept = 1 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Difference" 
      ),
    aes( 
      yintercept = 0 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_errorbar( 
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.14
    ) +
  
  geom_line( 
    linewidth = 0.8
    ) +
  
  geom_point(
    shape = 15,
    size = 2.5
    ) +
  
  scale_color_manual( 
    values = exposure_colors,
    labels = exposure_labels
    ) +
  
  labs( 
    x = "Survey Year",
    y = "Association Estimate (95% CI)",
    title = "Suicidal Thoughts",
    color = NULL
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom",
    plot.title = element_text( family = "Arial", size = 12, hjust = 0.5 )
    ) +
  
  facet_wrap(
    ~ estimate_type,
    ncol = 2,
    scales = "free" 
    ) +
  
  scale_x_discrete(
    limits = c( "2021", "2014", "2010", "2006", "2002" ),
    expand = expansion( 
      mult = c( 0.05, 0.05 ) 
      )
    ) +
  
  # plot_data %>%
  # group_by( estimate_type ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci ),
  #   max_upper_ci = max( upper_ci )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( 
          limits = c( 0.5, 3.5 ),
          breaks = seq( 0.5, 3.5, 0.5 ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( 
          limits = c( -10, 40 ),
          breaks = seq( -10, 40, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_flip()
  
p_pr_pd_thought

# suicide attempts
plot_data <- pr_pd_imp %>%
  filter( 
    outcome == "suicide_attempts"
    ) %>%
  mutate(
    year = as.factor( year )
  )

summary( plot_data )

plot_data %>%
  filter( 
    estimate_type == "Prevalence Difference" 
    ) %>%
  summary()

plot_data %>% 
  filter( 
    estimate_type == "Prevalence Ratio" 
    ) %>%
  summary()

p_pr_pd_attempt <- ggplot(
  plot_data,
  
  aes( 
    x = year,
    y = point_estimate,
    color = exposure_model,
    group = exposure_model 
    ) 
  ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Ratio" 
      ),
    aes( 
      yintercept = 1 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Difference" 
      ),
    aes( 
      yintercept = 0 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_errorbar( 
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.14
    ) +
  
  geom_line( 
    linewidth = 0.8
    ) +
  
  geom_point(
    shape = 15,
    size = 2.5
    ) +
  
  scale_color_manual( 
    values = exposure_colors,
    labels = exposure_labels
    ) +
  
  labs( 
    x = "Survey Year",
    y = "Association Estimate (95% CI)",
    title = "Suicide Attempts",
    color = NULL
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom",
    plot.title = element_text( family = "Arial", size = 12, hjust = 0.5 )
    ) +
  
  facet_wrap(
    ~ estimate_type,
    ncol = 2,
    scales = "free" 
    ) +
  
  scale_x_discrete(
    limits = c( "2021", "2014", "2010", "2006", "2002" ),
    expand = expansion( 
      mult = c( 0.05, 0.05 ) 
      )
    ) +
  
  # plot_data %>%
  # group_by( estimate_type ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci ),
  #   max_upper_ci = max( upper_ci )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( 
          limits = c( 0, 8 ),
          breaks = seq( 0, 8, 1 ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( 
          limits = c( -10, 30 ),
          breaks = seq( -10, 30, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_flip()
  
p_pr_pd_attempt

# combine plot
combined_plot <- 
  ( p_pr_pd_thought / plot_spacer() / p_pr_pd_attempt ) +
  plot_layout( guides = "collect",
               heights = c( 1, 0.02, 1 ) ) &
  theme( legend.position = "right" )
  
combined_plot
ggsave( "results_output/plots_mi/p_pr_pd_suicide_imp.svg", plot = combined_plot, width = 11, height = 10 )
```

### 5. Use of Antidepressants and Anxiolytics
#### 5.1. Prevalence by sexual identity
```{r}
plot_data <- prevalence_imp %>% 
  filter( 
    outcome %in% c( "antidepressant", "anxiolytic" )
    ) %>%
  mutate(
    lower_ci = if_else( 
      lower_ci < 0, 
      0, 
      lower_ci 
      )
    )

summary( plot_data )

p_prevalence <- ggplot( 
  plot_data,
  
  aes( 
    x = year, 
    y = point_estimate, 
    color = sexual_identity,
    linetype = sample_type,
    group = interaction( sexual_identity, sample_type )
    ) 
  ) +
  
  geom_errorbar(
    data = plot_data %>%
      filter( 
        sample_type == "survey" 
        ),
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.5 
    ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 2 ) +
  
  scale_x_continuous(
    breaks = seq( 2006, 2021, 3 ),
    expand = expansion( 
      mult = c( 0.08, 0.05 ) 
      ) 
    ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" 
      ) 
    ) +
  
  scale_linetype_manual(
    values = c(
      "CS" = "dotted",
      "survey" = "solid" 
      ),
    
    labels = c(
      "CS" = "Cross-Sectional Samples",
      "survey" = "Survey Samples" 
      ) 
    ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence (95% CI)",
    color = NULL,
    linetype = NULL
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom",
    legend.box = "vertical",
    legend.spacing.y = unit( -0.3, "cm" ),
    legend.box.just = "center"
    ) +
  
  guides(
    linetype = guide_legend(
      order = 1,
      nrow = 1
      ),
    
    color = guide_legend(
      order = 2,
      nrow = 1
      )
    ) +
  
  facet_wrap(
    ~ outcome,
    ncol = 2,
    scales = "free",
    labeller = labeller(
      outcome = c(
        "antidepressant" = "Antidepressant Use",
        "anxiolytic" = "Anxiolytic Use" 
        ) 
      )
    ) +
  
  # plot_data %>%
  # group_by( outcome ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci ),
  #   max_upper_ci = max( upper_ci )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      outcome == "antidepressant" ~ 
        scale_y_continuous( 
          limits = c( 0, 0.3 ),
          breaks = seq( 0, 0.3, 0.1 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion( 
            mult = c( 0.05, 0.01 ) 
            ) 
          ),
      
      outcome == "anxiolytic" ~ 
        scale_y_continuous( 
          limits = c( 0, 0.2 ),
          breaks = seq( 0, 0.2, 0.1 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion( 
            mult = c( 0.05, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_capped_cart( 
    left = 'both', 
    bottom = 'both' 
    ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_medication_imp.svg", plot = p_prevalence, width = 10, height = 5 )
```

#### 5.2. Prevalence of antidepressant use by sex
```{r}
plot_data <- prevalence_by_sex_imp %>% 
  filter( 
    outcome %in% c( "antidepressant" )
    ) %>%
  mutate(
    sex = factor(
      sex,
      levels = c( "Female", "Male" )
    ),
    lower_ci = if_else( 
      lower_ci < 0, 
      0, 
      lower_ci 
      )
    )

summary( plot_data )

p_prevalence <- ggplot( 
  plot_data,
  
  aes( 
    x = year, 
    y = point_estimate, 
    color = sexual_identity,
    linetype = sample_type,
    group = interaction( sexual_identity, sample_type )
    ) 
  ) +
  
  geom_errorbar(
    data = plot_data %>%
      filter( 
        sample_type == "survey" 
        ),
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.5 
    ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 2 ) +
  
  scale_x_continuous(
    breaks = seq( 2006, 2021, 3 ),
    expand = expansion( 
      mult = c( 0.08, 0.05 ) 
      ) 
    ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.4 ),
    breaks = seq( 0, 0.4, 0.1 ),
    labels = scales::percent_format( accuracy = 1 ),
    expand = expansion( 
      mult = c( 0.05, 0 ) 
      ) 
    ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" 
      ) 
    ) +
  
  scale_linetype_manual(
    values = c(
      "CS" = "dotted",
      "survey" = "solid" 
      ),
    
    labels = c(
      "CS" = "Cross-Sectional Samples",
      "survey" = "Survey Samples" 
      ) 
    ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Antidepressant Use (95% CI)",
    color = NULL,
    linetype = NULL
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom",
    legend.box = "vertical",
    legend.spacing.y = unit( -0.3, "cm" ),
    legend.box.just = "center"
    ) +
  
  guides(
    linetype = guide_legend(
      order = 1,
      nrow = 1
      ),
    
    color = guide_legend(
      order = 2,
      nrow = 1
      )
    ) +
  
  facet_wrap(
    ~ sex,
    ncol = 2,
    scales = "free_x" 
    ) +
  
  coord_capped_cart( 
    left = 'both', 
    bottom = 'both' 
    ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_antidepressant_by_sex_imp.svg", plot = p_prevalence, width = 9, height = 6 )
```

#### 5.3. PR/PD by sexual identity
```{r}
# antidepressant use
plot_data <- pr_pd_imp %>%
  filter( 
    outcome == "antidepressant"
    )

plot_data %>%
  filter( 
    estimate_type == "Prevalence Difference" 
    ) %>%
  summary()

plot_data %>% 
  filter( 
    estimate_type == "Prevalence Ratio" 
    ) %>%
  summary()

plot_data <- plot_data %>%
  mutate(
    pd_upper_clipped = 
      sample_type == "survey" &
      estimate_type == "Prevalence Difference" &
      upper_ci > 20,
    
    upper_ci = if_else( 
      pd_upper_clipped, 
      20, 
      upper_ci 
      ),
    
    pr_upper_clipped = 
      sample_type == "survey" &
      estimate_type == "Prevalence Ratio" & 
      upper_ci > 6,
    
    upper_ci = if_else( 
      pr_upper_clipped, 
      6, 
      upper_ci 
      )
  )


p_pr_pd_antidepressant <- ggplot(
  plot_data,
  
  aes( 
    x = year,
    y = point_estimate,
    color = exposure_model,
    linetype = sample_type,
    group = interaction( exposure_model, sample_type )
    ) 
  ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Ratio" 
      ),
    aes( 
      yintercept = 1 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Difference" 
      ),
    aes( 
      yintercept = 0 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  # error bar 
  geom_segment(
    data = plot_data %>%
      filter( sample_type == "survey" ),
    aes(
      x = year,
      xend = year,
      y = lower_ci,
      yend = upper_ci
    ),
    linewidth = 0.4
  ) +
  
  geom_segment(
    data = plot_data %>%
      filter(
        sample_type == "survey"
      ),
    aes(
      x = year - 0.25,
      xend = year + 0.25,
      y = lower_ci,
      yend = lower_ci
    ),
    linewidth = 0.4
  ) +
  
  geom_segment(
    data = plot_data %>%
      filter(
        sample_type == "survey",
        !pd_upper_clipped,
        !pr_upper_clipped
      ),
    aes(
      x = year - 0.25,
      xend = year + 0.25,
      y = upper_ci,
      yend = upper_ci
    ),
    linewidth = 0.4
  ) +
  
  geom_segment(
    data = plot_data %>%
      filter( pd_upper_clipped | 
                pr_upper_clipped ),
    aes(
      x = year,
      xend = year,
      y = upper_ci - 0.3,
      yend = upper_ci
    ),
    
    arrow = arrow(
      length = unit( 2.5, "mm" ),
      type = "closed"
    ),
    linewidth = 0.4,
    show.legend = FALSE
  ) +
  
  geom_line( 
    linewidth = 0.8
    ) +
  
  geom_point(
    shape = 15,
    size = 2.5
    ) +
  
  scale_color_manual( 
    values = exposure_colors,
    labels = exposure_labels
    ) +
  
  scale_linetype_manual(
    values = c(
      "CS" = "dotted",
      "survey" = "solid" 
      ),
    
    labels = c(
      "CS" = "Cross-Sectional Samples",
      "survey" = "Survey Samples" 
      ) 
    ) +
  

  labs( 
    x = "Calendar Year",
    y = "Association Estimate (95% CI)",
    title = "Antidepressant Use",
    color = NULL,
    linetype = NULL
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    plot.title = element_text( family = "Arial", size = 12, hjust = 0.5 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 )
    ) +
  
  guides(
    linetype = guide_legend(
      order = 1,
      nrow = 2
      ),
    
    color = guide_legend(
      order = 2,
      nrow = 4
      )
    ) +
  
  facet_wrap(
    ~ estimate_type,
    ncol = 2,
    scales = "free" 
    ) +
  
  scale_x_continuous( 
    trans = "reverse",
    breaks = seq( 2006, 2021, 3 ),
    expand = expansion( mult = c( 0.05, 0.05 ) ) ) +
  
  # plot_data %>%
  # group_by( estimate_type ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci ),
  #   max_upper_ci = max( upper_ci )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( 
          limits = c( 0, 6 ),
          breaks = seq( 0, 6, 1 ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( 
          limits = c( -10, 20 ),
          breaks = seq( -10, 20, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_flip()
  
p_pr_pd_antidepressant

# anxiolytic use
plot_data <- pr_pd_imp %>%
  filter( 
    outcome == "anxiolytic"
    )

plot_data %>%
  filter( 
    estimate_type == "Prevalence Difference" 
    ) %>%
  summary()

plot_data %>% 
  filter( 
    estimate_type == "Prevalence Ratio" 
    ) %>%
  summary()

plot_data <- plot_data %>%
  mutate(
    pr_upper_clipped = 
      sample_type == "survey" &
      estimate_type == "Prevalence Ratio" & 
      upper_ci > 8,
    
    upper_ci = if_else( 
      pr_upper_clipped, 
      8, 
      upper_ci 
      )
  )


p_pr_pd_anxiolytic <- ggplot(
  plot_data,
  
  aes( 
    x = year,
    y = point_estimate,
    color = exposure_model,
    linetype = sample_type,
    group = interaction( exposure_model, sample_type )
    ) 
  ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Ratio" 
      ),
    aes( 
      yintercept = 1 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Difference" 
      ),
    aes( 
      yintercept = 0 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  # error bar 
  geom_segment(
    data = plot_data %>%
      filter( sample_type == "survey" ),
    aes(
      x = year,
      xend = year,
      y = lower_ci,
      yend = upper_ci
    ),
    linewidth = 0.4
  ) +
  
  geom_segment(
    data = plot_data %>%
      filter(
        sample_type == "survey"
      ),
    aes(
      x = year - 0.25,
      xend = year + 0.25,
      y = lower_ci,
      yend = lower_ci
    ),
    linewidth = 0.4
  ) +
  
  geom_segment(
    data = plot_data %>%
      filter(
        sample_type == "survey",
        !pr_upper_clipped
      ),
    aes(
      x = year - 0.25,
      xend = year + 0.25,
      y = upper_ci,
      yend = upper_ci
    ),
    linewidth = 0.4
  ) +
  
  geom_segment(
    data = plot_data %>%
      filter( 
        pr_upper_clipped 
        ),
    aes(
      x = year,
      xend = year,
      y = upper_ci - 0.3,
      yend = upper_ci
    ),
    
    arrow = arrow(
      length = unit( 2.5, "mm" ),
      type = "closed"
    ),
    linewidth = 0.4,
    show.legend = FALSE
  ) +
  
  geom_line( 
    linewidth = 0.8
    ) +
  
  geom_point(
    shape = 15,
    size = 2.5
    ) +
  
  scale_color_manual( 
    values = exposure_colors,
    labels = exposure_labels
    ) +
  
  scale_linetype_manual(
    values = c(
      "CS" = "dotted",
      "survey" = "solid" 
      ),
    
    labels = c(
      "CS" = "Cross-Sectional Samples",
      "survey" = "Survey Samples" 
      ) 
    ) +
  

  labs( 
    x = "Calendar Year",
    y = "Association Estimate (95% CI)",
    title = "Anxiolytic Use",
    color = NULL,
    linetype = NULL
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    plot.title = element_text( family = "Arial", size = 12, hjust = 0.5 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 )
    ) +
  
  guides(
    linetype = guide_legend(
      order = 1,
      nrow = 2
      ),
    
    color = guide_legend(
      order = 2,
      nrow = 4
      )
    ) +
  
  facet_wrap(
    ~ estimate_type,
    ncol = 2,
    scales = "free" 
    ) +
  
  scale_x_continuous( 
    trans = "reverse",
    breaks = seq( 2006, 2021, 3 ),
    expand = expansion( mult = c( 0.05, 0.05 ) ) ) +
  
  # plot_data %>%
  # group_by( estimate_type ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci ),
  #   max_upper_ci = max( upper_ci )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( 
          limits = c( 0, 8 ),
          breaks = seq( 0, 8, 1 ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( 
          limits = c( -5, 15 ),
          breaks = seq( -5, 15, 5 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_flip()
  
p_pr_pd_anxiolytic

# combine plot
combined_plot <- 
  ( p_pr_pd_antidepressant / plot_spacer() / p_pr_pd_anxiolytic ) +
  plot_layout( guides = "collect",
               heights = c( 1, 0.02, 1 ) ) &
  theme( legend.position = "right" )
  
combined_plot
ggsave( "results_output/plots_mi/p_pr_pd_medication_imp.svg", plot = combined_plot, width = 11, height = 11 )
```

### 6. Other Register-Based Outcomes
#### 6.1. Prevalence by sexual identity
```{r}
prevalence_imp %>%
  filter( outcome %in% c( "depression" ),
          sample_type == "survey" ) %>%
  summary()

prevalence_imp %>%
  filter( outcome %in% c( "anxiety" ),
          sample_type == "survey" ) %>%
  summary()

prevalence_imp %>%
  filter( outcome %in% c( "stress_related" ),
          sample_type == "survey" ) %>%
  summary()

plot_data <- prevalence_imp %>% 
  filter( 
    outcome %in% c( "depression", "anxiety", "stress_related" ) 
    ) %>%
  mutate(
    outcome = factor(
      outcome,
      levels = c( "depression", "anxiety", "stress_related" )
      ),
    
    lower_ci = if_else( 
      sample_type == "survey" & lower_ci < 0, 
      0, 
      lower_ci 
      ),
    
    across(
      c( lower_ci, upper_ci ),
      ~ ifelse(
        outcome == "anxiety" &
          year == 2014 & 
          sexual_identity == "Homosexual",
        NA_real_,
          .
        )
      )
    )

p_prevalence <- ggplot( 
  plot_data,
  
  aes( 
    x = year, 
    y = point_estimate, 
    color = sexual_identity, 
    linetype = sample_type, 
    group = interaction( sexual_identity, sample_type ) 
    ) 
  ) +
  
  geom_errorbar(
    data = plot_data %>%
      filter( 
        sample_type == "survey" 
        ),
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.5 
    ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 2 ) +
  
  scale_x_continuous(
    breaks = seq( 2003, 2019, 4 ),
    limits = c( 2003, 2019 ),
    expand = expansion(
      mult = c( 0.08, 0.05 )
      ) 
    ) +
    
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" 
      ) 
    ) +
  
  scale_linetype_manual(
    values = c(
      "CS" = "dotted",
      "survey" = "solid" 
    ),
    
    labels = c(
      "CS" = "Cross-Sectional Samples",
      "survey" = "Survey Samples" 
    ) 
  ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence (95% CI)",
    color = NULL,
    linetype = NULL
  ) +
  
  facet_wrap( 
    ~ outcome,
    ncol = 2,
    axes = "all",
    scales = "free",
    labeller = labeller(
      outcome = c(
        "depression" = "Depression",
        "anxiety" = "Anxiety Disorders",
        "stress_related" = "Stress-Related Disorders" 
        ) 
      ) 
    ) +
  
  ggh4x::facetted_pos_scales( 
    y = list(
      outcome == "depression" ~ 
        scale_y_continuous( 
          limits = c( 0, 0.25 ),
          breaks = seq( 0, 0.25, 0.05 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion( 
            mult = c( 0.05, 0 ) 
            ) 
          ),
      
      outcome == "anxiety" ~ 
        scale_y_continuous( 
          limits = c( 0, 0.2 ),
          breaks = seq( 0, 0.2, 0.05 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion( 
            mult = c( 0.05, 0 ) 
            ) 
          ),
      
      outcome == "stress_related" ~ 
        scale_y_continuous( 
          limits = c( 0, 0.1 ),
          breaks = seq( 0, 0.1, 0.05 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion( 
            mult = c( 0.05, 0 ) 
            ) 
          ) 
      ) 
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom",
    legend.box = "vertical",
    legend.spacing.y = unit( -0.3, "cm" ),
    legend.box.just = "center"
  ) +
  
  guides(
    linetype = guide_legend(
      order = 1,
      nrow = 1
      ),
    
    color = guide_legend(
      order = 2,
      nrow = 1
    )
  ) +
  
  coord_capped_cart( 
    left = 'both', 
    bottom = 'both' 
    ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_diagnosis_imp.svg", plot = p_prevalence, width = 10, height = 8 )
```

### 7. Comparison of CC and MI Results
#### 7.1. Prevalence by sexual identity
```{r}
##### MI results #####

overall_prevalence_2002_imp <- read_xlsx( here( "results_output/results_mi/overall_prevalence_2002_imp.xlsx" ) )
overall_prevalence_2006_imp <- read_xlsx( here( "results_output/results_mi/overall_prevalence_2006_imp.xlsx" ) )
overall_prevalence_2010_imp <- read_xlsx( here( "results_output/results_mi/overall_prevalence_2010_imp.xlsx" ) )
overall_prevalence_2014_imp <- read_xlsx( here( "results_output/results_mi/overall_prevalence_2014_imp.xlsx" ) )
overall_prevalence_2021_imp <- read_xlsx( here( "results_output/results_mi/overall_prevalence_2021_imp.xlsx" ) )

prevalence_imp <- bind_rows( 
  overall_prevalence_2002_imp,
  overall_prevalence_2006_imp,
  overall_prevalence_2010_imp,
  overall_prevalence_2014_imp,
  overall_prevalence_2021_imp 
  ) %>%
  filter( 
    sexual_identity != "Other"
    ) %>%
  mutate( 
    sexual_identity = factor( 
      sexual_identity,
      levels = c( "Heterosexual", "Homosexual", "Bisexual" ) 
      ),
    outcome = as.factor( outcome ),
    year = as.factor( year ),
    analysis = "MI"
    )

summary( prevalence_imp )


##### CC results #####

prevalence_2002_by_identity_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2002_by_identity_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -sexual_identity,
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

prevalence_2006_by_identity_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2006_by_identity_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -sexual_identity,
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

prevalence_2010_by_identity_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2010_by_identity_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -sexual_identity,
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

prevalence_2014_by_identity_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2014_by_identity_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2014 ) %>%
  pivot_longer(
    cols = -sexual_identity,
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

prevalence_2021_by_identity_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2021_by_identity_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2021 ) %>%
  pivot_longer(
    cols = -sexual_identity,
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

prevalence_cc <- bind_rows( 
  prevalence_2002_by_identity_cc,
  prevalence_2006_by_identity_cc,
  prevalence_2010_by_identity_cc,
  prevalence_2014_by_identity_cc,
  prevalence_2021_by_identity_cc 
  ) %>%
  filter( sexual_identity != "Other" ) %>%
  mutate( 
    sexual_identity = factor( 
      sexual_identity, 
      levels = c( "Heterosexual", "Homosexual", "Bisexual" ) 
      ),
    outcome = as.factor( outcome ),
    year = as.factor( year ),
    analysis = "CCA" 
    )

summary( prevalence_cc )


##### merge data #####

setequal( colnames( prevalence_imp ), colnames( prevalence_cc ) )

prevalence_all <- bind_rows(
  prevalence_imp,
  prevalence_cc 
  ) %>%
  
  filter(
    !( year == 2021 &
         outcome %in% c( "depression", "anxiety", "stress_related" ) ) 
    ) %>%
  
  mutate( 
    analysis = factor( 
      analysis, 
      levels = c( "MI", "CCA" ) 
      ),
    
    lower_ci = if_else(
      lower_ci < 0,
      0,
      lower_ci
    ),
    
    across(
      c( lower_ci, upper_ci ),
      ~ if_else(
        (
          outcome == "anxiety" &
          year == 2014 &
          sexual_identity == "Homosexual"
        ) |
        (
          outcome == "stress_related" &
          year == 2006 &
          sexual_identity == "Bisexual"
        ),
        NA_real_,
        .
        )
      ),
    
    outcome = factor(
      outcome,
      levels = c(
        "psychological_distress",
        "suicidal_thoughts",
        "suicide_attempts",
        "antidepressant",
        "anxiolytic",
        "depression",
        "anxiety",
        "stress_related"
        )
      )
    )
  
summary( prevalence_all )


##### plotting #####

p_prevalence_compare <- ggplot(
  prevalence_all,
  aes(
    x = year,
    y = point_estimate,
    color = sexual_identity,
    linetype = analysis,
    group = interaction( sexual_identity, analysis )
    )
  ) +
  
  geom_errorbar(
    data = prevalence_all %>%
      filter(
        outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" )
        ),
    aes(
      ymin = lower_ci,
      ymax = upper_ci
      ),
    width = 0.16,
    show.legend = FALSE
    ) +

  geom_errorbar(
    data = prevalence_all %>%
      filter(
        outcome %in% c( "antidepressant", "anxiolytic" )
        ),
    aes(
      ymin = lower_ci,
      ymax = upper_ci
      ),
    width = ( 0.16 / 4 ) * 3,
    show.legend = FALSE
    ) +
  
  geom_errorbar(
    data = prevalence_all %>%
      filter(
        outcome %in% c( "depression", "anxiety", "stress_related" )
        ),
    aes(
      ymin = lower_ci,
      ymax = upper_ci
      ),
    width = ( 0.16 / 4 ) * 2,
    show.legend = FALSE
    ) +

  geom_line( linewidth = 0.8 ) +

  geom_point( size = 2 ) +

  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) 
    ) +

  scale_linetype_manual(
    values = c(
      "MI"  = "solid",
      "CCA" = "dashed"
      ),
    labels = c(
      "MI"  = "Multiple Imputation Analysis",
      "CCA" = "Complete-Case Analysis"
      )
    ) +

  labs(
    x = "Survey Year",
    y = "Prevalence (95% CI)",
    color = NULL,
    linetype = NULL
    ) +

  facet_wrap(
    ~ outcome,
    ncol = 4,
    axes = "all",
    scales = "free",
    labeller = labeller(
      outcome = c(
        "psychological_distress" = "Psychological Distress",
        "suicidal_thoughts"      = "Suicidal Thoughts",
        "suicide_attempts"       = "Suicide Attempts",
        "antidepressant"         = "Antidepressant Use",
        "anxiolytic"             = "Anxiolytic Use",
        "depression"             = "Depression",
        "anxiety"                = "Anxiety",
        "stress_related"         = "Stress-Related Disorders"
      )
    )
  ) +

  ggh4x::facetted_pos_scales(
    x = list(
      outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ) ~
        scale_x_discrete( 
          breaks = c( "2002", "2006", "2010", "2014", "2021" ),
          expand = expansion( 
            mult = c( 0.1, 0.05 ) 
            ) 
          ),

    outcome %in% c( "antidepressant", "anxiolytic" ) ~
        scale_x_discrete( 
          breaks = c( "2006", "2010", "2014", "2021" ),
          expand = expansion( 
            mult = c( 0.1, 0.05 ) 
            ) 
          ),
      
      outcome %in% c( "depression", "anxiety", "stress_related" ) ~
        scale_x_discrete( 
          breaks = c( "2006", "2010", "2014" ),
          expand = expansion( 
            mult = c( 0.1, 0.05 )
            )
          )
      ),
    
    
    # prevalence_all %>%
    #   group_by( outcome ) %>%
    #   summarise(
    #     min_lower = min( lower_ci, na.rm = TRUE ),
    #     max_upper = max( upper_ci, na.rm = TRUE ),
    #     .groups = "drop"
    #     )
    
    y = list(
      outcome %in% c( "psychological_distress", "suicidal_thoughts" ) ~
        scale_y_continuous(
          limits = c( 0, 0.75 ),
          breaks = seq( 0, 0.75, 0.25 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "suicide_attempts" ~
        scale_y_continuous(
          limits = c( 0, 0.4 ),
          breaks = seq( 0, 0.4, 0.1 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome %in% c( "antidepressant", "depression" ) ~
        scale_y_continuous(
          limits = c( 0, 0.3 ),
          breaks = seq( 0, 0.3, 0.1 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome %in% c( "anxiolytic", "anxiety", "stress_related" ) ~
        scale_y_continuous(
          limits = c( 0, 0.2 ),
          breaks = seq( 0, 0.2, 0.1 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        )
      )
    ) +

  guides(
    linetype = guide_legend(
      order = 1,
      nrow = 1
      ),
    
    color = guide_legend(
      order = 2,
      nrow = 1
      )
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom",
    legend.box = "vertical",
    legend.spacing.y = unit( -0.3, "cm" ),
    legend.box.just = "center" ) +
  
  coord_capped_cart( 
    left = 'both', 
    bottom = 'both' 
    ) 

p_prevalence_compare
ggsave( "results_output/plots_mi/p_prevalence_compare.svg", plot = p_prevalence_compare, width = 14, height = 8 )
```

#### 7.2. PR/PD by sexual identity
```{r}
##### MI results #####

pr_2002_imp <- read_xlsx( here( 'results_output/results_mi/pr_2002_imp.xlsx' ) )
pr_2006_imp <- read_xlsx( here( 'results_output/results_mi/pr_2006_imp.xlsx' ) )
pr_2010_imp <- read_xlsx( here( 'results_output/results_mi/pr_2010_imp.xlsx' ) )
pr_2014_imp <- read_xlsx( here( 'results_output/results_mi/pr_2014_imp.xlsx' ) )
pr_2021_imp <- read_xlsx( here( 'results_output/results_mi/pr_2021_imp.xlsx' ) )

pr_imp <- bind_rows( 
  pr_2002_imp,
  pr_2006_imp,
  pr_2010_imp,
  pr_2014_imp,
  pr_2021_imp 
  ) %>%
  mutate( estimate_type = "Prevalence Ratio" )

pd_2002_imp <- read_xlsx( here( 'results_output/results_mi/pd_2002_imp.xlsx' ) )
pd_2006_imp <- read_xlsx( here( 'results_output/results_mi/pd_2006_imp.xlsx' ) )
pd_2010_imp <- read_xlsx( here( 'results_output/results_mi/pd_2010_imp.xlsx' ) )
pd_2014_imp <- read_xlsx( here( 'results_output/results_mi/pd_2014_imp.xlsx' ) )
pd_2021_imp <- read_xlsx( here( 'results_output/results_mi/pd_2021_imp.xlsx' ) )

pd_imp <- bind_rows(
  pd_2002_imp,
  pd_2006_imp,
  pd_2010_imp,
  pd_2014_imp,
  pd_2021_imp
  ) %>%
  mutate( estimate_type = "Prevalence Difference" )

pr_pd_imp <- bind_rows( pr_imp, pd_imp ) %>%
  filter( sexual_identity != "Other" ) %>%
  mutate( outcome = as.factor( outcome ),
          year = as.factor( year ),
          sexual_identity = as.factor( sexual_identity ),
          model_type = recode_factor( model_type, "crude" = "Crude", "adjusted" = "Adjusted" ),
          estimate_type = factor( estimate_type, levels = c( "Prevalence Ratio", "Prevalence Difference" ) ),
          exposure_model = interaction( sexual_identity, model_type, sep = "_" ),
          exposure_model = factor( exposure_model, levels = c(
            "Bisexual_Crude",
            "Homosexual_Crude",
            "Bisexual_Adjusted",
            "Homosexual_Adjusted" ) ),
          analysis = "MI" )
summary( pr_pd_imp )


##### CC results #####
pr_2002_cc <- read_xlsx( here( 'results_output/results_cc/pr_2002_cc.xlsx' ) )
pr_2006_cc <- read_xlsx( here( 'results_output/results_cc/pr_2006_cc.xlsx' ) )
pr_2010_cc <- read_xlsx( here( 'results_output/results_cc/pr_2010_cc.xlsx' ) )
pr_2014_cc <- read_xlsx( here( 'results_output/results_cc/pr_2014_cc.xlsx' ) )
pr_2021_cc <- read_xlsx( here( 'results_output/results_cc/pr_2021_cc.xlsx' ) )

pr_cc <- bind_rows( pr_2002_cc,
                    pr_2006_cc,
                    pr_2010_cc,
                    pr_2014_cc,
                    pr_2021_cc ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate( estimate_type = "Prevalence Ratio" )

pd_2002_cc <- read_xlsx( here( 'results_output/results_cc/pd_2002_cc.xlsx' ) )
pd_2006_cc <- read_xlsx( here( 'results_output/results_cc/pd_2006_cc.xlsx' ) )
pd_2010_cc <- read_xlsx( here( 'results_output/results_cc/pd_2010_cc.xlsx' ) )
pd_2014_cc <- read_xlsx( here( 'results_output/results_cc/pd_2014_cc.xlsx' ) )
pd_2021_cc <- read_xlsx( here( 'results_output/results_cc/pd_2021_cc.xlsx' ) )

pd_cc <- bind_rows( pd_2002_cc,
                    pd_2006_cc,
                    pd_2010_cc,
                    pd_2014_cc,
                    pd_2021_cc ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate( estimate_type = "Prevalence Difference",
          across(
            c( point_estimate, lower_ci, upper_ci ),
            ~ .x * 100
            )
          )

pr_pd_cc <- bind_rows( pr_cc, pd_cc ) %>%
  filter( sexual_identity != "Other" ) %>%
  mutate( outcome = as.factor( outcome ),
          year = as.factor( year ),
          sexual_identity = as.factor( sexual_identity ),
          model_type = recode_factor( model_type, "crude" = "Crude", "adjusted" = "Adjusted" ),
          estimate_type = factor( estimate_type, levels = c( "Prevalence Ratio", "Prevalence Difference" ) ),
          exposure_model = interaction( sexual_identity, model_type, sep = "_" ),
          exposure_model = factor( exposure_model, levels = c(
            "Bisexual_Crude",
            "Homosexual_Crude",
            "Bisexual_Adjusted",
            "Homosexual_Adjusted" ) ),
          analysis = "CCA" )
summary( pr_pd_cc )


##### merge data #####

setequal( colnames( pr_pd_imp ), colnames( pr_pd_cc ) )
pr_pd_all <- bind_rows(
  pr_pd_imp,
  pr_pd_cc
  ) %>%
  mutate( 
    analysis = factor( analysis, levels = c( "MI", "CCA" ) ) 
    )
summary( pr_pd_all )

pr_pd_all <- pr_pd_all %>%
  mutate(
    across(
      c( point_estimate, lower_ci, upper_ci ),
      ~ ifelse(
        (
          outcome == "anxiety" &
          year == 2014 &
          sexual_identity == "Homosexual"
          ) |
          (
           outcome == "stress_related" &
           year == 2006 &
           sexual_identity == "Bisexual"
           ),
        NA_real_,
        .
        )
      )
    ) %>%
  filter(
    !( year == 2021 &
         outcome %in% c( "depression", "anxiety", "stress_related" ) ) 
    )
```

#### 7.3. Prevalence
```{r}

```

#### 7.4. Prevalence Difference
```{r}
summary( 
  pr_pd_all %>%
    filter(
      estimate_type == "Prevalence Difference"
      ) 
  )

plot_data <- pr_pd_all %>%
  filter(
    estimate_type == "Prevalence Difference"
    ) %>%
  mutate(
    outcome = factor(
      outcome,
      levels = c(
        "antidepressant",
        "anxiolytic",
        "psychological_distress",
        "suicidal_thoughts",
        "suicide_attempts",
        "depression",
        "anxiety",
        "stress_related"
        )
      )
    )
summary( plot_data )

p_pd_compare <- ggplot(
  plot_data,
  aes(
    x = year,
    y = point_estimate,
    color = exposure_model,
    linetype = analysis,
    group = interaction(
      exposure_model,
      analysis
      )
    )
  ) +

  geom_errorbar(
    data = plot_data %>%
      filter(
        outcome %in% c(
          "antidepressant", "anxiolytic" 
          )
        ),
    aes(
      ymin = lower_ci,
      ymax = upper_ci
      ),
    width = ( 0.16 / 4 ) * 3,
    show.legend = FALSE
    ) +
  
  geom_errorbar(
    data = plot_data %>%
      filter(
        outcome %in% c(
          "psychological_distress", "suicidal_thoughts", "suicide_attempts"
          )
        ),
    aes(
      ymin = lower_ci,
      ymax = upper_ci
      ),
    width = 0.16,
    show.legend = FALSE
    ) +
  
  geom_errorbar(
    data = plot_data %>%
      filter(
        outcome %in% c(
          "depression", "anxiety", "stress_related"
          )
        ),
    aes(
      ymin = lower_ci,
      ymax = upper_ci
      ),
    width = ( 0.16 / 4 ) * 2,
    show.legend = FALSE
    ) +

  geom_line(
    linewidth = 0.8
    ) +

  geom_point(
    size = 1.2
    ) +

  scale_color_manual( 
    values = exposure_colors,
    labels = exposure_labels 
    ) +

  scale_linetype_manual(
    values = c(
      "MI"  = "solid",
      "CCA" = "dashed"
      ),
    labels = c(
      "MI"  = "Multiple Imputation",
      "CCA" = "Complete-Case Analysis"
      )
    ) +

  labs(
    x = "Survey Year",
    y = "Prevalence Difference (95% CI)",
    color = NULL,
    linetype = NULL
    ) +

  facet_wrap(
    ~ outcome,
    ncol = 4,
    axes = "all",
    scales = "free",
    labeller = labeller(
      outcome = c(
        "psychological_distress" = "Psychological Distress",
        "suicidal_thoughts"      = "Suicidal Thoughts",
        "suicide_attempts"       = "Suicide Attempts",
        "antidepressant"         = "Antidepressant Use",
        "anxiolytic"             = "Anxiolytic Use",
        "depression"             = "Depression",
        "anxiety"                = "Anxiety",
        "stress_related"         = "Stress-Related Disorders"
      )
    )
  ) +

  ggh4x::facetted_pos_scales(
    x = list(
      outcome %in% c( "antidepressant", "anxiolytic" ) ~
        scale_x_discrete( breaks = c( "2006", "2010", "2014", "2021" ),
                          expand = expansion( mult = c( 0.1, 0.05 ) ) ),
      
      outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ) ~
        scale_x_discrete( breaks = c( "2002", "2006", "2010", "2014", "2021" ),
                          expand = expansion( mult = c( 0.1, 0.05 ) ) ),
      
      outcome %in% c( "depression", "anxiety", "stress_related" ) ~
        scale_x_discrete( breaks = c( "2006", "2010", "2014" ),
                          expand = expansion( mult = c( 0.1, 0.05 ) ) )
      ),
    
    
    # plot_data %>%
    #   group_by( outcome ) %>%
    #   summarise(
    #     min_point = min( point_estimate, na.rm = TRUE ),
    #     max_point = max( point_estimate, na.rm = TRUE ),
    #     min_lower = min( lower_ci, na.rm = TRUE ),
    #     max_upper = max( upper_ci, na.rm = TRUE ),
    #     .groups = "drop"
    #     )
    
    y = list(
      outcome == "psychological_distress" ~
        scale_y_continuous(
          limits = c( -20, 40 ),
          breaks = seq( -20, 40, 20 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "suicidal_thoughts" ~
        scale_y_continuous(
          limits = c( -15, 45 ),
          breaks = seq( -15, 45, 15 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "suicide_attempts" ~
        scale_y_continuous(
          limits = c( -10, 30 ),
          breaks = seq( -10, 30, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "antidepressant" ~
        scale_y_continuous(
          limits = c( -10, 30 ),
          breaks = seq( -10, 30, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "anxiolytic" ~
        scale_y_continuous(
          limits = c( -10, 20 ),
          breaks = seq( -10, 20, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "depression" ~
        scale_y_continuous(
          limits = c( -10, 20 ),
          breaks = seq( -10, 20, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "anxiety" ~
        scale_y_continuous(
          limits = c( -10, 20 ),
          breaks = seq( -10, 20, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "stress_related" ~
        scale_y_continuous(
          limits = c( -10, 10 ),
          breaks = seq( -10, 10, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        )
      )
    ) +

  guides(
    linetype = guide_legend(
      order = 1,
      nrow = 1
      ),
    
    color = guide_legend(
      order = 2,
      nrow = 1
      )
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom",
    legend.box = "vertical",
    legend.spacing.y = unit( -0.3, "cm" ),
    legend.box.just = "center" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_pd_compare
ggsave( "results_output/plots_mi/p_pd_compare.svg", plot = p_pd_compare, width = 14, height = 8 )
```

#### 7.5. Prevalence Ratio
```{r}
summary( 
  pr_pd_all %>%
    filter(
      estimate_type == "Prevalence Ratio"
      ) 
  )

plot_data <- pr_pd_all %>%
  filter(
    estimate_type == "Prevalence Ratio",
    !( year == 2021 &
         outcome %in% c( "depression", "anxiety", "stress_related" ) ) 
    ) %>%
  mutate(
    outcome = factor(
      outcome,
      levels = c(
        "antidepressant",
        "anxiolytic",
        "psychological_distress",
        "suicidal_thoughts",
        "suicide_attempts",
        "depression",
        "anxiety",
        "stress_related"
        )
      )
    )
summary( plot_data )

p_pd_compare <- ggplot(
  plot_data,
  aes(
    x = year,
    y = point_estimate,
    color = exposure_model,
    linetype = analysis,
    group = interaction(
      exposure_model,
      analysis
      )
    )
  ) +

  geom_errorbar(
    data = plot_data %>%
      filter(
        outcome %in% c(
          "antidepressant", "anxiolytic" 
          )
        ),
    aes(
      ymin = lower_ci,
      ymax = upper_ci
      ),
    width = ( 0.16 / 4 ) * 3,
    show.legend = FALSE
    ) +
  
  geom_errorbar(
    data = plot_data %>%
      filter(
        outcome %in% c(
          "psychological_distress", "suicidal_thoughts", "suicide_attempts"
          )
        ),
    aes(
      ymin = lower_ci,
      ymax = upper_ci
      ),
    width = 0.16,
    show.legend = FALSE
    ) +
  
  geom_errorbar(
    data = plot_data %>%
      filter(
        outcome %in% c(
          "depression", "anxiety", "stress_related"
          )
        ),
    aes(
      ymin = lower_ci,
      ymax = upper_ci
      ),
    width = ( 0.16 / 4 ) * 2,
    show.legend = FALSE
    ) +

  geom_line(
    linewidth = 0.8
    ) +

  geom_point(
    size = 1.2
    ) +

  scale_color_manual( 
    values = exposure_colors,
    labels = exposure_labels 
    ) +

  scale_linetype_manual(
    values = c(
      "MI"  = "solid",
      "CCA" = "dashed"
      ),
    labels = c(
      "MI"  = "Multiple Imputation",
      "CCA" = "Complete-Case Analysis"
      )
    ) +

  labs(
    x = "Survey Year",
    y = "Prevalence Difference (95% CI)",
    color = NULL,
    linetype = NULL
    ) +

  facet_wrap(
    ~ outcome,
    ncol = 4,
    axes = "all",
    scales = "free",
    labeller = labeller(
      outcome = c(
        "psychological_distress" = "Psychological Distress",
        "suicidal_thoughts"      = "Suicidal Thoughts",
        "suicide_attempts"       = "Suicide Attempts",
        "antidepressant"         = "Antidepressant Use",
        "anxiolytic"             = "Anxiolytic Use",
        "depression"             = "Depression",
        "anxiety"                = "Anxiety",
        "stress_related"         = "Stress-Related Disorders"
      )
    )
  ) +

  ggh4x::facetted_pos_scales(
    x = list(
      outcome %in% c( "antidepressant", "anxiolytic" ) ~
        scale_x_discrete( breaks = c( "2006", "2010", "2014", "2021" ),
                          expand = expansion( mult = c( 0.1, 0.05 ) ) ),
      
      outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ) ~
        scale_x_discrete( breaks = c( "2002", "2006", "2010", "2014", "2021" ),
                          expand = expansion( mult = c( 0.1, 0.05 ) ) ),
      
      outcome %in% c( "depression", "anxiety", "stress_related" ) ~
        scale_x_discrete( breaks = c( "2006", "2010", "2014" ),
                          expand = expansion( mult = c( 0.1, 0.05 ) ) )
      ),
    
    
    # plot_data %>%
    #   group_by( outcome ) %>%
    #   summarise(
    #     min_point = min( point_estimate, na.rm = TRUE ),
    #     max_point = max( point_estimate, na.rm = TRUE ),
    #     min_lower = min( lower_ci, na.rm = TRUE ),
    #     max_upper = max( upper_ci, na.rm = TRUE ),
    #     .groups = "drop"
    #     )
    
    y = list(
      outcome == "psychological_distress" ~
        scale_y_continuous(
          limits = c( -20, 40 ),
          breaks = seq( -20, 40, 20 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "suicidal_thoughts" ~
        scale_y_continuous(
          limits = c( -15, 45 ),
          breaks = seq( -15, 45, 15 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "suicide_attempts" ~
        scale_y_continuous(
          limits = c( -10, 30 ),
          breaks = seq( -10, 30, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "antidepressant" ~
        scale_y_continuous(
          limits = c( -10, 30 ),
          breaks = seq( -10, 30, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "anxiolytic" ~
        scale_y_continuous(
          limits = c( -10, 20 ),
          breaks = seq( -10, 20, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "depression" ~
        scale_y_continuous(
          limits = c( -10, 20 ),
          breaks = seq( -10, 20, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "anxiety" ~
        scale_y_continuous(
          limits = c( -10, 20 ),
          breaks = seq( -10, 20, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        ),

      outcome == "stress_related" ~
        scale_y_continuous(
          limits = c( -10, 10 ),
          breaks = seq( -10, 10, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion(
            mult = c( 0.05, 0.05 )
          )
        )
      )
    ) +

  guides(
    linetype = guide_legend(
      order = 1,
      nrow = 1
      ),
    
    color = guide_legend(
      order = 2,
      nrow = 1
      )
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom",
    legend.box = "vertical",
    legend.spacing.y = unit( -0.3, "cm" ),
    legend.box.just = "center" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_pd_compare
ggsave( "results_output/plots_mi/p_pd_compare.svg", plot = p_pd_compare, width = 14, height = 8 )
```



###### 2.2.1.2. Suicidal thoughts
```{r}
plot_data <- pr_pd_imp %>% 
  filter( outcome %in% c( "suicidal_thoughts" ) )
summary( plot_data )

plot_data %>%
  filter( estimate_type == "Prevalence Difference" ) %>%
  summary()

plot_data %>% 
  filter( estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd <- ggplot(
  plot_data,
  
  aes( x = year,
       y = point_estimate,
       color = exposure_model,
       group = exposure_model ) ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey80",
              linewidth = 0.4 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey80",
              linewidth = 0.4 ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 1, 5 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.6 ) +
  
  geom_point(
    shape = 15,
    size = 2
    ) +
  
  scale_color_manual( 
    values = exposure_colors,
    labels = exposure_labels
    ) +
  
  labs( 
    x = "Calendar Year",
    y = "Association Estimate (95% CI)",
    color = NULL,
    linetype = NULL 
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" 
    ) +
  
  facet_wrap(
    ~ estimate_type,
    ncol = 2,
    scales = "free" 
    ) + 
  
  scale_x_discrete( 
    limits = c( "2021", "2014", "2010", "2006", "2002" ),
    expand = expansion( mult = c( 0.05, 0.05 ) ) ) +
  
  ggh4x::facetted_pos_scales( 
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( limits = c( 0, 4 ),
                            breaks = c( seq( 0, 4, 1 ) ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( limits = c( -20, 40 ),
                            breaks = c( seq( -20, 40, 10 ) ),
                            labels = scales::label_number( suffix = "%" ),
                            expand = expansion( mult = c( 0.05, 0.01 ) ) ) ) ) +
  
  coord_flip() +
  
  guides(
    color = guide_legend(
      order = 1,
      nrow = 2,
      byrow = TRUE,
      override.aes = list(
        size = 2,
        linetype = 0
      )
    ),
    
    linetype = guide_legend(
      order = 2,
      nrow = 2,
      keywidth = unit( 0.8, "cm" )
    )
  )
  
p_pr_pd
ggsave( "results_output/plots_mi/p_pr_pd_self_report_imp.svg", plot = p_pr_pd, width = 9, height = 6 )
```

###### 2.2.1.2. Self-reported
```{r}
pr_pd_imp %>% 
  filter( outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ),
          estimate_type == "Prevalence Difference" ) %>%
  summary()

pr_pd_imp %>% 
  filter( outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ),
          estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd <- ggplot(
  pr_pd_imp %>%
    filter( outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ) ),
  
  aes( x = year, y = point_estimate, color = exposure_model, group = exposure_model ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 1, 5 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.05, 0.02 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 1 ) ) +
  
  labs( x = "Survey Year",
        y = "Association Estimate (95% CI)",
        color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ outcome,
              switch = "y",
              scales = "free_y",
              labeller = labeller(
                outcome = c(
                  "psychological_distress" = "Psychological Distress",
                  "suicidal_thoughts" = "Suicidal Thoughts",
                  "suicide_attempts" = "Suicide Attempts" ) ) ) +
  
  ggh4x::facetted_pos_scales( y = list(
    estimate_type == "Prevalence Ratio" ~ scale_y_continuous( limits = c( 0, 8 ), 
                                                              breaks = c( seq( 0, 8, 1 ) ), 
                                                              expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    estimate_type == "Prevalence Difference" ~ scale_y_continuous( limits = c( -20, 50 ), 
                                                                   breaks = c( seq( -20, 50, 10 ) ), 
                                                                   labels = scales::percent_format( accuracy = 1 ), 
                                                                   expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd
ggsave( "results_output/plots_mi/p_pr_pd_self_report_imp.svg", plot = p_pr_pd, width = 12, height = 7.5 )
```

###### 2.2.2.2. Psychological distress
```{r}
pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "psychological_distress" ),
          estimate_type == "Prevalence Difference" ) %>%
  summary()

pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "psychological_distress" ),
          estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd_by_sex <- ggplot(
  pr_pd_by_sex_imp %>%
    filter( outcome %in% c( "psychological_distress" ) ),
  
  aes( x = year, y = estimate, color = exposure_model, group = exposure_model ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 1, 5 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.05, 0.03 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  labs( x = "Survey Year",
        y = "Association Estimate of Psychological Distress (95% CI)",
        color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ sex,
              switch = "y",
              scales = "free_y" ) +
  
  ggh4x::facetted_pos_scales( y = list(
    estimate_type == "Prevalence Ratio" ~ scale_y_continuous( limits = c( 0, 4 ), 
                                                              breaks = c( seq( 0, 4, 1 ) ), 
                                                              expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    estimate_type == "Prevalence Difference" ~ scale_y_continuous( limits = c( -0.3, 0.5 ), 
                                                                   breaks = c( seq( -0.3, 0.5, 0.1 ) ), 
                                                                   labels = scales::percent_format( accuracy = 1 ), 
                                                                   expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd_by_sex
ggsave( "results_output/plots_mi/p_pr_pd_psychological_distress_by_sex_imp.svg", plot = p_pr_pd_by_sex, width = 9, height = 7.5 )
```

###### 2.2.2.3. Suicidal thoughts
```{r}
pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "suicidal_thoughts" ),
          estimate_type == "Prevalence Difference" ) %>%
  summary()

pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "suicidal_thoughts" ),
          estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd_by_sex <- ggplot(
  pr_pd_by_sex_imp %>%
    filter( outcome %in% c( "suicidal_thoughts" ) ),
  
  aes( x = year, y = estimate, color = exposure_model, group = exposure_model ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 1, 5 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.05, 0.03 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  labs( x = "Survey Year",
        y = "Association Estimate of Suicidal Thoughts (95% CI)",
        color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ sex,
              switch = "y",
              scales = "free_y" ) +
  
  ggh4x::facetted_pos_scales( y = list(
    estimate_type == "Prevalence Ratio" ~ scale_y_continuous( limits = c( 0, 5.1 ), 
                                                              breaks = c( seq( 0, 5, 1 ) ), 
                                                              expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    estimate_type == "Prevalence Difference" ~ scale_y_continuous( limits = c( -0.2, 0.6 ), 
                                                                   breaks = c( seq( -0.2, 0.6, 0.1 ) ), 
                                                                   labels = scales::percent_format( accuracy = 1 ), 
                                                                   expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd_by_sex
ggsave( "results_output/plots_mi/p_pr_pd_suicidal_thoughts_by_sex_imp.svg", plot = p_pr_pd_by_sex, width = 9, height = 7.5 )
```

###### 2.2.2.4. Suicide attempts
```{r}
pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "suicide_attempts" ),
          estimate_type == "Prevalence Difference" ) %>%
  summary()

pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "suicide_attempts" ),
          estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd_by_sex <- ggplot(
  pr_pd_by_sex_imp %>%
    filter( outcome %in% c( "suicide_attempts" ) ),
  aes( x = year, y = estimate, color = exposure_model, group = exposure_model ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 1, 5 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.05, 0.03 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  labs( x = "Survey Year",
        y = "Association Estimate of Suicide Attempts (95% CI)",
        color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ sex,
              switch = "y",
              scales = "free_y" ) +
  
  ggh4x::facetted_pos_scales( y = list(
    estimate_type == "Prevalence Ratio" ~ scale_y_continuous( limits = c( 0, 20 ), 
                                                              breaks = c( seq( 0, 20, 5 ) ), 
                                                              expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    estimate_type == "Prevalence Difference" ~ scale_y_continuous( limits = c( -0.2, 0.4 ), 
                                                                   breaks = c( seq( -0.2, 0.4, 0.1 ) ), 
                                                                   labels = scales::percent_format( accuracy = 1 ), 
                                                                   expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd_by_sex
ggsave( "results_output/plots_mi/p_pr_pd_suicide_attempts_by_sex_imp.svg", plot = p_pr_pd_by_sex, width = 9, height = 7.5 )
```




###### 3.1.2.2. Antidepressant use
```{r}
ann_prevalence_by_sex_imp %>%
  filter( outcome %in% c( "antidepressant" ),
          sample_type == "individual" ) %>%
  summary()

plot_data <- ann_prevalence_by_sex_imp %>% 
  filter( outcome %in% c( "antidepressant" ) )

p_prevalence <- ggplot( 
  plot_data,
  aes( x = year, y = point_estimate, color = sexual_identity, linetype = sample_type, group = interaction( sexual_identity, sample_type ) ) ) +
  
  geom_errorbar( data = plot_data %>%
                   filter( sample_type == "individual" ),
                 aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 2006, 2021 ) ) * 0.03 ) +

  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous( breaks = seq( 2006, 2021, 3 ),
                      expand = expansion( mult = c( 0.08, 0.02 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.4 ),
                      breaks = seq( 0, 0.4, 0.1 ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
  "pooled" = "Cross-Sectional Samples",
  "individual" = "Survey Samples" ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Antidepressant Use (95% CI)",
    color = NULL,
    linetype = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_indi_cs_med_antidepressant_by_sex_imp.svg", plot = p_prevalence, width = 10, height = 5 )
```

###### 3.1.2.3. Anxiolytic use
```{r}
ann_prevalence_by_sex_imp %>%
  filter( outcome %in% c( "anxiolytic" ),
          sample_type == "individual" ) %>%
  summary()

plot_data <- ann_prevalence_by_sex_imp %>% 
  filter( outcome %in% c( "anxiolytic" ) )

p_prevalence <- ggplot( 
  plot_data,
  aes( x = year, y = point_estimate, color = sexual_identity, linetype = sample_type, group = interaction( sexual_identity, sample_type ) ) ) +
  
  geom_errorbar( data = plot_data %>%
                   filter( sample_type == "individual" ),
                 aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 2006, 2021 ) ) * 0.03 ) +

  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous( breaks = seq( 2006, 2021, 3 ),
                      expand = expansion( mult = c( 0.08, 0.02 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.5 ),
                      breaks = seq( 0, 0.5, 0.1 ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
  "pooled" = "Cross-Sectional Samples",
  "individual" = "Survey Samples" ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Anxiolytic Use (95% CI)",
    color = NULL,
    linetype = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_indi_cs_med_anxiolytic_by_sex_imp.svg", plot = p_prevalence, width = 10, height = 5 )
```

###### 3.1.2.4. Depression
```{r}
ann_prevalence_by_sex_imp %>%
  filter( outcome %in% c( "depression" ),
          sample_type == "individual" ) %>%
  summary()

plot_data <- ann_prevalence_by_sex_imp %>% 
  filter( outcome %in% c( "depression" ) )

p_prevalence <- ggplot( 
  plot_data,
  aes( x = year, y = point_estimate, color = sexual_identity, linetype = sample_type, group = interaction( sexual_identity, sample_type ) ) ) +
  
  geom_errorbar( data = plot_data %>%
                   filter( sample_type == "individual" ),
                 aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 2003, 2019 ) ) * 0.03 ) +

  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous( breaks = seq( 2003, 2019, 4 ),
                      expand = expansion( mult = c( 0.08, 0.03 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.35 ),
                      breaks = seq( 0, 0.35, 0.05 ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
  "pooled" = "Cross-Sectional Samples",
  "individual" = "Survey Samples" ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Depression (95% CI)",
    color = NULL,
    linetype = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_indi_cs_dia_depression_by_sex_imp.svg", plot = p_prevalence, width = 10, height = 5 )
```

###### 3.1.2.5. Anxiety disorders
```{r}
ann_prevalence_by_sex_imp %>%
  filter( outcome %in% c( "anxiety" ),
          sample_type == "individual" ) %>%
  summary()

plot_data <- ann_prevalence_by_sex_imp %>% 
  filter( outcome %in% c( "anxiety" ) )

p_prevalence <- ggplot( 
  plot_data,
  aes( x = year, y = point_estimate, color = sexual_identity, linetype = sample_type, group = interaction( sexual_identity, sample_type ) ) ) +
  
  geom_errorbar( data = plot_data %>%
                   filter( sample_type == "individual" ),
                 aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 2003, 2019 ) ) * 0.03 ) +

  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous( breaks = seq( 2003, 2019, 4 ),
                      expand = expansion( mult = c( 0.08, 0.03 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.3 ),
                      breaks = seq( 0, 0.3, 0.1 ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
  "pooled" = "Cross-Sectional Samples",
  "individual" = "Survey Samples" ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Anxiety Disorders (95% CI)",
    color = NULL,
    linetype = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_indi_cs_dia_anxiety_by_sex_imp.svg", plot = p_prevalence, width = 10, height = 5 )
```

###### 3.1.2.6. Stress-related disorders
```{r}
ann_prevalence_by_sex_imp %>%
  filter( outcome %in% c( "stress_related" ),
          sample_type == "individual" ) %>%
  summary()

plot_data <- ann_prevalence_by_sex_imp %>% 
  filter( outcome %in% c( "stress_related" ) )

p_prevalence <- ggplot( 
  plot_data,
  aes( x = year, y = point_estimate, color = sexual_identity, linetype = sample_type, group = interaction( sexual_identity, sample_type ) ) ) +
  
  geom_errorbar( data = plot_data %>%
                   filter( sample_type == "individual" ),
                 aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 2003, 2019 ) ) * 0.03 ) +

  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous( breaks = seq( 2003, 2019, 4 ),
                      expand = expansion( mult = c( 0.08, 0.03 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.3 ),
                      breaks = seq( 0, 0.3, 0.1 ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
  "pooled" = "Cross-Sectional Samples",
  "individual" = "Survey Samples" ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Stress-Related Disorders (95% CI)",
    color = NULL,
    linetype = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_indi_cs_dia_stress_by_sex_imp.svg", plot = p_prevalence, width = 10, height = 5 )
```

#### 3.2. Prevalence ratio and difference
##### 3.2.1. By sexual identity
###### 3.2.1.1. Prepare data
```{r}
# prevalence difference
pd_2006_imp <- read_xlsx( here( 'results_output/results_mi/pd_2006_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Difference",
          sample_type = "individual" )

pd_2010_imp <- read_xlsx( here( 'results_output/results_mi/pd_2010_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Difference",
          sample_type = "individual" )

pd_2014_imp <- read_xlsx( here( 'results_output/results_mi/pd_2014_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Difference",
          sample_type = "individual" )

pd_2021_imp <- read_xlsx( here( 'results_output/results_mi/pd_2021_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Difference",
          sample_type = "individual" )

pd_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pd_poo_cs_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Difference",
          sample_type = "pooled",
          outcome = recode( outcome,
                            antidepressant_use = "antidepressant",
                            anxiolytic_use = "anxiolytic" 
                            ) )

# prevalence ratio
pr_2006_imp <- read_xlsx( here( 'results_output/results_mi/pr_2006_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Ratio",
          sample_type = "individual" )

pr_2010_imp <- read_xlsx( here( 'results_output/results_mi/pr_2010_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Ratio",
          sample_type = "individual" )

pr_2014_imp <- read_xlsx( here( 'results_output/results_mi/pr_2014_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Ratio",
          sample_type = "individual" )

pr_2021_imp <- read_xlsx( here( 'results_output/results_mi/pr_2021_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Ratio",
          sample_type = "individual" )

pr_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pr_poo_cs_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Ratio",
          sample_type = "pooled",
          outcome = recode( outcome,
                            antidepressant_use = "antidepressant",
                            anxiolytic_use = "anxiolytic" 
                            ) )

# merge and clean data
pr_pd_imp <- bind_rows( 
  pd_2006_imp,
  pd_2010_imp,
  pd_2014_imp,
  pd_2021_imp,
  pd_poo_cs_imp,
  
  pr_2006_imp,
  pr_2010_imp,
  pr_2014_imp,
  pr_2021_imp,
  pr_poo_cs_imp ) %>%
  
  filter( sexual_identity != "Other",
          outcome %in% c( "antidepressant", "anxiolytic", "depression", "anxiety", "stress_related" ) ) %>%
  mutate( outcome = as.factor( outcome ),
          year = as.integer( year ),
          sexual_identity = as.factor( sexual_identity ),
          sample_type = as.factor( sample_type ),
          model_type = recode_factor( model_type, "crude" = "Crude", "adjusted" = "Adjusted" ),
          estimate_type = factor( estimate_type, levels = c( "Prevalence Ratio", "Prevalence Difference" ) ),
          exposure_model = interaction( sexual_identity, model_type, sep = "_" ),
          exposure_model = factor( exposure_model, levels = c(
            "Bisexual_Crude",
            "Bisexual_Adjusted",
            "Homosexual_Crude",
            "Homosexual_Adjusted" ) ) )

pr_pd_imp <- pr_pd_imp %>%
  mutate(
    across(
      c( point_estimate, lower_ci, upper_ci ),
      ~ ifelse(
        (
          outcome == "anxiety" &
          year == 2014 &
          sexual_identity == "Homosexual" &
          sample_type == "individual"
          ) |
          (
           outcome == "stress_related" &
           year == 2006 &
           sexual_identity == "Bisexual" &
           sample_type == "individual"
           ),
        NA_real_,
        .
        )
      )
    )

# sanity check
pr_pd_imp %>%
  filter( is.na( point_estimate ) )
summary( pr_pd_imp )
summary( pr_pd_imp %>% filter( sample_type == "individual" ) )
```



###### 3.2.1.3. Other register-based outcomes
```{r}
pr_pd_imp %>% 
  filter( outcome %in% c( "depression", "anxiety", "stress_related" ),
          estimate_type == "Prevalence Difference",
          sample_type == "individual" ) %>%
  summary()

pr_pd_imp %>% 
  filter( outcome %in% c( "depression", "anxiety", "stress_related" ),
          estimate_type == "Prevalence Ratio",
          sample_type == "individual" ) %>%
  summary()

plot_data <- pr_pd_imp %>% 
  filter( outcome %in% c( "depression", "anxiety", "stress_related" ) ) %>%
  mutate(
    outcome = factor(
      outcome,
      levels = c( "depression", "anxiety", "stress_related" )
    )
  )

p_pr_pd <- ggplot(
  plot_data,
  
  aes( 
    x = year, 
    y = point_estimate, 
    color = exposure_model, 
    linetype = sample_type, 
    group = interaction( exposure_model, sample_type ) 
    ) ) +
  
  geom_errorbar( 
    data = plot_data %>%
      filter( sample_type == "individual" ),
    aes( ymin = lower_ci, ymax = upper_ci ),
    width = diff( range( 2003, 2019 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_color_manual( 
    values = c(
      "Bisexual_Adjusted"   = "#C77CFF",
      "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
      "Homosexual_Adjusted" = "#00BFC4",
      "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
      "pooled" = "Cross-Sectional Samples",
      "individual" = "Survey Samples" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  labs( x = "Calendar Year",
        y = "Association Estimate (95% CI)",
        color = NULL,
        linetype = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ outcome,
              scales = "free",
              switch = "y",
              labeller = labeller(
                outcome = c(
                  "depression" = "Depression",
                  "anxiety" = "Anxiety Disorders",
                  "stress_related" = "Stress-Related Disorders" ) ) ) +
  
  ggh4x::facetted_pos_scales( 
    x = list(
      outcome %in% c( "depression", "anxiety", "stress_related" ) ~
        scale_x_continuous( breaks = seq( 2003, 2019, 4 ),
                            limits = c( 2003, 2019 ),
                            expand = expansion( mult = c( 0.05, 0.03 ) ) ) ),
    
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( limits = c( 0, 16 ),
                            breaks = c( seq( 0, 16, 4 ) ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( limits = c( -5, 15 ),
                            breaks = c( seq( -5, 15, 5 ) ),
                            labels = scales::label_number( suffix = "%" ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd
ggsave( "results_output/plots_mi/p_pr_pd_dia_imp.svg", plot = p_pr_pd, width = 12, height = 8 )
```

##### 3.2.2. By sex
###### 3.2.2.1. Prepare data
```{r}
# among females
# prevalence ratio
pr_female_2002_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2002_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_female_2006_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2006_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_female_2010_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2010_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_female_2014_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2014_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_female_2021_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2021_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_female_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_poo_cs_imp.xlsx' ) ) %>%
  mutate( sample_type = "pooled",
          outcome = recode( outcome,
                            antidepressant_use = "antidepressant",
                            anxiolytic_use = "anxiolytic" ) )

pr_female_imp <- bind_rows( pr_female_2002_imp,
                           pr_female_2006_imp,
                           pr_female_2010_imp,
                           pr_female_2014_imp,
                           pr_female_2021_imp,
                           pr_female_poo_cs_imp ) %>%
  mutate( estimate_type = "Prevalence Ratio" )

# among males
# prevalence ratio
pr_male_2002_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2002_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_male_2006_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2006_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_male_2010_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2010_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_male_2014_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2014_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_male_2021_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2021_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_male_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_poo_cs_imp.xlsx' ) ) %>%
  mutate( sample_type = "pooled",
          outcome = recode( outcome,
                            antidepressant_use = "antidepressant",
                            anxiolytic_use = "anxiolytic" ) )

pr_male_imp <- bind_rows( pr_male_2002_imp,
                         pr_male_2006_imp,
                         pr_male_2010_imp,
                         pr_male_2014_imp,
                         pr_male_2021_imp,
                         pr_male_poo_cs_imp ) %>%
  mutate( estimate_type = "Prevalence Ratio" )


# among females
# prevalence difference
pd_female_2002_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2002_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_female_2006_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2006_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_female_2010_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2010_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_female_2014_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2014_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_female_2021_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2021_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_female_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_poo_cs_imp.xlsx' ) ) %>%
  mutate( sample_type = "pooled",
          outcome = recode( outcome,
                            antidepressant_use = "antidepressant",
                            anxiolytic_use = "anxiolytic" ) )

pd_female_imp <- bind_rows( pd_female_2002_imp,
                           pd_female_2006_imp,
                           pd_female_2010_imp,
                           pd_female_2014_imp,
                           pd_female_2021_imp,
                           pd_female_poo_cs_imp ) %>%
  mutate( estimate_type = "Prevalence Difference" )

# among males
# prevalence difference
pd_male_2002_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2002_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_male_2006_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2006_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_male_2010_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2010_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_male_2014_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2014_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_male_2021_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2021_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_male_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_poo_cs_imp.xlsx' ) ) %>%
  mutate( sample_type = "pooled",
          outcome = recode( outcome,
                            antidepressant_use = "antidepressant",
                            anxiolytic_use = "anxiolytic" ) )

pd_male_imp <- bind_rows( pd_male_2002_imp,
                         pd_male_2006_imp,
                         pd_male_2010_imp,
                         pd_male_2014_imp,
                         pd_male_2021_imp,
                         pd_male_poo_cs_imp ) %>%
  mutate( estimate_type = "Prevalence Difference" )

# merge data
pr_pd_by_sex_imp <- bind_rows( pr_female_imp, pd_female_imp, pr_male_imp, pd_male_imp ) %>%
  filter( exposure_level != "Other",
          outcome %in% c( "antidepressant", "anxiolytic", "depression", "anxiety", "stress_related" ) ) %>%
  mutate( outcome = as.factor( outcome ),
          sex = as.factor( sex ),
          year = as.integer( year ),
          exposure_level = as.factor( exposure_level ),
          sample_type = as.factor( sample_type ),
          model_type = recode_factor( model_type, "crude" = "Crude", "adjusted" = "Adjusted" ),
          estimate_type = factor( estimate_type, levels = c( "Prevalence Ratio", "Prevalence Difference" ) ),
          exposure_model = interaction( exposure_level, model_type, sep = "_" ),
          exposure_model = factor( exposure_model, levels = c(
            "Bisexual_Crude",
            "Homosexual_Crude",
            "Bisexual_Adjusted",
            "Homosexual_Adjusted" ) ) )

pr_pd_by_sex_imp <- pr_pd_by_sex_imp %>%
  filter(
    !( sample_type == "individual" & outcome %in% c( "depression", "anxiety", "stress_related" ) & year == 2002 ),
    !( sample_type == "individual" & outcome %in% c( "depression", "anxiety", "stress_related" ) & year == 2021 ),
    !( sample_type == "individual" & outcome %in% c( "antidepressant", "anxiolytic" ) & year == 2002 )
  )

pr_pd_by_sex_imp <- pr_pd_by_sex_imp %>%
  mutate(
    across(
      c( estimate, lower_ci, upper_ci ),
      ~ ifelse(
        (
          outcome == "antidepressant" &
          year == 2006 &
          exposure_level == "Bisexual" &
          sample_type == "individual" &
          sex == "Male"
        ),
        NA_real_,
        .
      )
    )
  )

# sanity check
pr_pd_by_sex_imp %>%
  filter( is.na( estimate ) )
summary( pr_pd_by_sex_imp )

# sex-stratified prevalence ratio and prevalence difference analyses for register-based mental health outcomes, including anxiolytic use, depression, anxiety, and stress-related disorders, were not presented because of sparse data and highly imprecise estimates in some subgroups
```

###### 3.2.2.2. Antidepressant use
```{r}
pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "antidepressant" ),
          estimate_type == "Prevalence Difference",
          sample_type == "individual" ) %>%
  summary()

pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "antidepressant" ),
          estimate_type == "Prevalence Ratio",
          sample_type == "individual" ) %>%
  summary()

plot_data <- pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "antidepressant" ) )

p_pr_pd_by_sex <- ggplot(
  plot_data,
  
  aes( x = year, y = estimate, color = exposure_model, linetype = sample_type, group = interaction( exposure_model, sample_type ) ) ) +
  
  geom_errorbar( data = plot_data %>%
                   filter( sample_type == "individual" ),
                 aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 2006, 2021 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_continuous( breaks = seq( 2006, 2021, 3 ),
                      expand = expansion( mult = c( 0.05, 0.03 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
      "pooled" = "Cross-Sectional Samples",
      "individual" = "Survey Samples" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  labs( x = "Calendar Year",
        y = "Association Estimate of Antidepressant Use (95% CI)",
        color = NULL,
        linetype = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ sex,
              switch = "y",
              scales = "free" ) +
  
  ggh4x::facetted_pos_scales( 
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( limits = c( 0, 18 ),
                            breaks = c( seq( 0, 18, 3 ) ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( limits = c( -0.1, 0.3 ),
                            breaks = c( seq( -0.1, 0.3, 0.1 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd_by_sex
ggsave( "results_output/plots_mi/p_pr_pd_antidepressant_by_sex_imp.svg", plot = p_pr_pd_by_sex, width = 9, height = 7.5 )
```
