---
title: "Summary plots of multiple imputation analyses among 16-29 years"
author: Willi Zhang
email: willi.zhang@ki.se
output: html_notebook
editor_options: 
  chunk_output_type: console
---

# Note: For SPHC-B 2002 and 2006, complete-case analyses were plotted (see Supplement 2 for reasons).

### 1. Load Packages and Color Settings
```{r}
library(forestploter)
library(grid)
library(readxl)
library(here)
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(colorspace)
library(naniar)
library(ggh4x)
library(scales)
library(lemon)
library(stringr)
library(patchwork)

exposure_colors <- c(
  "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
  "Bisexual_Adjusted"   = "#C77CFF",
  "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ),
  "Homosexual_Adjusted" = "#00BFC4"
  )

exposure_labels <- c(
  "Bisexual_Crude"      = "Bisexual (Crude)",
  "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
  "Homosexual_Crude"    = "Homosexual (Crude)",
  "Homosexual_Adjusted" = "Homosexual (Adjusted)"
  )
```

### 2. Prepare Data
#### 2.1. By sexual identity
```{r}
##### prevalence #####

# survey samples
prevalence_2002_by_identity_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2002_by_identity_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -sexual_identity,
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

prevalence_2006_by_identity_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2006_by_identity_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -sexual_identity,
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

overall_prevalence_2010_imp <- read_xlsx( here( "results_output/results_mi/overall_prevalence_2010_imp.xlsx" ) ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

overall_prevalence_2014_imp <- read_xlsx( here( "results_output/results_mi/overall_prevalence_2014_imp.xlsx" ) ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

overall_prevalence_2021_imp <- read_xlsx( here( "results_output/results_mi/overall_prevalence_2021_imp.xlsx" ) ) %>%
  mutate( 
    year = as.integer( year ),
    sample_type = "survey"
    )

# cross-sectional samples
prevalence_poo_cs_imp <- read_xlsx( here( "results_output/results_mi/prevalence_poo_cs_imp.xlsx" ) ) %>%
  mutate( sample_type = "CS",
          outcome = recode( 
            outcome,
            antidepressant_use = "antidepressant",
            anxiolytic_use = "anxiolytic"
            ) 
          )

str( prevalence_poo_cs_imp )

# merge prevalence data
setequal( colnames( prevalence_2002_by_identity_cc ), colnames( overall_prevalence_2010_imp ) )
setequal( colnames( prevalence_2002_by_identity_cc ), colnames( prevalence_poo_cs_imp ) )

prevalence_imp <- bind_rows( 
  prevalence_2002_by_identity_cc,
  prevalence_2006_by_identity_cc,
  overall_prevalence_2010_imp,
  overall_prevalence_2014_imp,
  overall_prevalence_2021_imp,
  prevalence_poo_cs_imp
  ) %>%
  filter( 
    sexual_identity != "Other"
    ) %>%
  mutate( 
    sexual_identity = factor( 
      sexual_identity,
      levels = c( "Heterosexual", "Homosexual", "Bisexual" ) 
      ),
    outcome = as.factor( outcome ),
    sample_type = as.factor( sample_type )
    )

summary( prevalence_imp )


##### prevalence ratio and difference #####

# prevalence ratio
pr_2002_cc <- read_xlsx( here( 'results_output/results_cc/pr_2002_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_2006_cc <- read_xlsx( here( 'results_output/results_cc/pr_2006_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_2010_imp <- read_xlsx( here( 'results_output/results_mi/pr_2010_imp.xlsx' ) ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_2014_imp <- read_xlsx( here( 'results_output/results_mi/pr_2014_imp.xlsx' ) ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_2021_imp <- read_xlsx( here( 'results_output/results_mi/pr_2021_imp.xlsx' ) ) %>%
  mutate(
    sample_type = "survey",
    estimate_type = "Prevalence Ratio"
  )

pr_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pr_poo_cs_imp.xlsx' ) ) %>%
  mutate( 
    estimate_type = "Prevalence Ratio",
    sample_type = "CS",
    outcome = recode( outcome,
                      antidepressant_use = "antidepressant",
                      anxiolytic_use = "anxiolytic"
                      ) 
    )

setequal( colnames( pr_2002_cc ), colnames( pr_2010_imp ) )
setequal( colnames( pr_2002_cc ), colnames( pr_poo_cs_imp ) )

# prevalence difference
pd_2002_cc <- read_xlsx( here( 'results_output/results_cc/pd_2002_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    across(
      c( point_estimate, lower_ci, upper_ci ),
      ~ .x * 100
      ),
    sample_type = "survey",
    estimate_type = "Prevalence Difference"
    )

pd_2006_cc <- read_xlsx( here( 'results_output/results_cc/pd_2006_cc.xlsx' ) ) %>%
  rename( sexual_identity = exposure_level,
          point_estimate = estimate ) %>%
  mutate(
    across(
      c( point_estimate, lower_ci, upper_ci ),
      ~ .x * 100
      ),
    sample_type = "survey",
    estimate_type = "Prevalence Difference"
    )

pd_2010_imp <- read_xlsx( here( 'results_output/results_mi/pd_2010_imp.xlsx' ) ) %>%
  mutate( 
    sample_type = "survey",
    estimate_type = "Prevalence Difference" 
    )

pd_2014_imp <- read_xlsx( here( 'results_output/results_mi/pd_2014_imp.xlsx' ) ) %>%
  mutate( 
    sample_type = "survey",
    estimate_type = "Prevalence Difference" 
    )

pd_2021_imp <- read_xlsx( here( 'results_output/results_mi/pd_2021_imp.xlsx' ) ) %>%
  mutate( 
    sample_type = "survey",
    estimate_type = "Prevalence Difference" 
    )

pd_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pd_poo_cs_imp.xlsx' ) ) %>%
  mutate( 
    estimate_type = "Prevalence Difference",
    sample_type = "CS",
    outcome = recode( 
      outcome,
      antidepressant_use = "antidepressant",
      anxiolytic_use = "anxiolytic"
      ) 
    )

setequal( colnames( pd_2002_cc ), colnames( pd_2010_imp ) )
setequal( colnames( pd_2002_cc ), colnames( pd_poo_cs_imp ) )

# merge prevalence difference and ratio
setequal( colnames( pr_2002_cc ), colnames( pd_2002_cc ) )

pr_pd_imp <- bind_rows( 
  pr_2002_cc,
  pr_2006_cc,
  pr_2010_imp,
  pr_2014_imp,
  pr_2021_imp,
  pr_poo_cs_imp,
  
  pd_2002_cc,
  pd_2006_cc,
  pd_2010_imp,
  pd_2014_imp,
  pd_2021_imp,
  pd_poo_cs_imp 
  ) %>%
  filter( 
    sexual_identity != "Other" 
    ) %>%
  mutate( 
    outcome = as.factor( outcome ),
    year = as.integer( year ),
    sample_type = as.factor( sample_type ),
    estimate_type = factor( estimate_type, levels = c( "Prevalence Difference", "Prevalence Ratio" ) ),
    sexual_identity = as.factor( sexual_identity ),
    model_type = recode_factor( model_type, "crude" = "Crude", "adjusted" = "Adjusted" ),
    exposure_model = interaction( sexual_identity, model_type, sep = "_" ),
    exposure_model = factor( 
      exposure_model, 
      levels = c(
        "Bisexual_Crude",
        "Homosexual_Crude",
        "Bisexual_Adjusted",
        "Homosexual_Adjusted" 
        ) 
      ) 
    )
summary( pr_pd_imp )

pr_pd_imp <- pr_pd_imp %>%
  mutate(
    across(
      c( point_estimate, lower_ci, upper_ci ),
      ~ if_else(
        (
          outcome == "anxiety" &
          year == 2014 &
          sexual_identity == "Homosexual" &
          sample_type == "survey"
        ) |
        (
          outcome == "stress_related" &
          year == 2006 &
          sexual_identity == "Bisexual" &
          sample_type == "survey"
        ),
        NA_real_,
        .
      )
    ),
    
    across(
      c( lower_ci, upper_ci ),
      ~ if_else(
        sample_type == "CS",
        NA_real_,
        .
        )
      )
    )
```

### 3. Psychological Distress
#### 3.1. Prevalence by sexual identity
```{r}
plot_data <- prevalence_imp %>% 
  filter( 
    outcome == "psychological_distress"
    ) %>%
  mutate(
    year = as.factor( year )
  )

summary( plot_data )

p_prevalence <- ggplot( 
  plot_data,
  
  aes( 
    x = year, 
    y = point_estimate, 
    color = sexual_identity, 
    group = sexual_identity 
    ) 
  ) +
  
  geom_errorbar( 
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.14 
    ) +
  
  geom_line( 
    linewidth = 0.8 
    ) +
  
  geom_point( 
    size = 2 
    ) +
  
  scale_x_discrete( 
    expand = expansion( 
      mult = c( 
        0.08, 0.05 
        ) 
      ) 
    ) +
  
# plot_data %>% 
#   group_by( outcome ) %>%
#   summarise(
#     min_lower_ci = min( lower_ci ),
#     max_upper_ci = max( upper_ci )
#   )
  
  scale_y_continuous( 
    limits = c( 0, 0.75 ),
    breaks = seq( 
      0, 0.75, 0.15 
      ),
    labels = scales::percent_format( 
      accuracy = 1 
      ),
    expand = expansion( 
      mult = c( 
        0.05, 0 
        ) 
      ) 
    ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  labs(
    x = "Survey Year",
    y = "Prevalence (95% CI)",
    color = NULL 
    ) +
  
  theme_classic() +
  theme(
    axis.title = element_text( 
      family = "Arial", size = 11 
      ),
    axis.text = element_text( 
      family = "Arial", size = 11 
      ),
    legend.title = element_blank(),
    legend.text = element_text( 
      family = "Arial", size = 10 
      ),
    legend.position = "bottom" 
    ) +
  
  coord_capped_cart( 
    left = 'both', 
    bottom = 'both' 
    ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_psychological_distress_imp.svg", plot = p_prevalence, width = 5, height = 5 )
```

#### 3.2. PR/PD by sexual identity
```{r}
plot_data <- pr_pd_imp %>%
  filter( outcome == "psychological_distress" ) %>%
    mutate(
    year = as.factor( year )
  )

summary( plot_data )

plot_data %>%
  filter( estimate_type == "Prevalence Difference" ) %>%
  summary()

plot_data %>% 
  filter( estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd <- ggplot(
  plot_data,
  
  aes( 
    x = year,
    y = point_estimate,
    color = exposure_model,
    group = exposure_model 
    ) 
  ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Ratio" 
      ),
    aes( 
      yintercept = 1 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Difference" 
      ),
    aes( 
      yintercept = 0 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_errorbar( 
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.14
    ) +
  
  geom_line( 
    linewidth = 0.8
    ) +
  
  geom_point(
    shape = 15,
    size = 2.5
    ) +
  
  scale_color_manual( 
    values = exposure_colors,
    labels = exposure_labels
    ) +
  
  labs( 
    x = "Survey Year",
    y = "Association Estimate (95% CI)",
    color = NULL
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom"
    ) +
  
  facet_wrap(
    ~ estimate_type,
    ncol = 2,
    scales = "free" 
    ) +
  
  scale_x_discrete(
    limits = c( "2021", "2014", "2010", "2006", "2002" ),
    expand = expansion( 
      mult = c( 0.05, 0.05 ) 
      )
    ) +
  
  # plot_data %>%
  # group_by( estimate_type ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci ),
  #   max_upper_ci = max( upper_ci )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( 
          limits = c( 0.5, 3 ),
          breaks = seq( 0.5, 3, 0.5 ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( 
          limits = c( -20, 40 ),
          breaks = seq( -20, 40, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_flip()
  
p_pr_pd
ggsave( "results_output/plots_mi/p_pr_pd_psychological_distress_imp.svg", plot = p_pr_pd, width = 9, height = 6 )
```

### 4. Suicidal Thoughts and Attempts
#### 4.1. Prevalence by sexual identity
```{r}
plot_data <- prevalence_imp %>% 
  filter( 
    outcome %in% c( "suicidal_thoughts", "suicide_attempts" )
    ) %>%
  mutate(
    year = as.factor( year ),
    lower_ci = if_else( 
      lower_ci < 0, 
      0, 
      lower_ci 
      )
    )

summary( plot_data )

p_prevalence <- ggplot( 
  plot_data,
  
  aes( 
    x = year, 
    y = point_estimate, 
    color = sexual_identity, 
    group = sexual_identity 
    ) 
  ) +
  
  geom_errorbar( 
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.14 
    ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 2 ) +
  
  scale_x_discrete( 
    expand = expansion( 
      mult = c( 0.08, 0.05 ) 
      ) 
    ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" 
      ) 
    ) +
  
  labs(
    x = "Survey Year",
    y = "Prevalence (95% CI)",
    color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom"
    ) +
  
  facet_wrap(
    ~ outcome,
    ncol = 2,
    scales = "free",
    labeller = labeller(
      outcome = c(
        "suicidal_thoughts" = "Suicidal Thoughts",
        "suicide_attempts" = "Suicide Attempts" 
        ) 
      )
    ) +
  
  # plot_data %>%
  # group_by( outcome ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci ),
  #   max_upper_ci = max( upper_ci )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      outcome == "suicidal_thoughts" ~ 
        scale_y_continuous( 
          limits = c( 0, 0.75 ),
          breaks = seq( 0, 0.75, 0.15 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion( 
            mult = c( 0.05, 0.01 ) 
            )
          ),
      
      outcome == "suicide_attempts" ~ 
        scale_y_continuous( 
          limits = c( 0, 0.4 ),
          breaks = seq( 0, 0.4, 0.1 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion( 
            mult = c( 0.05, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_capped_cart( 
    left = 'both', 
    bottom = 'both' 
    ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_suicide_imp.svg", plot = p_prevalence, width = 9.5, height = 5 )
```

#### 4.2. PR/PD by sexual identity
```{r}
# suicidal thoughts
plot_data <- pr_pd_imp %>%
  filter( 
    outcome == "suicidal_thoughts"
    ) %>%
  mutate(
    year = as.factor( year )
  )

summary( plot_data )

plot_data %>%
  filter( 
    estimate_type == "Prevalence Difference" 
    ) %>%
  summary()

plot_data %>% 
  filter( 
    estimate_type == "Prevalence Ratio" 
    ) %>%
  summary()

p_pr_pd_thought <- ggplot(
  plot_data,
  
  aes( 
    x = year,
    y = point_estimate,
    color = exposure_model,
    group = exposure_model 
    ) 
  ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Ratio" 
      ),
    aes( 
      yintercept = 1 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Difference" 
      ),
    aes( 
      yintercept = 0 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_errorbar( 
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.14
    ) +
  
  geom_line( 
    linewidth = 0.8
    ) +
  
  geom_point(
    shape = 15,
    size = 2.5
    ) +
  
  scale_color_manual( 
    values = exposure_colors,
    labels = exposure_labels
    ) +
  
  labs( 
    x = "Survey Year",
    y = "Association Estimate (95% CI)",
    title = "Suicidal Thoughts",
    color = NULL
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom",
    plot.title = element_text( family = "Arial", size = 12, hjust = 0.5 )
    ) +
  
  facet_wrap(
    ~ estimate_type,
    ncol = 2,
    scales = "free" 
    ) +
  
  scale_x_discrete(
    limits = c( "2021", "2014", "2010", "2006", "2002" ),
    expand = expansion( 
      mult = c( 0.05, 0.05 ) 
      )
    ) +
  
  # plot_data %>%
  # group_by( estimate_type ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci ),
  #   max_upper_ci = max( upper_ci )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( 
          limits = c( 0.5, 3.5 ),
          breaks = seq( 0.5, 3.5, 0.5 ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( 
          limits = c( -10, 40 ),
          breaks = seq( -10, 40, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_flip()
  
p_pr_pd_thought

# suicide attempts
plot_data <- pr_pd_imp %>%
  filter( 
    outcome == "suicide_attempts"
    ) %>%
  mutate(
    year = as.factor( year )
  )

summary( plot_data )

plot_data %>%
  filter( 
    estimate_type == "Prevalence Difference" 
    ) %>%
  summary()

plot_data %>% 
  filter( 
    estimate_type == "Prevalence Ratio" 
    ) %>%
  summary()

p_pr_pd_attempt <- ggplot(
  plot_data,
  
  aes( 
    x = year,
    y = point_estimate,
    color = exposure_model,
    group = exposure_model 
    ) 
  ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Ratio" 
      ),
    aes( 
      yintercept = 1 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Difference" 
      ),
    aes( 
      yintercept = 0 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_errorbar( 
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.14
    ) +
  
  geom_line( 
    linewidth = 0.8
    ) +
  
  geom_point(
    shape = 15,
    size = 2.5
    ) +
  
  scale_color_manual( 
    values = exposure_colors,
    labels = exposure_labels
    ) +
  
  labs( 
    x = "Survey Year",
    y = "Association Estimate (95% CI)",
    title = "Suicide Attempts",
    color = NULL
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom",
    plot.title = element_text( family = "Arial", size = 12, hjust = 0.5 )
    ) +
  
  facet_wrap(
    ~ estimate_type,
    ncol = 2,
    scales = "free" 
    ) +
  
  scale_x_discrete(
    limits = c( "2021", "2014", "2010", "2006", "2002" ),
    expand = expansion( 
      mult = c( 0.05, 0.05 ) 
      )
    ) +
  
  # plot_data %>%
  # group_by( estimate_type ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci ),
  #   max_upper_ci = max( upper_ci )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( 
          limits = c( 0, 8 ),
          breaks = seq( 0, 8, 1 ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( 
          limits = c( -10, 30 ),
          breaks = seq( -10, 30, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_flip()
  
p_pr_pd_attempt

# combine plot
combined_plot <- 
  ( p_pr_pd_thought / plot_spacer() / p_pr_pd_attempt ) +
  plot_layout( guides = "collect",
               heights = c( 1, 0.02, 1 ) ) &
  theme( legend.position = "right" )
  
combined_plot
ggsave( "results_output/plots_mi/p_pr_pd_suicide_imp.svg", plot = combined_plot, width = 11, height = 10 )
```

### 5. Use of Antidepressants and Anxiolytics
#### 5.1. Prevalence by sexual identity
```{r}
plot_data <- prevalence_imp %>% 
  filter( 
    outcome %in% c( "antidepressant", "anxiolytic" )
    ) %>%
  mutate(
    lower_ci = if_else( 
      lower_ci < 0, 
      0, 
      lower_ci 
      )
    )

summary( plot_data )

p_prevalence <- ggplot( 
  plot_data,
  
  aes( 
    x = year, 
    y = point_estimate, 
    color = sexual_identity,
    linetype = sample_type,
    group = interaction( sexual_identity, sample_type )
    ) 
  ) +
  
  geom_errorbar(
    data = plot_data %>%
      filter( 
        sample_type == "survey" 
        ),
    aes( 
      ymin = lower_ci, 
      ymax = upper_ci 
      ), 
    width = 0.5 
    ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 2 ) +
  
  scale_x_continuous(
    breaks = seq( 2006, 2021, 3 ),
    expand = expansion( 
      mult = c( 0.08, 0.05 ) 
      ) 
    ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" 
      ) 
    ) +
  
  scale_linetype_manual(
    values = c(
      "CS" = "dotted",
      "survey" = "solid" 
      ),
    
    labels = c(
      "CS" = "Cross-Sectional Samples",
      "survey" = "Survey Samples" 
      ) 
    ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence (95% CI)",
    color = NULL,
    linetype = NULL
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom",
    legend.box = "vertical",
    legend.spacing.y = unit( -0.3, "cm" ),
    legend.box.just = "center"
    ) +
  
  guides(
    linetype = guide_legend(
      order = 1,
      nrow = 1
      ),
    
    color = guide_legend(
      order = 2,
      nrow = 1
      )
    ) +
  
  facet_wrap(
    ~ outcome,
    ncol = 2,
    scales = "free",
    labeller = labeller(
      outcome = c(
        "antidepressant" = "Antidepressant Use",
        "anxiolytic" = "Anxiolytic Use" 
        ) 
      )
    ) +
  
  # plot_data %>%
  # group_by( outcome ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci ),
  #   max_upper_ci = max( upper_ci )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      outcome == "antidepressant" ~ 
        scale_y_continuous( 
          limits = c( 0, 0.3 ),
          breaks = seq( 0, 0.3, 0.1 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion( 
            mult = c( 0.05, 0.01 ) 
            ) 
          ),
      
      outcome == "anxiolytic" ~ 
        scale_y_continuous( 
          limits = c( 0, 0.2 ),
          breaks = seq( 0, 0.2, 0.1 ),
          labels = scales::percent_format( accuracy = 1 ),
          expand = expansion( 
            mult = c( 0.05, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_capped_cart( 
    left = 'both', 
    bottom = 'both' 
    ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_medication_imp.svg", plot = p_prevalence, width = 10, height = 5 )
```

#### 5.2. PR/PD by sexual identity
```{r}
# antidepressant use
plot_data <- pr_pd_imp %>%
  filter( 
    outcome == "antidepressant"
    )

plot_data %>%
  filter( 
    estimate_type == "Prevalence Difference" 
    ) %>%
  summary()

plot_data %>% 
  filter( 
    estimate_type == "Prevalence Ratio" 
    ) %>%
  summary()

plot_data <- plot_data %>%
  mutate(
    pd_upper_clipped = 
      sample_type == "survey" &
      estimate_type == "Prevalence Difference" &
      upper_ci > 20,
    
    upper_ci = if_else( 
      pd_upper_clipped, 
      20, 
      upper_ci 
      ),
    
    pr_upper_clipped = 
      sample_type == "survey" &
      estimate_type == "Prevalence Ratio" & 
      upper_ci > 6,
    
    upper_ci = if_else( 
      pr_upper_clipped, 
      6, 
      upper_ci 
      )
  )


p_pr_pd_antidepressant <- ggplot(
  plot_data,
  
  aes( 
    x = year,
    y = point_estimate,
    color = exposure_model,
    linetype = sample_type,
    group = interaction( exposure_model, sample_type )
    ) 
  ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Ratio" 
      ),
    aes( 
      yintercept = 1 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Difference" 
      ),
    aes( 
      yintercept = 0 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  # error bar 
  geom_segment(
    data = plot_data %>%
      filter( sample_type == "survey" ),
    aes(
      x = year,
      xend = year,
      y = lower_ci,
      yend = upper_ci
    ),
    linewidth = 0.4
  ) +
  
  geom_segment(
    data = plot_data %>%
      filter(
        sample_type == "survey"
      ),
    aes(
      x = year - 0.25,
      xend = year + 0.25,
      y = lower_ci,
      yend = lower_ci
    ),
    linewidth = 0.4
  ) +
  
  geom_segment(
    data = plot_data %>%
      filter(
        sample_type == "survey",
        !pd_upper_clipped,
        !pr_upper_clipped
      ),
    aes(
      x = year - 0.25,
      xend = year + 0.25,
      y = upper_ci,
      yend = upper_ci
    ),
    linewidth = 0.4
  ) +
  
  geom_segment(
    data = plot_data %>%
      filter( pd_upper_clipped | 
                pr_upper_clipped ),
    aes(
      x = year,
      xend = year,
      y = upper_ci - 0.3,
      yend = upper_ci
    ),
    
    arrow = arrow(
      length = unit( 2.5, "mm" ),
      type = "closed"
    ),
    linewidth = 0.4,
    show.legend = FALSE
  ) +
  
  geom_line( 
    linewidth = 0.8
    ) +
  
  geom_point(
    shape = 15,
    size = 2.5
    ) +
  
  scale_color_manual( 
    values = exposure_colors,
    labels = exposure_labels
    ) +
  
  scale_linetype_manual(
    values = c(
      "CS" = "dotted",
      "survey" = "solid" 
      ),
    
    labels = c(
      "CS" = "Cross-Sectional Samples",
      "survey" = "Survey Samples" 
      ) 
    ) +
  

  labs( 
    x = "Calendar Year",
    y = "Association Estimate (95% CI)",
    title = "Antidepressant Use",
    color = NULL,
    linetype = NULL
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    plot.title = element_text( family = "Arial", size = 12, hjust = 0.5 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 )
    ) +
  
  guides(
    linetype = guide_legend(
      order = 1,
      nrow = 2
      ),
    
    color = guide_legend(
      order = 2,
      nrow = 4
      )
    ) +
  
  facet_wrap(
    ~ estimate_type,
    ncol = 2,
    scales = "free" 
    ) +
  
  scale_x_continuous( 
    trans = "reverse",
    breaks = seq( 2006, 2021, 3 ),
    expand = expansion( mult = c( 0.05, 0.05 ) ) ) +
  
  # plot_data %>%
  # group_by( estimate_type ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci ),
  #   max_upper_ci = max( upper_ci )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( 
          limits = c( 0, 6 ),
          breaks = seq( 0, 6, 1 ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( 
          limits = c( -10, 20 ),
          breaks = seq( -10, 20, 10 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_flip()
  
p_pr_pd_antidepressant

# anxiolytic use
plot_data <- pr_pd_imp %>%
  filter( 
    outcome == "anxiolytic"
    )

plot_data %>%
  filter( 
    estimate_type == "Prevalence Difference" 
    ) %>%
  summary()

plot_data %>% 
  filter( 
    estimate_type == "Prevalence Ratio" 
    ) %>%
  summary()

plot_data <- plot_data %>%
  mutate(
    pr_upper_clipped = 
      sample_type == "survey" &
      estimate_type == "Prevalence Ratio" & 
      upper_ci > 8,
    
    upper_ci = if_else( 
      pr_upper_clipped, 
      8, 
      upper_ci 
      )
  )


p_pr_pd_anxiolytic <- ggplot(
  plot_data,
  
  aes( 
    x = year,
    y = point_estimate,
    color = exposure_model,
    linetype = sample_type,
    group = interaction( exposure_model, sample_type )
    ) 
  ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Ratio" 
      ),
    aes( 
      yintercept = 1 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  geom_hline( 
    data = data.frame( 
      estimate_type = "Prevalence Difference" 
      ),
    aes( 
      yintercept = 0 
      ),
    linetype = "dashed",
    color = "grey80",
    linewidth = 0.4 
    ) +
  
  # error bar 
  geom_segment(
    data = plot_data %>%
      filter( sample_type == "survey" ),
    aes(
      x = year,
      xend = year,
      y = lower_ci,
      yend = upper_ci
    ),
    linewidth = 0.4
  ) +
  
  geom_segment(
    data = plot_data %>%
      filter(
        sample_type == "survey"
      ),
    aes(
      x = year - 0.25,
      xend = year + 0.25,
      y = lower_ci,
      yend = lower_ci
    ),
    linewidth = 0.4
  ) +
  
  geom_segment(
    data = plot_data %>%
      filter(
        sample_type == "survey",
        !pr_upper_clipped
      ),
    aes(
      x = year - 0.25,
      xend = year + 0.25,
      y = upper_ci,
      yend = upper_ci
    ),
    linewidth = 0.4
  ) +
  
  geom_segment(
    data = plot_data %>%
      filter( 
        pr_upper_clipped 
        ),
    aes(
      x = year,
      xend = year,
      y = upper_ci - 0.3,
      yend = upper_ci
    ),
    
    arrow = arrow(
      length = unit( 2.5, "mm" ),
      type = "closed"
    ),
    linewidth = 0.4,
    show.legend = FALSE
  ) +
  
  geom_line( 
    linewidth = 0.8
    ) +
  
  geom_point(
    shape = 15,
    size = 2.5
    ) +
  
  scale_color_manual( 
    values = exposure_colors,
    labels = exposure_labels
    ) +
  
  scale_linetype_manual(
    values = c(
      "CS" = "dotted",
      "survey" = "solid" 
      ),
    
    labels = c(
      "CS" = "Cross-Sectional Samples",
      "survey" = "Survey Samples" 
      ) 
    ) +
  

  labs( 
    x = "Calendar Year",
    y = "Association Estimate (95% CI)",
    title = "Anxiolytic Use",
    color = NULL,
    linetype = NULL
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    plot.title = element_text( family = "Arial", size = 12, hjust = 0.5 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 )
    ) +
  
  guides(
    linetype = guide_legend(
      order = 1,
      nrow = 2
      ),
    
    color = guide_legend(
      order = 2,
      nrow = 4
      )
    ) +
  
  facet_wrap(
    ~ estimate_type,
    ncol = 2,
    scales = "free" 
    ) +
  
  scale_x_continuous( 
    trans = "reverse",
    breaks = seq( 2006, 2021, 3 ),
    expand = expansion( mult = c( 0.05, 0.05 ) ) ) +
  
  # plot_data %>%
  # group_by( estimate_type ) %>%
  # summarise(
  #   min_lower_ci = min( lower_ci ),
  #   max_upper_ci = max( upper_ci )
  # )
  
  ggh4x::facetted_pos_scales( 
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( 
          limits = c( 0, 8 ),
          breaks = seq( 0, 8, 1 ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( 
          limits = c( -5, 15 ),
          breaks = seq( -5, 15, 5 ),
          labels = scales::label_number( suffix = "%" ),
          expand = expansion( 
            mult = c( 0.08, 0.01 ) 
            ) 
          ) 
      ) 
    ) +
  
  coord_flip()
  
p_pr_pd_anxiolytic

# combine plot
combined_plot <- 
  ( p_pr_pd_antidepressant / plot_spacer() / p_pr_pd_anxiolytic ) +
  plot_layout( guides = "collect",
               heights = c( 1, 0.02, 1 ) ) &
  theme( legend.position = "right" )
  
combined_plot
ggsave( "results_output/plots_mi/p_pr_pd_medication_imp.svg", plot = combined_plot, width = 11, height = 11 )
```

##### 2.1.2. By sex
###### 2.1.2.1. Prepare data
```{r}
# by sexual identity and sex
prevalence_2002_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_2002_by_sex_imp.xlsx" ) )
prevalence_2006_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_2006_by_sex_imp.xlsx" ) )
prevalence_2010_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_2010_by_sex_imp.xlsx" ) )
prevalence_2014_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_2014_by_sex_imp.xlsx" ) )
prevalence_2021_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_2021_by_sex_imp.xlsx" ) )

# merge and clean data
prevalence_indi_by_sex_imp <- bind_rows(
  prevalence_2002_by_sex_imp,
  prevalence_2006_by_sex_imp,
  prevalence_2010_by_sex_imp,
  prevalence_2014_by_sex_imp,
  prevalence_2021_by_sex_imp 
  ) %>%
  filter( 
    sexual_identity != "Other",
    outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ) 
    ) %>%
  mutate( 
    sexual_identity = factor( sexual_identity, levels = c( "Heterosexual", "Homosexual", "Bisexual" ) ),
    sex = factor( sex, levels = c( "Female", "Male" ) ),
    outcome = factor( outcome, levels = c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ) ),
    year = as.character( year ) )

summary( prevalence_indi_by_sex_imp )
```

###### 2.1.2.2. Psychological distress
```{r}
prevalence_indi_by_sex_imp %>%
  filter( outcome %in% c( "psychological_distress" ) ) %>%
  summary()

p_prevalence <- ggplot( 
  prevalence_indi_by_sex_imp %>%
    filter( outcome %in% c( "psychological_distress" ) ),
  
  aes( x = year, y = point_estimate, color = sexual_identity, group = sexual_identity ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 1, 5 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.08, 0.02 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.8 ),
                      breaks = c( seq( 0, 0.8, 0.2 ) ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( values = c(
    "Heterosexual" = "#F8766D",
    "Bisexual" = "#C77CFF",
    "Homosexual" = "#00BFC4" ),
    
    guide = guide_legend( nrow = 1 ) ) +
  
  labs(
    x = "Survey Year",
    y = "Prevalence of Psychological Distress (95% CI)",
    color = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_psychological_distress_by_sex_imp.svg", plot = p_prevalence, width = 9, height = 6 )
```

###### 2.1.2.3. Suicidal thoughts
```{r}
prevalence_indi_by_sex_imp %>%
  filter( outcome %in% c( "suicidal_thoughts" ) ) %>%
  summary()

p_prevalence <- ggplot( 
  prevalence_indi_by_sex_imp %>%
    filter( outcome %in% c( "suicidal_thoughts" ) ),
  
  aes( x = year, y = point_estimate, color = sexual_identity, group = sexual_identity ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 1, 5 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.08, 0.02 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.8 ),
                      breaks = c( seq( 0, 0.8, 0.2 ) ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( values = c(
    "Heterosexual" = "#F8766D",
    "Bisexual" = "#C77CFF",
    "Homosexual" = "#00BFC4" ),
    
    guide = guide_legend( nrow = 1 ) ) +
  
  labs(
    x = "Survey Year",
    y = "Prevalence of Suicidal Thoughts (95% CI)",
    color = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_suicidal_thoughts_by_sex_imp.svg", plot = p_prevalence, width = 9, height = 6 )
```

###### 2.1.2.4. Suicide attempts
```{r}
prevalence_indi_by_sex_imp %>%
  filter( outcome %in% c( "suicide_attempts" ) ) %>%
  summary()

plot_data <- prevalence_indi_by_sex_imp %>% 
  filter( outcome %in% c( "suicide_attempts" ) ) %>%
  mutate(
    lower_ci = if_else( lower_ci < 0, 0, lower_ci )
    )

p_prevalence <- ggplot( 
  plot_data,
  
  aes( x = year, y = point_estimate, color = sexual_identity, group = sexual_identity ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 1, 5 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.08, 0.02 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.4 ),
                      breaks = c( seq( 0, 0.4, 0.1 ) ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( values = c(
    "Heterosexual" = "#F8766D",
    "Bisexual" = "#C77CFF",
    "Homosexual" = "#00BFC4" ),
    
    guide = guide_legend( nrow = 1 ) ) +
  
  labs(
    x = "Survey Year",
    y = "Prevalence of Suicide Attempts (95% CI)",
    color = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_suicide_attempts_by_sex_imp.svg", plot = p_prevalence, width = 9, height = 6 )
```

#### 2.2. Prevalence ratio and difference
##### 2.2.1. By sexual identity
###### 2.2.1.1. Prepare data
```{r}

```

###### 2.2.1.2. Suicidal thoughts
```{r}
plot_data <- pr_pd_imp %>% 
  filter( outcome %in% c( "suicidal_thoughts" ) )
summary( plot_data )

plot_data %>%
  filter( estimate_type == "Prevalence Difference" ) %>%
  summary()

plot_data %>% 
  filter( estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd <- ggplot(
  plot_data,
  
  aes( x = year,
       y = point_estimate,
       color = exposure_model,
       group = exposure_model ) ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey80",
              linewidth = 0.4 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey80",
              linewidth = 0.4 ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 1, 5 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.6 ) +
  
  geom_point(
    shape = 15,
    size = 2
    ) +
  
  scale_color_manual( 
    values = exposure_colors,
    labels = exposure_labels
    ) +
  
  labs( 
    x = "Calendar Year",
    y = "Association Estimate (95% CI)",
    color = NULL,
    linetype = NULL 
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" 
    ) +
  
  facet_wrap(
    ~ estimate_type,
    ncol = 2,
    scales = "free" 
    ) + 
  
  scale_x_discrete( 
    limits = c( "2021", "2014", "2010", "2006", "2002" ),
    expand = expansion( mult = c( 0.05, 0.05 ) ) ) +
  
  ggh4x::facetted_pos_scales( 
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( limits = c( 0, 4 ),
                            breaks = c( seq( 0, 4, 1 ) ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( limits = c( -20, 40 ),
                            breaks = c( seq( -20, 40, 10 ) ),
                            labels = scales::label_number( suffix = "%" ),
                            expand = expansion( mult = c( 0.05, 0.01 ) ) ) ) ) +
  
  coord_flip() +
  
  guides(
    color = guide_legend(
      order = 1,
      nrow = 2,
      byrow = TRUE,
      override.aes = list(
        size = 2,
        linetype = 0
      )
    ),
    
    linetype = guide_legend(
      order = 2,
      nrow = 2,
      keywidth = unit( 0.8, "cm" )
    )
  )
  
p_pr_pd
ggsave( "results_output/plots_mi/p_pr_pd_self_report_imp.svg", plot = p_pr_pd, width = 9, height = 6 )
```

###### 2.2.1.2. Self-reported
```{r}
pr_pd_imp %>% 
  filter( outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ),
          estimate_type == "Prevalence Difference" ) %>%
  summary()

pr_pd_imp %>% 
  filter( outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ),
          estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd <- ggplot(
  pr_pd_imp %>%
    filter( outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ) ),
  
  aes( x = year, y = point_estimate, color = exposure_model, group = exposure_model ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 1, 5 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.05, 0.02 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 1 ) ) +
  
  labs( x = "Survey Year",
        y = "Association Estimate (95% CI)",
        color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ outcome,
              switch = "y",
              scales = "free_y",
              labeller = labeller(
                outcome = c(
                  "psychological_distress" = "Psychological Distress",
                  "suicidal_thoughts" = "Suicidal Thoughts",
                  "suicide_attempts" = "Suicide Attempts" ) ) ) +
  
  ggh4x::facetted_pos_scales( y = list(
    estimate_type == "Prevalence Ratio" ~ scale_y_continuous( limits = c( 0, 8 ), 
                                                              breaks = c( seq( 0, 8, 1 ) ), 
                                                              expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    estimate_type == "Prevalence Difference" ~ scale_y_continuous( limits = c( -20, 50 ), 
                                                                   breaks = c( seq( -20, 50, 10 ) ), 
                                                                   labels = scales::percent_format( accuracy = 1 ), 
                                                                   expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd
ggsave( "results_output/plots_mi/p_pr_pd_self_report_imp.svg", plot = p_pr_pd, width = 12, height = 7.5 )
```

##### 2.2.2. By sex
###### 2.2.2.1. Prepare data
```{r}
# among females
pr_female_2002_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2002_imp.xlsx' ) )
pr_female_2006_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2006_imp.xlsx' ) )
pr_female_2010_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2010_imp.xlsx' ) )
pr_female_2014_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2014_imp.xlsx' ) )
pr_female_2021_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2021_imp.xlsx' ) )

pr_female_imp <- bind_rows( pr_female_2002_imp,
                           pr_female_2006_imp,
                           pr_female_2010_imp,
                           pr_female_2014_imp,
                           pr_female_2021_imp ) %>%
  mutate( estimate_type = "Prevalence Ratio" )

pd_female_2002_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2002_imp.xlsx' ) )
pd_female_2006_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2006_imp.xlsx' ) )
pd_female_2010_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2010_imp.xlsx' ) )
pd_female_2014_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2014_imp.xlsx' ) )
pd_female_2021_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2021_imp.xlsx' ) )

pd_female_imp <- bind_rows( pd_female_2002_imp,
                           pd_female_2006_imp,
                           pd_female_2010_imp,
                           pd_female_2014_imp,
                           pd_female_2021_imp ) %>%
  mutate( estimate_type = "Prevalence Difference" )

# among males
pr_male_2002_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2002_imp.xlsx' ) )
pr_male_2006_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2006_imp.xlsx' ) )
pr_male_2010_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2010_imp.xlsx' ) )
pr_male_2014_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2014_imp.xlsx' ) )
pr_male_2021_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2021_imp.xlsx' ) )

pr_male_imp <- bind_rows( pr_male_2002_imp,
                         pr_male_2006_imp,
                         pr_male_2010_imp,
                         pr_male_2014_imp,
                         pr_male_2021_imp ) %>%
  mutate( estimate_type = "Prevalence Ratio" )

pd_male_2002_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2002_imp.xlsx' ) )
pd_male_2006_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2006_imp.xlsx' ) )
pd_male_2010_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2010_imp.xlsx' ) )
pd_male_2014_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2014_imp.xlsx' ) )
pd_male_2021_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2021_imp.xlsx' ) )

pd_male_imp <- bind_rows( pd_male_2002_imp,
                         pd_male_2006_imp,
                         pd_male_2010_imp,
                         pd_male_2014_imp,
                         pd_male_2021_imp ) %>%
  mutate( estimate_type = "Prevalence Difference" )

# merge data
pr_pd_by_sex_imp <- bind_rows( pr_female_imp, pd_female_imp, pr_male_imp, pd_male_imp ) %>%
  filter( exposure_level != "Other" ) %>%
  mutate( outcome = as.factor( outcome ),
          year = as.factor( year ),
          sex = as.factor( sex ),
          exposure_level = as.factor( exposure_level ),
          model_type = recode_factor( model_type, "crude" = "Crude", "adjusted" = "Adjusted" ),
          estimate_type = factor( estimate_type, levels = c( "Prevalence Ratio", "Prevalence Difference" ) ),
          exposure_model = interaction( exposure_level, model_type, sep = "_" ),
          exposure_model = factor( exposure_model, levels = c(
            "Bisexual_Crude",
            "Homosexual_Crude",
            "Bisexual_Adjusted",
            "Homosexual_Adjusted" ) ) )

pr_pd_by_sex_imp <- pr_pd_by_sex_imp %>%
  mutate(
    across(
      c( estimate, lower_ci, upper_ci ),
      ~ ifelse(
        outcome == "suicide_attempts" &
          sex == "Male" &
          (
            ( year == 2002 & exposure_level == "Bisexual" ) | # four PR data points were not estimable due to zero events
            ( year == 2014 & exposure_level == "Homosexual" )
            ),
        NA_real_,
          .
        )
      )
    )

# sanity check
pr_pd_by_sex_imp %>%
  filter( is.na( estimate ) )
summary( pr_pd_by_sex_imp )
```

###### 2.2.2.2. Psychological distress
```{r}
pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "psychological_distress" ),
          estimate_type == "Prevalence Difference" ) %>%
  summary()

pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "psychological_distress" ),
          estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd_by_sex <- ggplot(
  pr_pd_by_sex_imp %>%
    filter( outcome %in% c( "psychological_distress" ) ),
  
  aes( x = year, y = estimate, color = exposure_model, group = exposure_model ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 1, 5 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.05, 0.03 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  labs( x = "Survey Year",
        y = "Association Estimate of Psychological Distress (95% CI)",
        color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ sex,
              switch = "y",
              scales = "free_y" ) +
  
  ggh4x::facetted_pos_scales( y = list(
    estimate_type == "Prevalence Ratio" ~ scale_y_continuous( limits = c( 0, 4 ), 
                                                              breaks = c( seq( 0, 4, 1 ) ), 
                                                              expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    estimate_type == "Prevalence Difference" ~ scale_y_continuous( limits = c( -0.3, 0.5 ), 
                                                                   breaks = c( seq( -0.3, 0.5, 0.1 ) ), 
                                                                   labels = scales::percent_format( accuracy = 1 ), 
                                                                   expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd_by_sex
ggsave( "results_output/plots_mi/p_pr_pd_psychological_distress_by_sex_imp.svg", plot = p_pr_pd_by_sex, width = 9, height = 7.5 )
```

###### 2.2.2.3. Suicidal thoughts
```{r}
pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "suicidal_thoughts" ),
          estimate_type == "Prevalence Difference" ) %>%
  summary()

pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "suicidal_thoughts" ),
          estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd_by_sex <- ggplot(
  pr_pd_by_sex_imp %>%
    filter( outcome %in% c( "suicidal_thoughts" ) ),
  
  aes( x = year, y = estimate, color = exposure_model, group = exposure_model ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 1, 5 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.05, 0.03 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  labs( x = "Survey Year",
        y = "Association Estimate of Suicidal Thoughts (95% CI)",
        color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ sex,
              switch = "y",
              scales = "free_y" ) +
  
  ggh4x::facetted_pos_scales( y = list(
    estimate_type == "Prevalence Ratio" ~ scale_y_continuous( limits = c( 0, 5.1 ), 
                                                              breaks = c( seq( 0, 5, 1 ) ), 
                                                              expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    estimate_type == "Prevalence Difference" ~ scale_y_continuous( limits = c( -0.2, 0.6 ), 
                                                                   breaks = c( seq( -0.2, 0.6, 0.1 ) ), 
                                                                   labels = scales::percent_format( accuracy = 1 ), 
                                                                   expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd_by_sex
ggsave( "results_output/plots_mi/p_pr_pd_suicidal_thoughts_by_sex_imp.svg", plot = p_pr_pd_by_sex, width = 9, height = 7.5 )
```

###### 2.2.2.4. Suicide attempts
```{r}
pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "suicide_attempts" ),
          estimate_type == "Prevalence Difference" ) %>%
  summary()

pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "suicide_attempts" ),
          estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd_by_sex <- ggplot(
  pr_pd_by_sex_imp %>%
    filter( outcome %in% c( "suicide_attempts" ) ),
  aes( x = year, y = estimate, color = exposure_model, group = exposure_model ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 1, 5 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.05, 0.03 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  labs( x = "Survey Year",
        y = "Association Estimate of Suicide Attempts (95% CI)",
        color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ sex,
              switch = "y",
              scales = "free_y" ) +
  
  ggh4x::facetted_pos_scales( y = list(
    estimate_type == "Prevalence Ratio" ~ scale_y_continuous( limits = c( 0, 20 ), 
                                                              breaks = c( seq( 0, 20, 5 ) ), 
                                                              expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    estimate_type == "Prevalence Difference" ~ scale_y_continuous( limits = c( -0.2, 0.4 ), 
                                                                   breaks = c( seq( -0.2, 0.4, 0.1 ) ), 
                                                                   labels = scales::percent_format( accuracy = 1 ), 
                                                                   expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd_by_sex
ggsave( "results_output/plots_mi/p_pr_pd_suicide_attempts_by_sex_imp.svg", plot = p_pr_pd_by_sex, width = 9, height = 7.5 )
```

### 3. Register-Based Outcomes (Survey and Cross-Sectional Samples)
#### 3.1. Annual prevalence
##### 3.1.1. By sexual identity
###### 3.1.1.1. Prepare data
```{r}
# individual surveys
overall_prevalence_2006_imp <- read_xlsx( 
  here( "results_output/results_mi/overall_prevalence_2006_imp.xlsx" ) 
  ) %>%
  mutate( sample_type = "individual" )

overall_prevalence_2010_imp <- read_xlsx( 
  here( "results_output/results_mi/overall_prevalence_2010_imp.xlsx" ) 
  ) %>%
  mutate( sample_type = "individual" )

overall_prevalence_2014_imp <- read_xlsx( 
  here( "results_output/results_mi/overall_prevalence_2014_imp.xlsx" ) 
  ) %>%
  mutate( sample_type = "individual" )

overall_prevalence_2021_imp <- read_xlsx( 
  here( "results_output/results_mi/overall_prevalence_2021_imp.xlsx" ) 
  ) %>%
  mutate( sample_type = "individual" )

prevalence_survey_imp <- bind_rows( 
  overall_prevalence_2006_imp,
  overall_prevalence_2010_imp,
  overall_prevalence_2014_imp,
  overall_prevalence_2021_imp 
  )

str( prevalence_survey_imp )

prevalence_survey_imp %>%
  group_by( year ) %>%
  count( outcome ) %>%
  View()

# pooled sample
prevalence_poo_cs_imp <- read_xlsx( here( "results_output/results_mi/prevalence_poo_cs_imp.xlsx" ) ) %>%
  mutate( sample_type = "pooled",
          outcome = recode( 
            outcome,
            antidepressant_use = "antidepressant",
            anxiolytic_use = "anxiolytic"
            ) 
          )

str( prevalence_poo_cs_imp )

prevalence_poo_cs_imp %>%
  group_by( year ) %>%
  count( outcome ) %>%
  View()

# merge and clean data
ann_prevalence_imp <- bind_rows( 
  prevalence_survey_imp,
  prevalence_poo_cs_imp 
  ) %>%
  filter( sexual_identity != "Other",
          outcome %in% c( "antidepressant", "anxiolytic", "depression", "anxiety", "stress_related" ) ) %>%
  mutate( 
    sexual_identity = factor( sexual_identity, levels = c( "Heterosexual", "Homosexual", "Bisexual" ) ),
    outcome = as.factor( outcome ),
    year = as.integer( year ),
    sample_type = as.factor( sample_type ) )

summary( ann_prevalence_imp )
```

###### 3.1.1.3. Other register-based outcomes
```{r}
ann_prevalence_imp %>%
  filter( outcome %in% c( "depression" ),
          sample_type == "individual" ) %>%
  summary()

ann_prevalence_imp %>%
  filter( outcome %in% c( "anxiety" ),
          sample_type == "individual" ) %>%
  summary()

ann_prevalence_imp %>%
  filter( outcome %in% c( "stress_related" ),
          sample_type == "individual" ) %>%
  summary()

plot_data <- ann_prevalence_imp %>% 
  filter( outcome %in% c( "depression", "anxiety", "stress_related" ) ) %>%
  mutate(
    outcome = factor(
      outcome,
      levels = c( "depression", "anxiety", "stress_related" )
    )
  ) %>%
  mutate(
    lower_ci = if_else( sample_type == "individual" & lower_ci < 0, 0, lower_ci )
    )

p_prevalence <- ggplot( 
  plot_data,
  aes( x = year, y = point_estimate, color = sexual_identity, linetype = sample_type, group = interaction( sexual_identity, sample_type ) ) ) +
  
  geom_errorbar( data = plot_data %>%
                   filter( sample_type == "individual" ),
                 aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 2003, 2019 ) ) * 0.03 ) +

  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
      "pooled" = "Cross-Sectional Samples",
      "individual" = "Survey Samples" ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence (95% CI)",
    color = NULL,
    linetype = NULL ) +
  
  facet_wrap( ~ outcome,
              ncol = 2,
              axes = "all",
              scales = "free",
              labeller = labeller(
                outcome = c(
                  "depression" = "Depression",
                  "anxiety" = "Anxiety Disorders",
                  "stress_related" = "Stress-Related Disorders" ) ) ) +
  
  ggh4x::facetted_pos_scales( 
    x = list(
      outcome %in% c( "depression", "anxiety", "stress_related" ) ~
        scale_x_continuous( breaks = seq( 2003, 2019, 4 ),
                            limits = c( 2003, 2019 ),
                            expand = expansion( mult = c( 0.08, 0.05 ) ) ) ),
    
    y = list(
      outcome == "depression" ~ 
        scale_y_continuous( limits = c( 0, 0.2 ),
                            breaks = c( seq( 0, 0.2, 0.05 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
      
      outcome == "anxiety" ~ 
        scale_y_continuous( limits = c( 0, 0.2 ),
                            breaks = c( seq( 0, 0.2, 0.05 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
      
      outcome == "stress_related" ~ 
        scale_y_continuous( limits = c( 0, 0.1 ),
                            breaks = c( seq( 0, 0.1, 0.05 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_indi_cs_dia_imp.svg", plot = p_prevalence, width = 10, height = 8 )
```

##### 3.1.2. By sex
###### 3.1.2.1. Prepare data
```{r}
# individual surveys
prevalence_2002_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_2002_by_sex_imp.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" ) %>% 
  mutate( sample_type = "individual" )

prevalence_2006_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_2006_by_sex_imp.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" ) %>% 
  mutate( sample_type = "individual" )

prevalence_2010_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_2010_by_sex_imp.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" ) %>% 
  mutate( sample_type = "individual" )

prevalence_2014_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_2014_by_sex_imp.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2014 ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" ) %>% 
  mutate( sample_type = "individual" )

prevalence_2021_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_2021_by_sex_imp.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2021 ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" ) %>% 
  mutate( sample_type = "individual" )

# pooled sample
prevalence_poo_cs_by_sex_imp <- read_xlsx( here( "results_output/results_mi/prevalence_poo_cs_by_sex_imp.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_baseline ) %>%
  mutate( sample_type = "pooled",
          year = as.character( year ),
          outcome = recode( outcome,
                            antidepressant_use = "antidepressant",
                            anxiolytic_use = "anxiolytic" 
                            ) 
          )

summary( prevalence_poo_cs_by_sex_imp )

# merge and clean data
ann_prevalence_by_sex_imp <- bind_rows( 
  prevalence_2002_by_sex_imp,
  prevalence_2006_by_sex_imp,
  prevalence_2010_by_sex_imp,
  prevalence_2014_by_sex_imp,
  prevalence_2021_by_sex_imp,
  prevalence_poo_cs_by_sex_imp ) %>%
  filter( sexual_identity != "Other",
          outcome %in% c( "antidepressant", "anxiolytic", "depression", "anxiety", "stress_related" ) ) %>%
  mutate( 
    sexual_identity = factor( sexual_identity, levels = c( "Heterosexual", "Homosexual", "Bisexual" ) ),
    outcome = as.factor( outcome ),
    sex = factor( sex, levels = c( "Female", "Male" ) ),
    year = as.integer( year ),
    sample_type = as.factor( sample_type ) ) 

ann_prevalence_by_sex_imp <- ann_prevalence_by_sex_imp %>%
  filter(
    !( sample_type == "individual" & outcome %in% c( "depression", "anxiety", "stress_related" ) & year == 2002 ),
    !( sample_type == "individual" & outcome %in% c( "depression", "anxiety", "stress_related" ) & year == 2021 ),
    !( sample_type == "individual" & outcome %in% c( "antidepressant", "anxiolytic" ) & year == 2002 )
  )

summary( ann_prevalence_by_sex_imp )
```

###### 3.1.2.2. Antidepressant use
```{r}
ann_prevalence_by_sex_imp %>%
  filter( outcome %in% c( "antidepressant" ),
          sample_type == "individual" ) %>%
  summary()

plot_data <- ann_prevalence_by_sex_imp %>% 
  filter( outcome %in% c( "antidepressant" ) )

p_prevalence <- ggplot( 
  plot_data,
  aes( x = year, y = point_estimate, color = sexual_identity, linetype = sample_type, group = interaction( sexual_identity, sample_type ) ) ) +
  
  geom_errorbar( data = plot_data %>%
                   filter( sample_type == "individual" ),
                 aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 2006, 2021 ) ) * 0.03 ) +

  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous( breaks = seq( 2006, 2021, 3 ),
                      expand = expansion( mult = c( 0.08, 0.02 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.4 ),
                      breaks = seq( 0, 0.4, 0.1 ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
  "pooled" = "Cross-Sectional Samples",
  "individual" = "Survey Samples" ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Antidepressant Use (95% CI)",
    color = NULL,
    linetype = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_indi_cs_med_antidepressant_by_sex_imp.svg", plot = p_prevalence, width = 10, height = 5 )
```

###### 3.1.2.3. Anxiolytic use
```{r}
ann_prevalence_by_sex_imp %>%
  filter( outcome %in% c( "anxiolytic" ),
          sample_type == "individual" ) %>%
  summary()

plot_data <- ann_prevalence_by_sex_imp %>% 
  filter( outcome %in% c( "anxiolytic" ) )

p_prevalence <- ggplot( 
  plot_data,
  aes( x = year, y = point_estimate, color = sexual_identity, linetype = sample_type, group = interaction( sexual_identity, sample_type ) ) ) +
  
  geom_errorbar( data = plot_data %>%
                   filter( sample_type == "individual" ),
                 aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 2006, 2021 ) ) * 0.03 ) +

  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous( breaks = seq( 2006, 2021, 3 ),
                      expand = expansion( mult = c( 0.08, 0.02 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.5 ),
                      breaks = seq( 0, 0.5, 0.1 ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
  "pooled" = "Cross-Sectional Samples",
  "individual" = "Survey Samples" ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Anxiolytic Use (95% CI)",
    color = NULL,
    linetype = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_indi_cs_med_anxiolytic_by_sex_imp.svg", plot = p_prevalence, width = 10, height = 5 )
```

###### 3.1.2.4. Depression
```{r}
ann_prevalence_by_sex_imp %>%
  filter( outcome %in% c( "depression" ),
          sample_type == "individual" ) %>%
  summary()

plot_data <- ann_prevalence_by_sex_imp %>% 
  filter( outcome %in% c( "depression" ) )

p_prevalence <- ggplot( 
  plot_data,
  aes( x = year, y = point_estimate, color = sexual_identity, linetype = sample_type, group = interaction( sexual_identity, sample_type ) ) ) +
  
  geom_errorbar( data = plot_data %>%
                   filter( sample_type == "individual" ),
                 aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 2003, 2019 ) ) * 0.03 ) +

  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous( breaks = seq( 2003, 2019, 4 ),
                      expand = expansion( mult = c( 0.08, 0.03 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.35 ),
                      breaks = seq( 0, 0.35, 0.05 ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
  "pooled" = "Cross-Sectional Samples",
  "individual" = "Survey Samples" ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Depression (95% CI)",
    color = NULL,
    linetype = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_indi_cs_dia_depression_by_sex_imp.svg", plot = p_prevalence, width = 10, height = 5 )
```

###### 3.1.2.5. Anxiety disorders
```{r}
ann_prevalence_by_sex_imp %>%
  filter( outcome %in% c( "anxiety" ),
          sample_type == "individual" ) %>%
  summary()

plot_data <- ann_prevalence_by_sex_imp %>% 
  filter( outcome %in% c( "anxiety" ) )

p_prevalence <- ggplot( 
  plot_data,
  aes( x = year, y = point_estimate, color = sexual_identity, linetype = sample_type, group = interaction( sexual_identity, sample_type ) ) ) +
  
  geom_errorbar( data = plot_data %>%
                   filter( sample_type == "individual" ),
                 aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 2003, 2019 ) ) * 0.03 ) +

  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous( breaks = seq( 2003, 2019, 4 ),
                      expand = expansion( mult = c( 0.08, 0.03 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.3 ),
                      breaks = seq( 0, 0.3, 0.1 ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
  "pooled" = "Cross-Sectional Samples",
  "individual" = "Survey Samples" ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Anxiety Disorders (95% CI)",
    color = NULL,
    linetype = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_indi_cs_dia_anxiety_by_sex_imp.svg", plot = p_prevalence, width = 10, height = 5 )
```

###### 3.1.2.6. Stress-related disorders
```{r}
ann_prevalence_by_sex_imp %>%
  filter( outcome %in% c( "stress_related" ),
          sample_type == "individual" ) %>%
  summary()

plot_data <- ann_prevalence_by_sex_imp %>% 
  filter( outcome %in% c( "stress_related" ) )

p_prevalence <- ggplot( 
  plot_data,
  aes( x = year, y = point_estimate, color = sexual_identity, linetype = sample_type, group = interaction( sexual_identity, sample_type ) ) ) +
  
  geom_errorbar( data = plot_data %>%
                   filter( sample_type == "individual" ),
                 aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 2003, 2019 ) ) * 0.03 ) +

  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous( breaks = seq( 2003, 2019, 4 ),
                      expand = expansion( mult = c( 0.08, 0.03 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.3 ),
                      breaks = seq( 0, 0.3, 0.1 ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
  "pooled" = "Cross-Sectional Samples",
  "individual" = "Survey Samples" ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Stress-Related Disorders (95% CI)",
    color = NULL,
    linetype = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_mi/p_prevalence_indi_cs_dia_stress_by_sex_imp.svg", plot = p_prevalence, width = 10, height = 5 )
```

#### 3.2. Prevalence ratio and difference
##### 3.2.1. By sexual identity
###### 3.2.1.1. Prepare data
```{r}
# prevalence difference
pd_2006_imp <- read_xlsx( here( 'results_output/results_mi/pd_2006_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Difference",
          sample_type = "individual" )

pd_2010_imp <- read_xlsx( here( 'results_output/results_mi/pd_2010_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Difference",
          sample_type = "individual" )

pd_2014_imp <- read_xlsx( here( 'results_output/results_mi/pd_2014_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Difference",
          sample_type = "individual" )

pd_2021_imp <- read_xlsx( here( 'results_output/results_mi/pd_2021_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Difference",
          sample_type = "individual" )

pd_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pd_poo_cs_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Difference",
          sample_type = "pooled",
          outcome = recode( outcome,
                            antidepressant_use = "antidepressant",
                            anxiolytic_use = "anxiolytic" 
                            ) )

# prevalence ratio
pr_2006_imp <- read_xlsx( here( 'results_output/results_mi/pr_2006_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Ratio",
          sample_type = "individual" )

pr_2010_imp <- read_xlsx( here( 'results_output/results_mi/pr_2010_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Ratio",
          sample_type = "individual" )

pr_2014_imp <- read_xlsx( here( 'results_output/results_mi/pr_2014_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Ratio",
          sample_type = "individual" )

pr_2021_imp <- read_xlsx( here( 'results_output/results_mi/pr_2021_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Ratio",
          sample_type = "individual" )

pr_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pr_poo_cs_imp.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Ratio",
          sample_type = "pooled",
          outcome = recode( outcome,
                            antidepressant_use = "antidepressant",
                            anxiolytic_use = "anxiolytic" 
                            ) )

# merge and clean data
pr_pd_imp <- bind_rows( 
  pd_2006_imp,
  pd_2010_imp,
  pd_2014_imp,
  pd_2021_imp,
  pd_poo_cs_imp,
  
  pr_2006_imp,
  pr_2010_imp,
  pr_2014_imp,
  pr_2021_imp,
  pr_poo_cs_imp ) %>%
  
  filter( sexual_identity != "Other",
          outcome %in% c( "antidepressant", "anxiolytic", "depression", "anxiety", "stress_related" ) ) %>%
  mutate( outcome = as.factor( outcome ),
          year = as.integer( year ),
          sexual_identity = as.factor( sexual_identity ),
          sample_type = as.factor( sample_type ),
          model_type = recode_factor( model_type, "crude" = "Crude", "adjusted" = "Adjusted" ),
          estimate_type = factor( estimate_type, levels = c( "Prevalence Ratio", "Prevalence Difference" ) ),
          exposure_model = interaction( sexual_identity, model_type, sep = "_" ),
          exposure_model = factor( exposure_model, levels = c(
            "Bisexual_Crude",
            "Bisexual_Adjusted",
            "Homosexual_Crude",
            "Homosexual_Adjusted" ) ) )

pr_pd_imp <- pr_pd_imp %>%
  mutate(
    across(
      c( point_estimate, lower_ci, upper_ci ),
      ~ ifelse(
        (
          outcome == "anxiety" &
          year == 2014 &
          sexual_identity == "Homosexual" &
          sample_type == "individual"
          ) |
          (
           outcome == "stress_related" &
           year == 2006 &
           sexual_identity == "Bisexual" &
           sample_type == "individual"
           ),
        NA_real_,
        .
        )
      )
    )

# sanity check
pr_pd_imp %>%
  filter( is.na( point_estimate ) )
summary( pr_pd_imp )
summary( pr_pd_imp %>% filter( sample_type == "individual" ) )
```



###### 3.2.1.3. Other register-based outcomes
```{r}
pr_pd_imp %>% 
  filter( outcome %in% c( "depression", "anxiety", "stress_related" ),
          estimate_type == "Prevalence Difference",
          sample_type == "individual" ) %>%
  summary()

pr_pd_imp %>% 
  filter( outcome %in% c( "depression", "anxiety", "stress_related" ),
          estimate_type == "Prevalence Ratio",
          sample_type == "individual" ) %>%
  summary()

plot_data <- pr_pd_imp %>% 
  filter( outcome %in% c( "depression", "anxiety", "stress_related" ) ) %>%
  mutate(
    outcome = factor(
      outcome,
      levels = c( "depression", "anxiety", "stress_related" )
    )
  )

p_pr_pd <- ggplot(
  plot_data,
  
  aes( 
    x = year, 
    y = point_estimate, 
    color = exposure_model, 
    linetype = sample_type, 
    group = interaction( exposure_model, sample_type ) 
    ) ) +
  
  geom_errorbar( 
    data = plot_data %>%
      filter( sample_type == "individual" ),
    aes( ymin = lower_ci, ymax = upper_ci ),
    width = diff( range( 2003, 2019 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_color_manual( 
    values = c(
      "Bisexual_Adjusted"   = "#C77CFF",
      "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
      "Homosexual_Adjusted" = "#00BFC4",
      "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
      "pooled" = "Cross-Sectional Samples",
      "individual" = "Survey Samples" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  labs( x = "Calendar Year",
        y = "Association Estimate (95% CI)",
        color = NULL,
        linetype = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ outcome,
              scales = "free",
              switch = "y",
              labeller = labeller(
                outcome = c(
                  "depression" = "Depression",
                  "anxiety" = "Anxiety Disorders",
                  "stress_related" = "Stress-Related Disorders" ) ) ) +
  
  ggh4x::facetted_pos_scales( 
    x = list(
      outcome %in% c( "depression", "anxiety", "stress_related" ) ~
        scale_x_continuous( breaks = seq( 2003, 2019, 4 ),
                            limits = c( 2003, 2019 ),
                            expand = expansion( mult = c( 0.05, 0.03 ) ) ) ),
    
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( limits = c( 0, 16 ),
                            breaks = c( seq( 0, 16, 4 ) ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( limits = c( -5, 15 ),
                            breaks = c( seq( -5, 15, 5 ) ),
                            labels = scales::label_number( suffix = "%" ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd
ggsave( "results_output/plots_mi/p_pr_pd_dia_imp.svg", plot = p_pr_pd, width = 12, height = 8 )
```

##### 3.2.2. By sex
###### 3.2.2.1. Prepare data
```{r}
# among females
# prevalence ratio
pr_female_2002_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2002_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_female_2006_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2006_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_female_2010_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2010_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_female_2014_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2014_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_female_2021_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_2021_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_female_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pr_female_poo_cs_imp.xlsx' ) ) %>%
  mutate( sample_type = "pooled",
          outcome = recode( outcome,
                            antidepressant_use = "antidepressant",
                            anxiolytic_use = "anxiolytic" ) )

pr_female_imp <- bind_rows( pr_female_2002_imp,
                           pr_female_2006_imp,
                           pr_female_2010_imp,
                           pr_female_2014_imp,
                           pr_female_2021_imp,
                           pr_female_poo_cs_imp ) %>%
  mutate( estimate_type = "Prevalence Ratio" )

# among males
# prevalence ratio
pr_male_2002_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2002_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_male_2006_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2006_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_male_2010_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2010_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_male_2014_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2014_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_male_2021_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_2021_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pr_male_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pr_male_poo_cs_imp.xlsx' ) ) %>%
  mutate( sample_type = "pooled",
          outcome = recode( outcome,
                            antidepressant_use = "antidepressant",
                            anxiolytic_use = "anxiolytic" ) )

pr_male_imp <- bind_rows( pr_male_2002_imp,
                         pr_male_2006_imp,
                         pr_male_2010_imp,
                         pr_male_2014_imp,
                         pr_male_2021_imp,
                         pr_male_poo_cs_imp ) %>%
  mutate( estimate_type = "Prevalence Ratio" )


# among females
# prevalence difference
pd_female_2002_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2002_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_female_2006_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2006_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_female_2010_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2010_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_female_2014_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2014_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_female_2021_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_2021_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_female_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pd_female_poo_cs_imp.xlsx' ) ) %>%
  mutate( sample_type = "pooled",
          outcome = recode( outcome,
                            antidepressant_use = "antidepressant",
                            anxiolytic_use = "anxiolytic" ) )

pd_female_imp <- bind_rows( pd_female_2002_imp,
                           pd_female_2006_imp,
                           pd_female_2010_imp,
                           pd_female_2014_imp,
                           pd_female_2021_imp,
                           pd_female_poo_cs_imp ) %>%
  mutate( estimate_type = "Prevalence Difference" )

# among males
# prevalence difference
pd_male_2002_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2002_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_male_2006_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2006_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_male_2010_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2010_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_male_2014_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2014_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_male_2021_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_2021_imp.xlsx' ) ) %>%
  mutate( sample_type = "individual" )

pd_male_poo_cs_imp <- read_xlsx( here( 'results_output/results_mi/pd_male_poo_cs_imp.xlsx' ) ) %>%
  mutate( sample_type = "pooled",
          outcome = recode( outcome,
                            antidepressant_use = "antidepressant",
                            anxiolytic_use = "anxiolytic" ) )

pd_male_imp <- bind_rows( pd_male_2002_imp,
                         pd_male_2006_imp,
                         pd_male_2010_imp,
                         pd_male_2014_imp,
                         pd_male_2021_imp,
                         pd_male_poo_cs_imp ) %>%
  mutate( estimate_type = "Prevalence Difference" )

# merge data
pr_pd_by_sex_imp <- bind_rows( pr_female_imp, pd_female_imp, pr_male_imp, pd_male_imp ) %>%
  filter( exposure_level != "Other",
          outcome %in% c( "antidepressant", "anxiolytic", "depression", "anxiety", "stress_related" ) ) %>%
  mutate( outcome = as.factor( outcome ),
          sex = as.factor( sex ),
          year = as.integer( year ),
          exposure_level = as.factor( exposure_level ),
          sample_type = as.factor( sample_type ),
          model_type = recode_factor( model_type, "crude" = "Crude", "adjusted" = "Adjusted" ),
          estimate_type = factor( estimate_type, levels = c( "Prevalence Ratio", "Prevalence Difference" ) ),
          exposure_model = interaction( exposure_level, model_type, sep = "_" ),
          exposure_model = factor( exposure_model, levels = c(
            "Bisexual_Crude",
            "Homosexual_Crude",
            "Bisexual_Adjusted",
            "Homosexual_Adjusted" ) ) )

pr_pd_by_sex_imp <- pr_pd_by_sex_imp %>%
  filter(
    !( sample_type == "individual" & outcome %in% c( "depression", "anxiety", "stress_related" ) & year == 2002 ),
    !( sample_type == "individual" & outcome %in% c( "depression", "anxiety", "stress_related" ) & year == 2021 ),
    !( sample_type == "individual" & outcome %in% c( "antidepressant", "anxiolytic" ) & year == 2002 )
  )

pr_pd_by_sex_imp <- pr_pd_by_sex_imp %>%
  mutate(
    across(
      c( estimate, lower_ci, upper_ci ),
      ~ ifelse(
        (
          outcome == "antidepressant" &
          year == 2006 &
          exposure_level == "Bisexual" &
          sample_type == "individual" &
          sex == "Male"
        ),
        NA_real_,
        .
      )
    )
  )

# sanity check
pr_pd_by_sex_imp %>%
  filter( is.na( estimate ) )
summary( pr_pd_by_sex_imp )

# sex-stratified prevalence ratio and prevalence difference analyses for register-based mental health outcomes, including anxiolytic use, depression, anxiety, and stress-related disorders, were not presented because of sparse data and highly imprecise estimates in some subgroups
```

###### 3.2.2.2. Antidepressant use
```{r}
pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "antidepressant" ),
          estimate_type == "Prevalence Difference",
          sample_type == "individual" ) %>%
  summary()

pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "antidepressant" ),
          estimate_type == "Prevalence Ratio",
          sample_type == "individual" ) %>%
  summary()

plot_data <- pr_pd_by_sex_imp %>% 
  filter( outcome %in% c( "antidepressant" ) )

p_pr_pd_by_sex <- ggplot(
  plot_data,
  
  aes( x = year, y = estimate, color = exposure_model, linetype = sample_type, group = interaction( exposure_model, sample_type ) ) ) +
  
  geom_errorbar( data = plot_data %>%
                   filter( sample_type == "individual" ),
                 aes( ymin = lower_ci, ymax = upper_ci ), width = diff( range( 2006, 2021 ) ) * 0.03 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_continuous( breaks = seq( 2006, 2021, 3 ),
                      expand = expansion( mult = c( 0.05, 0.03 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  scale_linetype_manual(
    values = c(
      "pooled" = "dotted",
      "individual" = "solid" ),
    
    labels = c(
      "pooled" = "Cross-Sectional Samples",
      "individual" = "Survey Samples" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  labs( x = "Calendar Year",
        y = "Association Estimate of Antidepressant Use (95% CI)",
        color = NULL,
        linetype = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ sex,
              switch = "y",
              scales = "free" ) +
  
  ggh4x::facetted_pos_scales( 
    y = list(
      estimate_type == "Prevalence Ratio" ~ 
        scale_y_continuous( limits = c( 0, 18 ),
                            breaks = c( seq( 0, 18, 3 ) ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
      
      estimate_type == "Prevalence Difference" ~ 
        scale_y_continuous( limits = c( -0.1, 0.3 ),
                            breaks = c( seq( -0.1, 0.3, 0.1 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd_by_sex
ggsave( "results_output/plots_mi/p_pr_pd_antidepressant_by_sex_imp.svg", plot = p_pr_pd_by_sex, width = 9, height = 7.5 )
```

### 4. Year-Specific Cohort Analyses
#### 4.1. Annual prevalence
##### 4.1.1. By sexual identity
###### 4.1.1.1. Prepare data
```{r}
ann_prevalence_poo_co_imp <- read_xlsx( here( "results_output/results_mi/ann_prevalence_poo_co_imp.xlsx" ) )
summary( ann_prevalence_poo_co_imp )
unique( ann_prevalence_poo_co_imp$sexual_identity_baseline )

plot_co_data_imp <- ann_prevalence_poo_co_imp %>%
  filter(
    sexual_identity_baseline %in% c( "Heterosexual", "Homosexual", "Bisexual" )
    ) %>%
  mutate(
    sexual_identity_baseline = factor(
      sexual_identity_baseline,
      levels = c( "Heterosexual", "Homosexual", "Bisexual" )
      ),
    outcome = as.factor( outcome )
    )

summary( plot_co_data_imp )

vline_data <- data.frame(
  year = 2009, # May 1, 2009
  label = "Marriage Equality",
  sexual_identity_baseline = factor( c( "Bisexual", "Homosexual" ),
                                     levels = c( "Heterosexual", "Bisexual", "Homosexual" ) ) )

# vline_data_covid <- data.frame(
#   year = 2020, # March 2020
#   label = "COVID-19 Outbreak",
#   sexual_identity_baseline = factor( c( "Heterosexual" ),
#                                      levels = c( "Heterosexual", "Bisexual", "Homosexual" ) ) )
```

###### 4.1.1.2. Antidepressant use
```{r}
plot_co_data_imp %>%
  filter( outcome == "antidepressant_use" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_data_imp %>%
    filter( outcome == "antidepressant_use",
            cohort_year >= 2006 ),
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2006, 2021 ),
    breaks = seq( 2006, 2021, by = 3 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.3 ),
    breaks = seq( 0, 0.3, by = 0.05 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2006, 2021 ),
    breaks = c( 2007, 2013, 2020 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Annual Prevalence of Antidepressant Use" ) +
  
  facet_wrap( ~ sexual_identity_baseline ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' ) 
# +
#   
#   geom_vline(
#     data = vline_data,
#     aes( xintercept = year ),
#     linetype = "dashed",
#     color = "grey20",
#     linewidth = 0.4 ) +
#   
#   geom_text(
#     data = vline_data,
#     aes( x = year, y = 0.15, label = label ),
#     angle = 90,
#     nudge_x = -0.7,
#     nudge_y = 0.05,
#     size = 11 / .pt,
#     family = "Arial",
#     color = "grey20",
#     inherit.aes = FALSE )

# p_prevalence <- p_prevalence +
#   
#   geom_vline(
#     data = vline_data_covid,
#     aes( xintercept = year ),
#     linetype = "dashed",
#     color = "grey20",
#     linewidth = 0.4 ) +
#   
#   geom_text(
#     data = vline_data_covid,
#     aes( x = year, y = 0.15, label = label ),
#     angle = 90,
#     nudge_x = -0.7,
#     nudge_y = 0.05,
#     size = 11 / .pt,
#     family = "Arial",
#     color = "grey20",
#     inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_prevalence_poo_co_antidepressant_imp.svg", plot = p_prevalence, width = 14, height = 6 )
```

###### 4.1.1.3. Anxiolytic use
```{r}
plot_co_data_imp %>%
  filter( outcome == "anxiolytic_use" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_data_imp %>%
    filter( outcome == "anxiolytic_use",
            cohort_year >= 2006 ),
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2006, 2021 ),
    breaks = seq( 2006, 2021, by = 3 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.15 ),
    breaks = seq( 0, 0.15, by = 0.05 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2006, 2021 ),
    breaks = c( 2007, 2013, 2020 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Annual Prevalence of Anxiolytic Use" ) +
  
  facet_wrap( ~ sexual_identity_baseline ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' ) 
# +
#   
#   geom_vline(
#     data = vline_data,
#     aes( xintercept = year ),
#     linetype = "dashed",
#     color = "grey20",
#     linewidth = 0.4 ) +
#   
#   geom_text(
#     data = vline_data,
#     aes( x = year, y = 0.06, label = label ),
#     angle = 90,
#     nudge_x = -0.7,
#     nudge_y = 0.05,
#     size = 11 / .pt,
#     family = "Arial",
#     color = "grey20",
#     inherit.aes = FALSE )

# p_prevalence <- p_prevalence +
#   
#   geom_vline(
#     data = vline_data_covid,
#     aes( xintercept = year ),
#     linetype = "dashed",
#     color = "grey20",
#     linewidth = 0.4 ) +
#   
#   geom_text(
#     data = vline_data_covid,
#     aes( x = year, y = 0.06, label = label ),
#     angle = 90,
#     nudge_x = -0.7,
#     nudge_y = 0.05,
#     size = 11 / .pt,
#     family = "Arial",
#     color = "grey20",
#     inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_prevalence_poo_co_anxiolytic_imp.svg", plot = p_prevalence, width = 14, height = 6 )
```

###### 4.1.1.4. Depression
```{r}
plot_co_data_imp %>%
  filter( outcome == "depression" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_data_imp %>%
    filter( outcome == "depression",
            cohort_year >= 2003 ),
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
    
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.10 ),
    breaks = seq( 0, 0.10, by = 0.02 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Annual Prevalence of Depression" ) +
  
  facet_wrap( ~ sexual_identity_baseline ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' ) 
# +
#   
#   geom_vline(
#     data = vline_data,
#     aes( xintercept = year ),
#     linetype = "dashed",
#     color = "grey20",
#     linewidth = 0.4 ) +
#   
#   geom_text(
#     data = vline_data,
#     aes( x = year, y = 0.03, label = label ),
#     angle = 90,
#     nudge_x = -0.7,
#     nudge_y = 0.05,
#     size = 11 / .pt,
#     family = "Arial",
#     color = "grey20",
#     inherit.aes = FALSE )

# p_prevalence <- p_prevalence +
#   
#   geom_vline(
#     data = vline_data_covid,
#     aes( xintercept = year ),
#     linetype = "dashed",
#     color = "grey20",
#     linewidth = 0.4 ) +
#   
#   geom_text(
#     data = vline_data_covid,
#     aes( x = year, y = 0.03, label = label ),
#     angle = 90,
#     nudge_x = -0.7,
#     nudge_y = 0.05,
#     size = 11 / .pt,
#     family = "Arial",
#     color = "grey20",
#     inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_prevalence_poo_co_depression_imp.svg", plot = p_prevalence, width = 14, height = 6 )
```

###### 4.1.1.5. Anxiety disorders
```{r}
plot_co_data_imp %>%
  filter( outcome == "anxiety" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_data_imp %>%
    filter( outcome == "anxiety",
            cohort_year >= 2003 ),
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
    
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.15 ),
    breaks = seq( 0, 0.15, by = 0.05 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Annual Prevalence of Anxiety Disorders" ) +
  
  facet_wrap( ~ sexual_identity_baseline ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' ) 
# +
#   
#   geom_vline(
#     data = vline_data,
#     aes( xintercept = year ),
#     linetype = "dashed",
#     color = "grey20",
#     linewidth = 0.4 ) +
#   
#   geom_text(
#     data = vline_data,
#     aes( x = year, y = 0.05, label = label ),
#     angle = 90,
#     nudge_x = -0.7,
#     nudge_y = 0.05,
#     size = 11 / .pt,
#     family = "Arial",
#     color = "grey20",
#     inherit.aes = FALSE )

# p_prevalence <- p_prevalence +
#   
#   geom_vline(
#     data = vline_data_covid,
#     aes( xintercept = year ),
#     linetype = "dashed",
#     color = "grey20",
#     linewidth = 0.4 ) +
#   
#   geom_text(
#     data = vline_data_covid,
#     aes( x = year, y = 0.05, label = label ),
#     angle = 90,
#     nudge_x = -0.7,
#     nudge_y = 0.05,
#     size = 11 / .pt,
#     family = "Arial",
#     color = "grey20",
#     inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_prevalence_poo_co_anxiety_imp.svg", plot = p_prevalence, width = 14, height = 6 )
```

###### 4.1.1.6. Stress-related disorders
```{r}
plot_co_data_imp %>%
  filter( outcome == "stress_related" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_data_imp %>%
    filter( outcome == "stress_related",
            cohort_year >= 2003 ),
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
    
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.1 ),
    breaks = seq( 0, 0.1, by = 0.02 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Annual Prevalence of Stress-Related Disorders" ) +
  
  facet_wrap( ~ sexual_identity_baseline ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' ) 
# +
#   
#   geom_vline(
#     data = vline_data,
#     aes( xintercept = year ),
#     linetype = "dashed",
#     color = "grey20",
#     linewidth = 0.4 ) +
#   
#   geom_text(
#     data = vline_data,
#     aes( x = year, y = 0.01, label = label ),
#     angle = 90,
#     nudge_x = -0.7,
#     nudge_y = 0.05,
#     size = 11 / .pt,
#     family = "Arial",
#     color = "grey20",
#     inherit.aes = FALSE )

# p_prevalence <- p_prevalence +
#   
#   geom_vline(
#     data = vline_data_covid,
#     aes( xintercept = year ),
#     linetype = "dashed",
#     color = "grey20",
#     linewidth = 0.4 ) +
#   
#   geom_text(
#     data = vline_data_covid,
#     aes( x = year, y = 0.01, label = label ),
#     angle = 90,
#     nudge_x = -0.7,
#     nudge_y = 0.05,
#     size = 11 / .pt,
#     family = "Arial",
#     color = "grey20",
#     inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_prevalence_poo_co_stress_imp.svg", plot = p_prevalence, width = 14, height = 6 )
```

##### 4.1.2. By sex
###### 4.1.2.1. Prepare data
```{r}
ann_prevalence_poo_co_by_sex_imp <- read_xlsx( here( "results_output/results_mi/ann_prevalence_poo_co_by_sex_imp.xlsx" ) )
summary( ann_prevalence_poo_co_by_sex_imp )
unique( ann_prevalence_poo_co_by_sex_imp$sexual_identity_baseline )

plot_co_data_by_sex_imp <- ann_prevalence_poo_co_by_sex_imp %>%
  filter(
    sexual_identity_baseline %in% c( "Heterosexual", "Homosexual", "Bisexual" )
    ) %>%
  mutate(
    sexual_identity_baseline = factor(
      sexual_identity_baseline,
      levels = c( "Heterosexual", "Homosexual", "Bisexual" )
      ),
    sex = as.factor( sex ),
    outcome = as.factor( outcome )
    )

summary( plot_co_data_by_sex_imp )

# vline_data <- data.frame(
#   year = 2009, # May 1, 2009
#   label = "Marriage Equality",
#   sexual_identity_baseline = factor( c( "Bisexual", "Homosexual" ),
#                                      levels = c( "Heterosexual", "Bisexual", "Homosexual" ) ) )

# vline_data_covid <- data.frame(
#   year = 2020, # March 2020
#   label = "COVID-19 Outbreak",
#   sexual_identity_baseline = factor( c( "Heterosexual" ),
#                                      levels = c( "Heterosexual", "Bisexual", "Homosexual" ) ) )
```

###### 4.1.2.2. Antidepressant use
```{r}
plot_co_data_by_sex_imp %>%
  filter( outcome == "antidepressant_use" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_data_by_sex_imp %>%
    filter( outcome == "antidepressant_use",
            cohort_year >= 2006 ),
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2006, 2021 ),
    breaks = seq( 2006, 2021, by = 3 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.35 ),
    breaks = seq( 0, 0.35, by = 0.05 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2006, 2021 ),
    breaks = c( 2007, 2013, 2020 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Annual Prevalence of Antidepressant Use" ) +
  
  facet_grid( sex ~ sexual_identity_baseline,
              switch = "y" ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )
  
  # geom_vline(
  #   data = vline_data %>%
  #     mutate( sex = "Male" ),
  #   aes( xintercept = year ),
  #   linetype = "dashed",
  #   color = "grey20",
  #   linewidth = 0.4 ) +
  # 
  # geom_text(
  #   data = vline_data %>%
  #     mutate( sex = "Male" ),
  #   aes( x = year, y = 0.15, label = label ),
  #   angle = 90,
  #   nudge_x = -0.7,
  #   nudge_y = 0.05,
  #   size = 11 / .pt,
  #   family = "Arial",
  #   color = "grey20",
  #   inherit.aes = FALSE )

# p_prevalence <- p_prevalence +
# 
#   geom_vline(
#     data = vline_data_covid %>%
#       mutate( sex = "Male" ),
#     aes( xintercept = year ),
#     linetype = "dashed",
#     color = "grey20",
#     linewidth = 0.4 ) +
#   
#   geom_text(
#     data = vline_data_covid %>%
#       mutate( sex = "Male" ),
#     aes( x = year, y = 0.15, label = label ),
#     angle = 90,
#     nudge_x = -0.7,
#     nudge_y = 0.05,
#     size = 11 / .pt,
#     family = "Arial",
#     color = "grey20",
#     inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_prevalence_poo_co_antidepressant_by_sex_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

###### 4.1.2.3. Anxiolytic use
```{r}
plot_co_data_by_sex_imp %>%
  filter( outcome == "anxiolytic_use" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_data_by_sex_imp %>%
    filter( outcome == "anxiolytic_use",
            cohort_year >= 2006 ),
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2006, 2021 ),
    breaks = seq( 2006, 2021, by = 3 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.15 ),
    breaks = seq( 0, 0.15, by = 0.05 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2006, 2021 ),
    breaks = c( 2007, 2013, 2020 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Annual Prevalence of Anxiolytic Use" ) +
  
  facet_grid( sex ~ sexual_identity_baseline,
              switch = "y" ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )
  
  # geom_vline(
  #   data = vline_data %>%
  #     mutate( sex = "Male" ),
  #   aes( xintercept = year ),
  #   linetype = "dashed",
  #   color = "grey20",
  #   linewidth = 0.4 ) +
  # 
  # geom_text(
  #   data = vline_data %>%
  #     mutate( sex = "Male" ),
  #   aes( x = year, y = 0.06, label = label ),
  #   angle = 90,
  #   nudge_x = -0.7,
  #   nudge_y = 0.05,
  #   size = 11 / .pt,
  #   family = "Arial",
  #   color = "grey20",
  #   inherit.aes = FALSE )

# p_prevalence <- p_prevalence +
# 
#   geom_vline(
#     data = vline_data_covid %>%
#       mutate( sex = "Male" ),
#     aes( xintercept = year ),
#     linetype = "dashed",
#     color = "grey20",
#     linewidth = 0.4 ) +
#   
#   geom_text(
#     data = vline_data_covid %>%
#       mutate( sex = "Male" ),
#     aes( x = year, y = 0.06, label = label ),
#     angle = 90,
#     nudge_x = -0.7,
#     nudge_y = 0.05,
#     size = 11 / .pt,
#     family = "Arial",
#     color = "grey20",
#     inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_prevalence_poo_co_anxiolytic_by_sex_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

###### 4.1.2.4. Depression
```{r}
plot_co_data_by_sex_imp %>%
  filter( outcome == "depression" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_data_by_sex_imp %>%
    filter( outcome == "depression",
            cohort_year >= 2003 ),
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.15 ),
    breaks = seq( 0, 0.15, by = 0.05 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Annual Prevalence of Depression" ) +
  
  facet_grid( sex ~ sexual_identity_baseline,
              switch = "y" ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )
  
  # geom_vline(
  #   data = vline_data %>%
  #     mutate( sex = "Male" ),
  #   aes( xintercept = year ),
  #   linetype = "dashed",
  #   color = "grey20",
  #   linewidth = 0.4 ) +
  # 
  # geom_text(
  #   data = vline_data %>%
  #     mutate( sex = "Male" ),
  #   aes( x = year, y = 0.03, label = label ),
  #   angle = 90,
  #   nudge_x = -0.7,
  #   nudge_y = 0.05,
  #   size = 11 / .pt,
  #   family = "Arial",
  #   color = "grey20",
  #   inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_prevalence_poo_co_depression_by_sex_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

###### 4.1.2.5. Anxiety disorders
```{r}
plot_co_data_by_sex_imp %>%
  filter( outcome == "anxiety" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_data_by_sex_imp %>%
    filter( outcome == "anxiety",
            cohort_year >= 2003 ),
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.15 ),
    breaks = seq( 0, 0.15, by = 0.05 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Annual Prevalence of Anxiety Disorders" ) +
  
  facet_grid( sex ~ sexual_identity_baseline,
              switch = "y" ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )
  # 
  # geom_vline(
  #   data = vline_data %>%
  #     mutate( sex = "Male" ),
  #   aes( xintercept = year ),
  #   linetype = "dashed",
  #   color = "grey20",
  #   linewidth = 0.4 ) +
  # 
  # geom_text(
  #   data = vline_data %>%
  #     mutate( sex = "Male" ),
  #   aes( x = year, y = 0.03, label = label ),
  #   angle = 90,
  #   nudge_x = -0.7,
  #   nudge_y = 0.05,
  #   size = 11 / .pt,
  #   family = "Arial",
  #   color = "grey20",
  #   inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_prevalence_poo_co_anxiety_by_sex_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

###### 4.1.2.6. Stress-related disorders
```{r}
plot_co_data_by_sex_imp %>%
  filter( outcome == "stress_related" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_data_by_sex_imp %>%
    filter( outcome == "stress_related",
            cohort_year >= 2003 ),
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.15 ),
    breaks = seq( 0, 0.15, by = 0.05 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Annual Prevalence of Stress-Related Disorders" ) +
  
  facet_grid( sex ~ sexual_identity_baseline,
              switch = "y" ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )
  
  # geom_vline(
  #   data = vline_data %>%
  #     mutate( sex = "Male" ),
  #   aes( xintercept = year ),
  #   linetype = "dashed",
  #   color = "grey20",
  #   linewidth = 0.4 ) +
  # 
  # geom_text(
  #   data = vline_data %>%
  #     mutate( sex = "Male" ),
  #   aes( x = year, y = 0.03, label = label ),
  #   angle = 90,
  #   nudge_x = -0.7,
  #   nudge_y = 0.05,
  #   size = 11 / .pt,
  #   family = "Arial",
  #   color = "grey20",
  #   inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_prevalence_poo_co_stress_by_sex_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

#### 4.2. Cumulative prevalence
##### 4.2.1. By sexual identity
###### 4.2.1.1. Prepare data
```{r}
cum_prevalence_poo_co_imp <- read_xlsx( here( "results_output/results_mi/cum_prevalence_poo_co_imp.xlsx" ) )
summary( cum_prevalence_poo_co_imp )
unique( cum_prevalence_poo_co_imp$sexual_identity_baseline )

plot_co_cum_prevalence <- cum_prevalence_poo_co_imp %>%
  filter(
    sexual_identity_baseline %in% c( "Heterosexual", "Homosexual", "Bisexual" )
    ) %>%
  mutate(
    sexual_identity_baseline = factor(
      sexual_identity_baseline,
      levels = c( "Heterosexual", "Homosexual", "Bisexual" )
      ),
    outcome = as.factor( outcome )
    )

summary( plot_co_cum_prevalence )
```

###### 4.2.1.2. Antidepressant use
```{r}
plot_co_cum_prevalence %>%
  filter( outcome == "antidepressant_use" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_cum_prevalence %>%
    filter( outcome == "antidepressant_use",
            cohort_year >= 2006 ),
  aes( x = cum_year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2006, 2021 ),
    breaks = seq( 2006, 2021, by = 3 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.6 ),
    breaks = seq( 0, 0.6, by = 0.1 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2006, 2021 ),
    breaks = c( 2007, 2013, 2020 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Cumulative Prevalence of Antidepressant Use" ) +
  
  facet_wrap( ~ sexual_identity_baseline ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )

p_prevalence
ggsave( "results_output/plots_mi/p_cum_prevalence_poo_co_antidepressant_imp.svg", plot = p_prevalence, width = 14, height = 6 )
```

###### 4.2.1.3. Anxiolytic use
```{r}
plot_co_cum_prevalence %>%
  filter( outcome == "anxiolytic_use" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_cum_prevalence %>%
    filter( outcome == "anxiolytic_use",
            cohort_year >= 2006 ),
  aes( x = cum_year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2006, 2021 ),
    breaks = seq( 2006, 2021, by = 3 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.5 ),
    breaks = seq( 0, 0.5, by = 0.1 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2006, 2021 ),
    breaks = c( 2007, 2013, 2020 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Cumulative Prevalence of Anxiolytic Use" ) +
  
  facet_wrap( ~ sexual_identity_baseline ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )

p_prevalence
ggsave( "results_output/plots_mi/p_cum_prevalence_poo_co_anxiolytic_imp.svg", plot = p_prevalence, width = 14, height = 6 )
```

###### 4.2.1.4. Depression
```{r}
plot_co_cum_prevalence %>%
  filter( outcome == "depression" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_cum_prevalence %>%
    filter( outcome == "depression",
            cohort_year >= 2003 ),
  aes( x = cum_year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.4 ),
    breaks = seq( 0, 0.4, by = 0.1 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Cumulative Prevalence of Depression" ) +
  
  facet_wrap( ~ sexual_identity_baseline ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )

p_prevalence
ggsave( "results_output/plots_mi/p_cum_prevalence_poo_co_depression_imp.svg", plot = p_prevalence, width = 14, height = 6 )
```

###### 4.2.1.5. Anxiety disorders
```{r}
plot_co_cum_prevalence %>%
  filter( outcome == "anxiety" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_cum_prevalence %>%
    filter( outcome == "anxiety",
            cohort_year >= 2003 ),
  aes( x = cum_year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.4 ),
    breaks = seq( 0, 0.4, by = 0.1 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Cumulative Prevalence of Anxiety Disorders" ) +
  
  facet_wrap( ~ sexual_identity_baseline ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )

p_prevalence
ggsave( "results_output/plots_mi/p_cum_prevalence_poo_co_anxiety_imp.svg", plot = p_prevalence, width = 14, height = 6 )
```

###### 4.2.1.6. Stress-related disorders
```{r}
plot_co_cum_prevalence %>%
  filter( outcome == "stress_related" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_cum_prevalence %>%
    filter( outcome == "stress_related",
            cohort_year >= 2003 ),
  aes( x = cum_year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.35 ),
    breaks = seq( 0, 0.35, by = 0.05 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Cumulative Prevalence of Stress-Related Disorders" ) +
  
  facet_wrap( ~ sexual_identity_baseline ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )

p_prevalence
ggsave( "results_output/plots_mi/p_cum_prevalence_poo_co_stress_imp.svg", plot = p_prevalence, width = 14, height = 6 )
```

##### 4.2.2. By sex
###### 4.2.2.1. Prepare data
```{r}
cum_prevalence_poo_co_by_sex_imp <- read_xlsx( here( "results_output/results_mi/cum_prevalence_poo_co_by_sex_imp.xlsx" ) )
summary( cum_prevalence_poo_co_by_sex_imp )
unique( cum_prevalence_poo_co_by_sex_imp$sexual_identity_baseline )

plot_co_cum_prevalence_by_sex <- cum_prevalence_poo_co_by_sex_imp %>%
  filter(
    sexual_identity_baseline %in% c( "Heterosexual", "Homosexual", "Bisexual" )
    ) %>%
  mutate(
    sexual_identity_baseline = factor(
      sexual_identity_baseline,
      levels = c( "Heterosexual", "Homosexual", "Bisexual" )
      ),
    sex = as.factor( sex ),
    outcome = as.factor( outcome )
    )

summary( plot_co_cum_prevalence_by_sex )
```

###### 4.2.2.2. Antidepressant use
```{r}
plot_co_cum_prevalence_by_sex %>%
  filter( outcome == "antidepressant_use" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_cum_prevalence_by_sex %>%
    filter( outcome == "antidepressant_use",
            cohort_year >= 2006 ),
  aes( x = cum_year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2006, 2021 ),
    breaks = seq( 2006, 2021, by = 3 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.6 ),
    breaks = seq( 0, 0.6, by = 0.1 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2006, 2021 ),
    breaks = c( 2007, 2013, 2020 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Cumulative Prevalence of Antidepressant Use" ) +
  
  facet_grid( sex ~ sexual_identity_baseline,
              switch = "y" ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )

p_prevalence
ggsave( "results_output/plots_mi/p_cum_prevalence_poo_co_antidepressant_by_sex_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

###### 4.2.2.3. Anxiolytic use
```{r}
plot_co_cum_prevalence_by_sex %>%
  filter( outcome == "anxiolytic_use" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_cum_prevalence_by_sex %>%
    filter( outcome == "anxiolytic_use",
            cohort_year >= 2006 ),
  aes( x = cum_year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2006, 2021 ),
    breaks = seq( 2006, 2021, by = 3 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.5 ),
    breaks = seq( 0, 0.5, by = 0.1 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2006, 2021 ),
    breaks = c( 2007, 2013, 2020 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Cumulative Prevalence of Anxiolytic Use" ) +
  
  facet_grid( sex ~ sexual_identity_baseline,
              switch = "y" ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )

p_prevalence
ggsave( "results_output/plots_mi/p_cum_prevalence_poo_co_anxiolytic_by_sex_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

###### 4.2.2.4. Depression
```{r}
plot_co_cum_prevalence_by_sex %>%
  filter( outcome == "depression" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_cum_prevalence_by_sex %>%
    filter( outcome == "depression",
            cohort_year >= 2003 ),
  aes( x = cum_year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.4 ),
    breaks = seq( 0, 0.4, by = 0.1 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Cumulative Prevalence of Depression" ) +
  
  facet_grid( sex ~ sexual_identity_baseline,
              switch = "y" ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )

p_prevalence
ggsave( "results_output/plots_mi/p_cum_prevalence_poo_co_depression_by_sex_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

###### 4.2.2.5. Anxiety disorders
```{r}
plot_co_cum_prevalence_by_sex %>%
  filter( outcome == "anxiety" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_cum_prevalence_by_sex %>%
    filter( outcome == "anxiety",
            cohort_year >= 2003 ),
  aes( x = cum_year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.4 ),
    breaks = seq( 0, 0.4, by = 0.1 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Cumulative Prevalence of Anxiety Disorders" ) +
  
  facet_grid( sex ~ sexual_identity_baseline,
              switch = "y" ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )

p_prevalence
ggsave( "results_output/plots_mi/p_cum_prevalence_poo_co_anxiety_by_sex_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

###### 4.2.2.6. Stress-related disorders
```{r}
plot_co_cum_prevalence_by_sex %>%
  filter( outcome == "stress_related" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_cum_prevalence_by_sex %>%
    filter( outcome == "stress_related",
            cohort_year >= 2003 ),
  aes( x = cum_year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_y_continuous( 
    limits = c( 0, 0.4 ),
    breaks = seq( 0, 0.4, by = 0.1 ),
    expand = expansion( mult = c( 0.05, 0.01 ) ),
    labels = percent_format( accuracy = 1 ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Cumulative Prevalence of Stress-Related Disorders" ) +
  
  facet_grid( sex ~ sexual_identity_baseline,
              switch = "y" ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )
  
p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )

p_prevalence
ggsave( "results_output/plots_mi/p_cum_prevalence_poo_co_stress_by_sex_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

###### 4.2.2.7. The 2006 cohort
```{r}
plot_cum_by_sex_2006 <- plot_co_cum_prevalence_by_sex %>%
  filter( cohort_year == 2006 ) %>%
  mutate(
    outcome = factor(
      outcome,
      levels = c(
        "depression", "anxiety", "stress_related",
        "antidepressant_use", "anxiolytic_use"
        ),
      labels = c(
        "Depression", "Anxiety Disorders", "Stress-Related Disorders",
        "Antidepressant Use", "Anxiolytic Use"
        )
      )
    )

summary( plot_cum_by_sex_2006 )

# diagnosis
plot_cum_diag <- plot_cum_by_sex_2006 %>%
  filter( outcome %in% c(
    "Depression",
    "Anxiety Disorders",
    "Stress-Related Disorders"
    ) )

plot_cum_diag %>%
  group_by( outcome ) %>%
  summarise(
    min = min( point_estimate ),
    max = max( point_estimate )
  )

p_cum_diag_by_sex <- ggplot(
  plot_cum_diag,
  
  aes(
    x = cum_year,
    y = point_estimate,
    color = sexual_identity_baseline,
    group = sexual_identity_baseline
    )
  ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" 
      ) 
    ) +
  
  scale_x_continuous(
    limits = c( 2006, 2019 ),
    breaks = c( seq( 2006, 2015, by = 3 ), 2019 ),
    expand = expansion( mult = c( 0.07, 0.05 ) )
    ) +
  
  labs(
    x = "Calendar Year",
    y = "Cumulative Prevalence",
    color = NULL
    ) +
  
  facet_grid(
    outcome ~ sex,
    scales = "free_y",
    switch = "y",
    axes = "all_x"
    ) +
  
  ggh4x::facetted_pos_scales( y = list(
    outcome == "Depression" ~ scale_y_continuous( 
      limits = c( 0, 0.4 ),
      breaks = c( seq( 0, 0.4, 0.1 ) ),
      labels = scales::percent_format( accuracy = 1 ),
      expand = expansion( mult = c( 0.05, 0.02 ) ) ),
    
    outcome == "Anxiety Disorders" ~ scale_y_continuous( 
      limits = c( 0, 0.4 ),
      breaks = c( seq( 0, 0.4, 0.1 ) ),
      labels = scales::percent_format( accuracy = 1 ),
      expand = expansion( mult = c( 0.05, 0.02 ) ) ),
    
    outcome == "Stress-Related Disorders" ~ scale_y_continuous( 
      limits = c( 0, 0.4 ),
      breaks = c( seq( 0, 0.4, 0.1 ) ),
      labels = scales::percent_format( accuracy = 1 ),
      expand = expansion( mult = c( 0.05, 0.02 ) ) ) ) ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_cum_diag_by_sex
ggsave(
  "results_output/plots_mi/p_cum_prevalence_poo_co_diag_2006_by_sex_imp.svg",
  plot = p_cum_diag_by_sex,
  width = 8,
  height = 8 
  )


# medication
plot_cum_med <- plot_cum_by_sex_2006 %>%
  filter( outcome %in% c(
    "Antidepressant Use", 
    "Anxiolytic Use"
  ) )

plot_cum_med %>%
  group_by( outcome ) %>%
  summarise(
    min = min( point_estimate ),
    max = max( point_estimate )
  )

p_cum_med_by_sex <- ggplot(
  plot_cum_med,
  
  aes(
    x = cum_year,
    y = point_estimate,
    color = sexual_identity_baseline,
    group = sexual_identity_baseline
  )
) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" 
    ) 
  ) +
  
  scale_x_continuous(
    limits = c( 2006, 2021 ),
    breaks = c( seq( 2006, 2021, by = 3 ) ),
    expand = expansion( mult = c( 0.07, 0.05 ) )
  ) +
  
  labs(
    x = "Calendar Year",
    y = "Cumulative Prevalence",
    color = NULL
  ) +
  
  facet_grid(
    outcome ~ sex,
    scales = "free_y",
    switch = "y",
    axes = "all_x"
  ) +
  
  ggh4x::facetted_pos_scales( y = list(
    outcome == "Antidepressant Use" ~ scale_y_continuous( 
      limits = c( 0, 0.6 ),
      breaks = c( seq( 0, 0.6, 0.15 ) ),
      labels = scales::percent_format( accuracy = 1 ),
      expand = expansion( mult = c( 0.05, 0.02 ) ) ),
    
    outcome == "Anxiolytic Use" ~ scale_y_continuous( 
      limits = c( 0, 0.5 ),
      breaks = c( seq( 0, 0.5, 0.1 ) ),
      labels = scales::percent_format( accuracy = 1 ),
      expand = expansion( mult = c( 0.05, 0.02 ) ) ) ) ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_cum_med_by_sex
ggsave(
  "results_output/plots_mi/p_cum_prevalence_poo_co_med_2006_by_sex_imp.svg",
  plot = p_cum_med_by_sex,
  width = 8,
  height = 5.7
)
```

#### 4.3. Annual and cumulative prevalence
##### 4.3.1. By sexual identity
###### 4.3.1.1. Prepare data
```{r}
# annual prevalence
ann_prevalence_poo_co_imp <- read_xlsx( here( "results_output/results_mi/ann_prevalence_poo_co_imp.xlsx" ) )
summary( ann_prevalence_poo_co_imp )
unique( ann_prevalence_poo_co_imp$sexual_identity_baseline )

plot_co_data_imp <- ann_prevalence_poo_co_imp %>%
  filter(
    sexual_identity_baseline %in% c( "Heterosexual", "Homosexual", "Bisexual" )
    ) %>%
  mutate(
    sexual_identity_baseline = factor(
      sexual_identity_baseline,
      levels = c( "Heterosexual", "Homosexual", "Bisexual" )
      ),
    outcome = as.factor( outcome )
    )

summary( plot_co_data_imp )

# cumulative prevalence
cum_prevalence_poo_co_imp <- read_xlsx( here( "results_output/results_mi/cum_prevalence_poo_co_imp.xlsx" ) )
summary( cum_prevalence_poo_co_imp )
unique( cum_prevalence_poo_co_imp$sexual_identity_baseline )

plot_co_cum_prevalence <- cum_prevalence_poo_co_imp %>%
  filter(
    sexual_identity_baseline %in% c( "Heterosexual", "Homosexual", "Bisexual" )
    ) %>%
  mutate(
    sexual_identity_baseline = factor(
      sexual_identity_baseline,
      levels = c( "Heterosexual", "Homosexual", "Bisexual" )
      ),
    outcome = as.factor( outcome )
    )

summary( plot_co_cum_prevalence )

# merge data
plot_co_ann_cum_prevalence <- bind_rows(
  plot_co_data_imp %>%
    mutate( type = "annual" ),
  
  plot_co_cum_prevalence %>%
    rename( year = cum_year ) %>%
    mutate( type = "cumulative" )
  ) %>%
  mutate( type = as.factor( type ) )

summary( plot_co_ann_cum_prevalence )

# vline_data <- data.frame(
#   year = 2009, # May 1, 2009
#   label = "Marriage Equality",
#   sexual_identity_baseline = factor( c( "Bisexual", "Homosexual" ),
#                                      levels = c( "Heterosexual", "Bisexual", "Homosexual" ) ) )


# double check whether first-year annual and cumulative prevalence is exactly the same
plot_co_ann_cum_prevalence %>%
  filter( outcome == "antidepressant_use" ) %>%
  filter(
    year == if_else( cohort_year <= 2006, 2006, cohort_year ) 
    ) %>%
  select(
    cohort_year,
    year,
    sexual_identity_baseline,
    type,
    point_estimate,
    lower_ci,
    upper_ci
    ) %>%
  tidyr::pivot_wider(
    names_from = type,
    values_from = c( point_estimate, lower_ci, upper_ci )
    ) %>%
  mutate(
    identical_all =
      point_estimate_annual == point_estimate_cumulative &
      lower_ci_annual == lower_ci_cumulative &
      upper_ci_annual == upper_ci_cumulative
    ) %>%
  count( identical_all )
```

###### 4.3.1.2. Antidepressant use
```{r}
plot_co_ann_cum_prevalence %>%
  filter( outcome == "antidepressant_use",
          type == "annual" ) %>%
  summary()

plot_co_ann_cum_prevalence %>%
  filter( outcome == "antidepressant_use",
          type == "cumulative" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_ann_cum_prevalence %>%
    filter( outcome %in% c( "antidepressant_use" ),
            cohort_year >= 2006 ),
  
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2006, 2021 ),
    breaks = seq( 2006, 2021, by = 3 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2006, 2021 ),
    breaks = c( 2007, 2013, 2020 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Antidepressant Use" ) +
  
  facet_grid( type ~ sexual_identity_baseline,
              switch = "y",
              scales = "free_y",
              labeller = labeller(
                type = c(
                  "annual" = "Annual",
                  "cumulative" = "Cumulative" ) ) ) +
  
  ggh4x::facetted_pos_scales( y = list(
    type == "annual" ~ scale_y_continuous( limits = c( 0, 0.3 ),
                                           breaks = c( seq( 0, 0.3, 0.1 ) ),
                                           labels = scales::percent_format( accuracy = 1 ),
                                           expand = expansion( mult = c( 0.05, 0.01 ) ) ),
    
    type == "cumulative" ~ scale_y_continuous( limits = c( 0, 0.6 ),
                                               breaks = c( seq( 0, 0.6, 0.1 ) ),
                                               labels = scales::percent_format( accuracy = 1 ),
                                               expand = expansion( mult = c( 0.05, 0.01 ) ) ) ) ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )

p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )
  
  # geom_vline(
  #   data = vline_data %>%
  #     mutate( type = "annual" ),
  #   aes( xintercept = year ),
  #   linetype = "dashed",
  #   color = "grey20",
  #   linewidth = 0.4 ) +
  # 
  # geom_text(
  #   data = vline_data %>%
  #     mutate( type = "annual" ),
  #   aes( x = year, y = 0.17, label = label ),
  #   angle = 90,
  #   nudge_x = -0.7,
  #   nudge_y = 0.05,
  #   size = 11 / .pt,
  #   family = "Arial",
  #   color = "grey20",
  #   inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_cum_prevalence_poo_co_antidepressant_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

###### 4.3.1.3. Anxiolytic use
```{r}
plot_co_ann_cum_prevalence %>%
  filter( outcome == "anxiolytic_use",
          type == "annual" ) %>%
  summary()

plot_co_ann_cum_prevalence %>%
  filter( outcome == "anxiolytic_use",
          type == "cumulative" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_ann_cum_prevalence %>%
    filter( outcome %in% c( "anxiolytic_use" ),
            cohort_year >= 2006 ),
  
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2006, 2021 ),
    breaks = seq( 2006, 2021, by = 3 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2006, 2021 ),
    breaks = c( 2007, 2013, 2020 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Anxiolytic Use" ) +
  
  facet_grid( type ~ sexual_identity_baseline,
              switch = "y",
              scales = "free_y",
              labeller = labeller(
                type = c(
                  "annual" = "Annual",
                  "cumulative" = "Cumulative" ) ) ) +
  
  ggh4x::facetted_pos_scales( y = list(
    type == "annual" ~ scale_y_continuous( limits = c( 0, 0.15 ),
                                           breaks = c( seq( 0, 0.15, 0.05 ) ),
                                           labels = scales::percent_format( accuracy = 1 ),
                                           expand = expansion( mult = c( 0.05, 0.01 ) ) ),
    
    type == "cumulative" ~ scale_y_continuous( limits = c( 0, 0.5 ),
                                               breaks = c( seq( 0, 0.5, 0.1 ) ),
                                               labels = scales::percent_format( accuracy = 1 ),
                                               expand = expansion( mult = c( 0.05, 0.01 ) ) ) ) ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )

p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )
  
  # geom_vline(
  #   data = vline_data %>%
  #     mutate( type = "annual" ),
  #   aes( xintercept = year ),
  #   linetype = "dashed",
  #   color = "grey20",
  #   linewidth = 0.4 ) +
  # 
  # geom_text(
  #   data = vline_data %>%
  #     mutate( type = "annual" ),
  #   aes( x = year, y = 0.06, label = label ),
  #   angle = 90,
  #   nudge_x = -0.7,
  #   nudge_y = 0.05,
  #   size = 11 / .pt,
  #   family = "Arial",
  #   color = "grey20",
  #   inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_cum_prevalence_poo_co_anxiolytic_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

###### 4.3.1.4. Depression
```{r}
plot_co_ann_cum_prevalence %>%
  filter( outcome == "depression",
          type == "annual" ) %>%
  summary()

plot_co_ann_cum_prevalence %>%
  filter( outcome == "depression",
          type == "cumulative" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_ann_cum_prevalence %>%
    filter( outcome %in% c( "depression" ),
            cohort_year >= 2003 ),
  
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Depression" ) +
  
  facet_grid( type ~ sexual_identity_baseline,
              switch = "y",
              scales = "free_y",
              labeller = labeller(
                type = c(
                  "annual" = "Annual",
                  "cumulative" = "Cumulative" ) ) ) +
  
  ggh4x::facetted_pos_scales( y = list(
    type == "annual" ~ scale_y_continuous( limits = c( 0, 0.1 ),
                                           breaks = c( seq( 0, 0.1, 0.02 ) ),
                                           labels = scales::percent_format( accuracy = 1 ),
                                           expand = expansion( mult = c( 0.05, 0.01 ) ) ),
    
    type == "cumulative" ~ scale_y_continuous( limits = c( 0, 0.4 ),
                                               breaks = c( seq( 0, 0.4, 0.1 ) ),
                                               labels = scales::percent_format( accuracy = 1 ),
                                               expand = expansion( mult = c( 0.05, 0.01 ) ) ) ) ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )

p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )
  
  # geom_vline(
  #   data = vline_data %>%
  #     mutate( type = "annual" ),
  #   aes( xintercept = year ),
  #   linetype = "dashed",
  #   color = "grey20",
  #   linewidth = 0.4 ) +
  # 
  # geom_text(
  #   data = vline_data %>%
  #     mutate( type = "annual" ),
  #   aes( x = year, y = -0.033, label = label ),
  #   angle = 90,
  #   nudge_x = -0.7,
  #   nudge_y = 0.05,
  #   size = 11 / .pt,
  #   family = "Arial",
  #   color = "grey20",
  #   inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_cum_prevalence_poo_co_depression_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

###### 4.3.1.5. Anxiety disorders
```{r}
plot_co_ann_cum_prevalence %>%
  filter( outcome == "anxiety",
          type == "annual" ) %>%
  summary()

plot_co_ann_cum_prevalence %>%
  filter( outcome == "anxiety",
          type == "cumulative" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_ann_cum_prevalence %>%
    filter( outcome %in% c( "anxiety" ),
            cohort_year >= 2003 ),
  
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Anxiety Disorders" ) +
  
  facet_grid( type ~ sexual_identity_baseline,
              switch = "y",
              scales = "free_y",
              labeller = labeller(
                type = c(
                  "annual" = "Annual",
                  "cumulative" = "Cumulative" ) ) ) +
  
  ggh4x::facetted_pos_scales( y = list(
    type == "annual" ~ scale_y_continuous( limits = c( 0, 0.15 ),
                                           breaks = c( seq( 0, 0.15, 0.05 ) ),
                                           labels = scales::percent_format( accuracy = 1 ),
                                           expand = expansion( mult = c( 0.05, 0.01 ) ) ),
    
    type == "cumulative" ~ scale_y_continuous( limits = c( 0, 0.4 ),
                                               breaks = c( seq( 0, 0.4, 0.1 ) ),
                                               labels = scales::percent_format( accuracy = 1 ),
                                               expand = expansion( mult = c( 0.05, 0.01 ) ) ) ) ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )

p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )
  
  # geom_vline(
  #   data = vline_data %>%
  #     mutate( type = "annual" ),
  #   aes( xintercept = year ),
  #   linetype = "dashed",
  #   color = "grey20",
  #   linewidth = 0.4 ) +
  # 
  # geom_text(
  #   data = vline_data %>%
  #     mutate( type = "annual" ),
  #   aes( x = year, y = 0.05, label = label ),
  #   angle = 90,
  #   nudge_x = -0.7,
  #   nudge_y = 0.05,
  #   size = 11 / .pt,
  #   family = "Arial",
  #   color = "grey20",
  #   inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_cum_prevalence_poo_co_anxiety_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

###### 4.3.1.6. Stress-related disorders
```{r}
plot_co_ann_cum_prevalence %>%
  filter( outcome == "stress_related",
          type == "annual" ) %>%
  summary()

plot_co_ann_cum_prevalence %>%
  filter( outcome == "stress_related",
          type == "cumulative" ) %>%
  summary()

p_prevalence <- ggplot( 
  plot_co_ann_cum_prevalence %>%
    filter( outcome %in% c( "stress_related" ),
            cohort_year >= 2003 ),
  
  aes( x = year, y = point_estimate, color = cohort_year, group = cohort_year ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous(
    limits = c( 2003, 2019 ),
    breaks = seq( 2003, 2019, by = 4 ),
    expand = expansion( mult = c( 0.07, 0.05 ) ) ) +
  
  scale_color_gradientn(
    colours = colorRampPalette( viridis::viridis( 21, option = "turbo" )[ 3:20 ] )( 100 ),
    name = "Cohort Year",
    limits = c( 2003, 2019 ),
    breaks = c( 2004, 2011, 2018 ) ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence of Stress-Related Disorders" ) +
  
  facet_grid( type ~ sexual_identity_baseline,
              switch = "y",
              scales = "free_y",
              labeller = labeller(
                type = c(
                  "annual" = "Annual",
                  "cumulative" = "Cumulative" ) ) ) +
  
  ggh4x::facetted_pos_scales( y = list(
    type == "annual" ~ scale_y_continuous( limits = c( 0, 0.1 ),
                                           breaks = c( seq( 0, 0.1, 0.02 ) ),
                                           labels = scales::percent_format( accuracy = 1 ),
                                           expand = expansion( mult = c( 0.05, 0.01 ) ) ),
    
    type == "cumulative" ~ scale_y_continuous( limits = c( 0, 0.3 ),
                                               breaks = c( seq( 0, 0.3, 0.1 ) ),
                                               labels = scales::percent_format( accuracy = 1 ),
                                               expand = expansion( mult = c( 0.05, 0.02 ) ) ) ) ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_text( family = "Arial", size = 11 ),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "right" )

p_prevalence <- p_prevalence +
  coord_capped_cart( left = 'both', bottom = 'both' )
  
  # geom_vline(
  #   data = vline_data %>%
  #     mutate( type = "annual" ),
  #   aes( xintercept = year ),
  #   linetype = "dashed",
  #   color = "grey20",
  #   linewidth = 0.4 ) +
  # 
  # geom_text(
  #   data = vline_data %>%
  #     mutate( type = "annual" ),
  #   aes( x = year, y = 0.01, label = label ),
  #   angle = 90,
  #   nudge_x = -0.7,
  #   nudge_y = 0.05,
  #   size = 11 / .pt,
  #   family = "Arial",
  #   color = "grey20",
  #   inherit.aes = FALSE )

p_prevalence
ggsave( "results_output/plots_mi/p_ann_cum_prevalence_poo_co_stress_imp.svg", plot = p_prevalence, width = 14, height = 7 )
```

##### 4.3.2. The 2006 cohort
###### 4.3.2.1. Prepare data
```{r}
# annual prevalence
ann_prevalence_poo_co_imp <- read_xlsx( here( "results_output/results_mi/ann_prevalence_poo_co_imp.xlsx" ) )
summary( ann_prevalence_poo_co_imp )
unique( ann_prevalence_poo_co_imp$sexual_identity_baseline )

plot_co_data_imp <- ann_prevalence_poo_co_imp %>%
  filter(
    sexual_identity_baseline %in% c( "Heterosexual", "Homosexual", "Bisexual" )
    ) %>%
  mutate(
    sexual_identity_baseline = factor(
      sexual_identity_baseline,
      levels = c( "Heterosexual", "Homosexual", "Bisexual" )
      ),
    outcome = as.factor( outcome )
    )

summary( plot_co_data_imp )

# cumulative prevalence
cum_prevalence_poo_co_imp <- read_xlsx( here( "results_output/results_mi/cum_prevalence_poo_co_imp.xlsx" ) )
summary( cum_prevalence_poo_co_imp )
unique( cum_prevalence_poo_co_imp$sexual_identity_baseline )

plot_co_cum_prevalence <- cum_prevalence_poo_co_imp %>%
  filter(
    sexual_identity_baseline %in% c( "Heterosexual", "Homosexual", "Bisexual" )
    ) %>%
  mutate(
    sexual_identity_baseline = factor(
      sexual_identity_baseline,
      levels = c( "Heterosexual", "Homosexual", "Bisexual" )
      ),
    outcome = as.factor( outcome )
    )

summary( plot_co_cum_prevalence )

# merge data
plot_co_ann_cum_prevalence <- bind_rows(
  plot_co_data_imp %>%
    mutate( type = "annual" ),
  
  plot_co_cum_prevalence %>%
    rename( year = cum_year ) %>%
    mutate( type = "cumulative" )
  ) %>%
  mutate( type = as.factor( type ) )

summary( plot_co_ann_cum_prevalence )

plot_co_single_cohort <- plot_co_ann_cum_prevalence %>%
  filter( cohort_year == 2006 ) %>%
  mutate(
    outcome = factor(
      outcome,
      levels = c(
        "depression", "anxiety", "stress_related",
        "antidepressant_use", "anxiolytic_use"
        ),
      labels = c(
        "Depression", "Anxiety Disorders", "Stress-Related Disorders",
        "Antidepressant Use", "Anxiolytic Use"
        )
      ),
    
    type = factor(
      type,
      levels = c( "annual", "cumulative" ),
      labels = c( "Annual", "Cumulative" )
      )
    )

summary( plot_co_single_cohort )
```

###### 4.3.2.2. Diagnosis
```{r}
plot_diag <- plot_co_single_cohort %>%
  filter( outcome %in% c(
    "Depression",
    "Anxiety Disorders",
    "Stress-Related Disorders"
    ) )

plot_diag %>%
  group_by( outcome ) %>%
  summarise(
    min = min( point_estimate ),
    max = max( point_estimate )
  )

p_diag <- ggplot(
  plot_diag,
  
  aes(
    x = year,
    y = point_estimate,
    color = sexual_identity_baseline,
    linetype = type,
    group = interaction( sexual_identity_baseline, type )
    ) 
  ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) 
    ) +
  
  scale_linetype_manual(
    values = c( "Annual" = "dotted", 
                "Cumulative" = "solid" )
    ) +
  
  scale_x_continuous(
    limits = c( 2006, 2019 ),
    breaks = c( seq( 2006, 2015, by = 3 ), 2019 ),
    expand = expansion( mult = c( 0.07, 0.02 ) )
    ) +
  
  labs(
    x = "Calendar Year",
    y = "Prevalence",
    color = NULL,
    linetype = NULL
    ) +
  
  facet_wrap( ~ outcome, 
              ncol = 1,
              scales = "free_y",
              axes = "all_x" ) +
  
  ggh4x::facetted_pos_scales( y = list(
    outcome == "Depression" ~ scale_y_continuous( 
      limits = c( 0, 0.6 ),
      breaks = c( seq( 0, 0.6, 0.15 ) ),
      labels = scales::percent_format( accuracy = 1 ),
      expand = expansion( mult = c( 0.05, 0.02 ) ) ),
    
    outcome == "Anxiety Disorders" ~ scale_y_continuous( 
      limits = c( 0, 0.4 ),
      breaks = c( seq( 0, 0.4, 0.1 ) ),
      labels = scales::percent_format( accuracy = 1 ),
      expand = expansion( mult = c( 0.05, 0.02 ) ) ),
    
    outcome == "Stress-Related Disorders" ~ scale_y_continuous( 
      limits = c( 0, 0.3 ),
      breaks = c( seq( 0, 0.3, 0.1 ) ),
      labels = scales::percent_format( accuracy = 1 ),
      expand = expansion( mult = c( 0.05, 0.02 ) ) ) ) ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_diag
# ggsave(
#   "results_output/plots_mi/p_ann_cum_prevalence_poo_co_diag_2006_imp.svg",
#   plot = p_diag,
#   width = 7,
#   height = 9 
#   )
```

###### 4.3.2.3. Medication
```{r}
plot_med <- plot_co_single_cohort %>%
  filter( outcome %in% c(
    "Antidepressant Use",
    "Anxiolytic Use"
    ) )

plot_med %>%
  group_by( outcome ) %>%
  summarise(
    min = min( point_estimate ),
    max = max( point_estimate )
  )

plot_med$outcome <- factor(
  plot_med$outcome,
  levels = c(
    "Antidepressant Use",
    "Anxiolytic Use",
    " "
    )
  ) # create place holder

plot_med %>%
  filter( outcome == " " )

p_med <- ggplot(
  plot_med,
  
  aes(
    x = year,
    y = point_estimate,
    color = sexual_identity_baseline,
    linetype = type,
    group = interaction( sexual_identity_baseline, type )
    ) 
  ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) 
    ) +
  
  scale_linetype_manual(
    values = c( "Annual" = "dotted", 
                "Cumulative" = "solid" )
    ) +
  
  scale_x_continuous(
    limits = c( 2006, 2021 ),
    breaks = c( seq( 2006, 2021, by = 3 ) ),
    expand = expansion( mult = c( 0.07, 0.02 ) )
    ) +
  
  labs(
    x = "Calendar Year",
    y = NULL,
    color = NULL,
    linetype = NULL
    ) +
  
  facet_wrap( ~ outcome, 
              ncol = 1,
              scales = "free_y",
              drop = FALSE,
              axes = "all_x" ) +
  
  ggh4x::facetted_pos_scales( y = list(
    outcome == "Antidepressant Use" ~ scale_y_continuous( 
      limits = c( 0, 0.6 ),
      breaks = c( seq( 0, 0.6, 0.15 ) ),
      labels = scales::percent_format( accuracy = 1 ),
      expand = expansion( mult = c( 0.05, 0.02 ) ) ),
    
    outcome == "Anxiolytic Use" ~ scale_y_continuous( 
      limits = c( 0, 0.4 ),
      breaks = c( seq( 0, 0.4, 0.1 ) ),
      labels = scales::percent_format( accuracy = 1 ),
      expand = expansion( mult = c( 0.05, 0.02 ) ) ) ) ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_med
# ggsave(
#   "results_output/plots_mi/p_ann_cum_prevalence_poo_co_med_2006_imp.svg",
#   plot = p_med,
#   width = 7,
#   height = 9
#   )
```

###### 4.3.2.4. Merge plot
```{r}
p_prevalence <-
  p_diag +
  plot_spacer() +
  p_med +
  plot_layout(
    widths = c( 1, 0.08, 1 ),
    guides = "collect"
    ) &
  theme(
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom"
    )

p_prevalence
ggsave(
  "results_output/plots_mi/p_ann_cum_prevalence_poo_co_2006_imp.svg",
  plot = p_prevalence,
  width = 12,
  height = 9
)
```