---
title: "Summary plots of complete-case analyses among 16-29 years"
author: Willi Zhang
email: willi.zhang@ki.se
output: html_notebook
editor_options: 
  chunk_output_type: console
---

### 1. Load Packages and Global Settings
```{r}
library(forestploter)
library(grid)
library(readxl)
library(here)
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(colorspace)
library(naniar)
library(ggh4x)
library(scales)
library(lemon)
library(stringr)

# fixed year color mapping (2001-2021)
all_years <- 2001:2021
palette_full <- colorRampPalette( viridis::viridis( 16, option = "turbo" )[3:14] )( length( all_years ) )
year_colors <- setNames( palette_full, all_years )
```

### 2. Individual Surveys
#### 2.1. By sexual identity
##### 2.1.1. Prepare data
```{r}
# by sexual identity
prevalence_2002_by_identity_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2002_by_identity_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = - c( sexual_identity ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

prevalence_2006_by_identity_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2006_by_identity_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -c( sexual_identity ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

prevalence_2010_by_identity_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2010_by_identity_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -c( sexual_identity ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

prevalence_2014_by_identity_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2014_by_identity_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2014 ) %>%
  pivot_longer(
    cols = -c( sexual_identity ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

prevalence_2021_by_identity_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2021_by_identity_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2021 ) %>%
  pivot_longer(
    cols = -c( sexual_identity ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

# overall prevalence
overall_prevalence_2002_cc <- read_xlsx( here( "results_output/results_cc/overall_prevalence_2002_cc.xlsx" ) ) %>%
  pivot_longer(
    cols = -c( sexual_identity ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

overall_prevalence_2006_cc <- read_xlsx( here( "results_output/results_cc/overall_prevalence_2006_cc.xlsx" ) ) %>%
  pivot_longer(
    cols = -c( sexual_identity ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

overall_prevalence_2010_cc <- read_xlsx( here( "results_output/results_cc/overall_prevalence_2010_cc.xlsx" ) ) %>%
  pivot_longer(
    cols = -c( sexual_identity ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

overall_prevalence_2014_cc <- read_xlsx( here( "results_output/results_cc/overall_prevalence_2014_cc.xlsx" ) ) %>%
  pivot_longer(
    cols = -c( sexual_identity ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

overall_prevalence_2021_cc <- read_xlsx( here( "results_output/results_cc/overall_prevalence_2021_cc.xlsx" ) ) %>%
  pivot_longer(
    cols = -c( sexual_identity ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

# merge and clean data
prevalence_cc <- bind_rows( prevalence_2002_by_identity_cc,
                            prevalence_2006_by_identity_cc,
                            prevalence_2010_by_identity_cc,
                            prevalence_2014_by_identity_cc,
                            prevalence_2021_by_identity_cc,
                            overall_prevalence_2002_cc,
                            overall_prevalence_2006_cc,
                            overall_prevalence_2010_cc,
                            overall_prevalence_2014_cc,
                            overall_prevalence_2021_cc
                            ) %>%
  mutate( sexual_identity = factor( 
    sexual_identity, levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other", "Stockholm County" ) ),
    outcome = as.factor( outcome ),
    year = as.factor( year ) ) %>%
  filter( sexual_identity != "Other" )

summary( prevalence_cc )
unique( prevalence_cc$outcome )
```

##### 2.1.2. Self-reported
```{r}
prevalence_cc %>%
  filter( outcome %in% c( "psychological_distress" ) ) %>%
  summary()

prevalence_cc %>%
  filter( outcome %in% c( "suicidal_thoughts" ) ) %>%
  summary()

prevalence_cc %>%
  filter( outcome %in% c( "suicide_attempts" ) ) %>%
  summary()

p_prevalence <- ggplot( 
  prevalence_cc %>%
    filter( outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ) ) %>%
    mutate( outcome = factor( outcome, levels = c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ) ) ),
  
  aes( x = year, y = point_estimate, color = sexual_identity, group = sexual_identity ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = 0.1 ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.08, 0.02 ) ) ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF",
      "Stockholm County" = "brown" ) ) +
  
  labs(
    x = NULL,
    y = "Prevalence (95% CI)",
    color = NULL ) +
  
  facet_wrap( ~ outcome, 
              ncol = 2,
              axes = "all",
              scales = "free_y",
              labeller = labeller(
                outcome = c(
                  "psychological_distress" = "Psychological Distress",
                  "suicidal_thoughts" = "Suicidal Thoughts",
                  "suicide_attempts" = "Suicide Attempts" ) ) ) +
  
  ggh4x::facetted_pos_scales( y = list(
    outcome == "psychological_distress" ~ scale_y_continuous( limits = c( 0, 0.7 ), 
                                                              breaks = c( seq( 0, 0.7, 0.1 ) ),
                                                              labels = scales::percent_format( accuracy = 1 ),
                                                              expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    outcome == "suicidal_thoughts" ~ scale_y_continuous( limits = c( 0, 0.7 ), 
                                                         breaks = c( seq( 0, 0.7, 0.1 ) ),
                                                         labels = scales::percent_format( accuracy = 1 ),
                                                         expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    outcome == "suicide_attempts" ~ scale_y_continuous( limits = c( 0, 0.4 ), 
                                                        breaks = c( seq( 0, 0.4, 0.1 ) ),
                                                        labels = scales::percent_format( accuracy = 1 ),
                                                        expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_cc/p_prevalence_self_report_cc.svg", plot = p_prevalence, width = 9, height = 8 )
```

##### 2.1.3. Register based
```{r}
prevalence_cc %>%
  filter( outcome %in% c( "depression" ) ) %>%
  summary()

prevalence_cc %>%
  filter( outcome %in% c( "antidepressant" ) ) %>%
  summary()

prevalence_cc %>%
  filter( outcome %in% c( "anxiety" ) ) %>%
  summary()

prevalence_cc %>%
  filter( outcome %in% c( "anxiolytic" ) ) %>%
  summary()

prevalence_cc %>%
  filter( outcome %in% c( "stress_related" ) ) %>%
  summary()

p_prevalence <- ggplot( 
  prevalence_cc %>%
    filter( outcome %in% c( "antidepressant", "depression", "anxiolytic", "anxiety", "stress_related" ) ) %>%
    mutate( outcome = factor( outcome, levels = c( "antidepressant", "depression", "anxiolytic", "anxiety", "stress_related" ) ) ),
  
  aes( x = year, y = point_estimate, color = sexual_identity, group = sexual_identity ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = 0.1 ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF",
      "Stockholm County" = "brown" ) ) +
  
  labs(
    x = NULL,
    y = "Prevalence (95% CI)",
    color = NULL ) +
  
  facet_wrap( ~ outcome, 
              ncol = 2,
              axes = "all",
              scales = "free",
              labeller = labeller(
                outcome = c(
                  "depression" = "Depression",
                  "antidepressant" = "Antidepressant Use",
                  "anxiety" = "Anxiety Disorders",
                  "anxiolytic" = "Anxiolytic Use",
                  "stress_related" = "Stress-Related Disorders" ) ) ) +
  
  ggh4x::facetted_pos_scales( 
    x = list(
      outcome %in% c( "depression", "anxiety", "stress_related" ) ~
        scale_x_discrete( breaks = c( "2002", "2006", "2010", "2014", "2021" ),
                          expand = expansion( mult = c( 0.08, 0.02 ) ) ),
      
      outcome %in% c( "antidepressant", "anxiolytic" ) ~
        scale_x_discrete( breaks = c( "2006", "2010", "2014", "2021" ),
                          expand = expansion( mult = c( 0.08, 0.02 ) ) ) ),
      
    y = list(
      outcome %in% c( "depression", "antidepressant" ) ~ 
        scale_y_continuous( limits = c( 0, 0.3 ),
                            breaks = c( seq( 0, 0.3, 0.1 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
      
      outcome %in% c( "anxiety", "anxiolytic" ) ~ 
        scale_y_continuous( limits = c( 0, 0.2 ),
                            breaks = c( seq( 0, 0.2, 0.1 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
    
      outcome %in% c( "stress_related" ) ~ 
        scale_y_continuous( limits = c( 0, 0.15 ),
                            breaks = c( seq( 0, 0.15, 0.05 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ) ) 
    ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_cc/p_prevalence_register_based_cc.svg", plot = p_prevalence, width = 9, height = 10.5 )
```

##### 2.1.2. By sex
###### 2.1.2.1. Prepare data
```{r}
# by sexual identity and sex
prevalence_2002_by_sex_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2002_by_sex_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

prevalence_2006_by_sex_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2006_by_sex_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

prevalence_2010_by_sex_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2010_by_sex_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2010 ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

prevalence_2014_by_sex_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2014_by_sex_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2014 ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

prevalence_2021_by_sex_cc <- read_xlsx( here( "results_output/results_cc/prevalence_2021_by_sex_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_2021 ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

# by sex
overall_prevalence_2002_by_sex_cc <- read_xlsx( here( "results_output/results_cc/overall_prevalence_2002_by_sex_cc.xlsx" ) ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

overall_prevalence_2006_by_sex_cc <- read_xlsx( here( "results_output/results_cc/overall_prevalence_2006_by_sex_cc.xlsx" ) ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

overall_prevalence_2010_by_sex_cc <- read_xlsx( here( "results_output/results_cc/overall_prevalence_2010_by_sex_cc.xlsx" ) ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

overall_prevalence_2014_by_sex_cc <- read_xlsx( here( "results_output/results_cc/overall_prevalence_2014_by_sex_cc.xlsx" ) ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

overall_prevalence_2021_by_sex_cc <- read_xlsx( here( "results_output/results_cc/overall_prevalence_2021_by_sex_cc.xlsx" ) ) %>%
  pivot_longer(
    cols = -c( sexual_identity, sex ),
    names_to = c( "outcome", "year", ".value" ),
    names_pattern = "(.+?)_(\\d{4})_(point_estimate|lower_ci|upper_ci)" )

# merge and clean data
prevalence_indi_by_sex_cc <- bind_rows( prevalence_2002_by_sex_cc,
                                        prevalence_2006_by_sex_cc,
                                        prevalence_2010_by_sex_cc,
                                        prevalence_2014_by_sex_cc,
                                        prevalence_2021_by_sex_cc,
                                        overall_prevalence_2002_by_sex_cc,
                                        overall_prevalence_2006_by_sex_cc,
                                        overall_prevalence_2010_by_sex_cc,
                                        overall_prevalence_2014_by_sex_cc,
                                        overall_prevalence_2021_by_sex_cc 
                                        ) %>%
  mutate( sexual_identity = factor( sexual_identity, levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other", "Stockholm County" ) ),
          sex = factor( sex, levels = c( "Female", "Male" ) ),
          outcome = as.factor( outcome ),
          year = as.factor( year ) ) %>%
  filter( sexual_identity != "Other" )

summary( prevalence_indi_by_sex_cc )
```

###### 2.1.2.2. Suicidal thoughts
```{r}
prevalence_indi_by_sex_cc %>%
  filter( outcome %in% c( "suicidal_thoughts" ) ) %>%
  summary()

p_prevalence <- ggplot( 
  prevalence_indi_by_sex_cc %>%
    filter( outcome %in% c( "suicidal_thoughts" ) ),
  
  aes( x = year, y = point_estimate, color = sexual_identity, group = sexual_identity ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = 0.1 ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.08, 0.02 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.9 ),
                      breaks = c( seq( 0, 0.9, 0.1 ) ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( values = c(
    "Heterosexual" = "#F8766D",
    "Bisexual" = "#C77CFF",
    "Homosexual" = "#00BFC4",
    "Stockholm County" = "brown" ),
    
    guide = guide_legend( nrow = 1 ) ) +
  
  labs(
    x = "Survey Year",
    y = "Prevalence of Suicidal Thoughts (95% CI)",
    color = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_cc/p_prevalence_suicidal_thoughts_by_sex_cc.svg", plot = p_prevalence, width = 9, height = 6 )
```

###### 2.1.2.3. Suicide attempts
```{r}
prevalence_indi_by_sex_cc %>%
  filter( outcome %in% c( "suicide_attempts" ) ) %>%
  summary()

p_prevalence <- ggplot( 
  prevalence_indi_by_sex_cc %>%
    filter( outcome %in% c( "suicide_attempts" ) ),
  
  aes( x = year, y = point_estimate, color = sexual_identity, group = sexual_identity ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = 0.1 ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.08, 0.02 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.5 ),
                      breaks = c( seq( 0, 0.5, 0.1 ) ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( values = c(
    "Heterosexual" = "#F8766D",
    "Bisexual" = "#C77CFF",
    "Homosexual" = "#00BFC4",
    "Stockholm County" = "brown" ),
    
    guide = guide_legend( nrow = 1 ) ) +
  
  labs(
    x = "Survey Year",
    y = "Prevalence of Suicide Attempts (95% CI)",
    color = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_cc/p_prevalence_suicide_attempts_by_sex_cc.svg", plot = p_prevalence, width = 9, height = 6 )
```

###### 2.1.2.4. Psychological distress
```{r}
prevalence_indi_by_sex_cc %>%
  filter( outcome %in% c( "psychological_distress" ) ) %>%
  summary()

p_prevalence <- ggplot( 
  prevalence_indi_by_sex_cc %>%
    filter( outcome %in% c( "psychological_distress" ) ),
  
  aes( x = year, y = point_estimate, color = sexual_identity, group = sexual_identity ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = 0.1 ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.08, 0.02 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 1 ),
                      breaks = c( seq( 0, 1, 0.1 ) ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( values = c(
    "Heterosexual" = "#F8766D",
    "Bisexual" = "#C77CFF",
    "Homosexual" = "#00BFC4",
    "Stockholm County" = "brown" ),
    
    guide = guide_legend( nrow = 1 ) ) +
  
  labs(
    x = "Survey Year",
    y = "Prevalence of Psychological Distress (95% CI)",
    color = NULL ) +
  
  facet_grid( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_cc/p_prevalence_psychological_distress_by_sex_cc.svg", plot = p_prevalence, width = 9, height = 6 )
```

#### 2.2. Prevalence ratio and difference
##### 2.2.1. By sexual identity
###### 2.2.1.1. Prepare data
```{r}
pr_2002_cc <- read_xlsx( here( 'results_output/results_cc/pr_2002_cc.xlsx' ) )
pr_2006_cc <- read_xlsx( here( 'results_output/results_cc/pr_2006_cc.xlsx' ) )
pr_2010_cc <- read_xlsx( here( 'results_output/results_cc/pr_2010_cc.xlsx' ) )
pr_2014_cc <- read_xlsx( here( 'results_output/results_cc/pr_2014_cc.xlsx' ) )
pr_2021_cc <- read_xlsx( here( 'results_output/results_cc/pr_2021_cc.xlsx' ) )

pr_cc <- bind_rows( pr_2002_cc,
                    pr_2006_cc,
                    pr_2010_cc,
                    pr_2014_cc,
                    pr_2021_cc ) %>%
  mutate( estimate_type = "Prevalence Ratio" )

pd_2002_cc <- read_xlsx( here( 'results_output/results_cc/pd_2002_cc.xlsx' ) )
pd_2006_cc <- read_xlsx( here( 'results_output/results_cc/pd_2006_cc.xlsx' ) )
pd_2010_cc <- read_xlsx( here( 'results_output/results_cc/pd_2010_cc.xlsx' ) )
pd_2014_cc <- read_xlsx( here( 'results_output/results_cc/pd_2014_cc.xlsx' ) )
pd_2021_cc <- read_xlsx( here( 'results_output/results_cc/pd_2021_cc.xlsx' ) )

pd_cc <- bind_rows( pd_2002_cc,
                    pd_2006_cc,
                    pd_2010_cc,
                    pd_2014_cc,
                    pd_2021_cc ) %>%
  mutate( estimate_type = "Prevalence Difference" )

pr_pd_cc <- bind_rows( pr_cc, pd_cc ) %>%
  filter( exposure_level != "Other" ) %>%
  mutate( outcome = as.factor( outcome ),
          year = as.factor( year ),
          exposure_level = as.factor( exposure_level ),
          model_type = recode_factor( model_type, "crude" = "Crude", "adjusted" = "Adjusted" ),
          estimate_type = factor( estimate_type, levels = c( "Prevalence Ratio", "Prevalence Difference" ) ),
          exposure_model = interaction( exposure_level, model_type, sep = "_" ),
          exposure_model = factor( exposure_model, levels = c(
            "Bisexual_Crude",
            "Homosexual_Crude",
            "Bisexual_Adjusted",
            "Homosexual_Adjusted" ) ) )
summary( pr_pd_cc )
```

###### 2.2.1.2. Self-reported
```{r}
pr_pd_cc %>% 
  filter( outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ),
          estimate_type == "Prevalence Difference" ) %>%
  summary()

pr_pd_cc %>% 
  filter( outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ),
          estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd <- ggplot(
  pr_pd_cc %>%
    filter( outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ) ),
  
  aes( x = year, y = estimate, color = exposure_model, group = exposure_model ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = 0.1 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.05, 0.02 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 1 ) ) +
  
  labs( x = "Survey Year",
        y = "Estimate (95% CI)",
        color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ outcome,
              switch = "y",
              scales = "free_y",
              labeller = labeller(
                outcome = c(
                  "psychological_distress" = "Psychological Distress",
                  "suicidal_thoughts" = "Suicidal Thoughts",
                  "suicide_attempts" = "Suicide Attempts" ) ) ) +
  
  ggh4x::facetted_pos_scales( y = list(
    estimate_type == "Prevalence Ratio" ~ scale_y_continuous( limits = c( 0, 8 ), 
                                                              breaks = c( seq( 0, 8, 1 ) ), 
                                                              expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    estimate_type == "Prevalence Difference" ~ scale_y_continuous( limits = c( -0.2, 0.5 ), 
                                                                   breaks = c( seq( -0.2, 0.5, 0.1 ) ), 
                                                                   labels = scales::percent_format( accuracy = 1 ), 
                                                                   expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd
ggsave( "results_output/plots_cc/p_pr_pd_self_report_cc.svg", plot = p_pr_pd, width = 12, height = 7.5 )
```

##### 2.2.2. By sex
###### 2.2.2.1. Prepare data
```{r}
# among females
pr_female_2002_cc <- read_xlsx( here( 'results_output/results_cc/pr_female_2002_cc.xlsx' ) )
pr_female_2006_cc <- read_xlsx( here( 'results_output/results_cc/pr_female_2006_cc.xlsx' ) )
pr_female_2010_cc <- read_xlsx( here( 'results_output/results_cc/pr_female_2010_cc.xlsx' ) )
pr_female_2014_cc <- read_xlsx( here( 'results_output/results_cc/pr_female_2014_cc.xlsx' ) )
pr_female_2021_cc <- read_xlsx( here( 'results_output/results_cc/pr_female_2021_cc.xlsx' ) )

pr_female_cc <- bind_rows( pr_female_2002_cc,
                           pr_female_2006_cc,
                           pr_female_2010_cc,
                           pr_female_2014_cc,
                           pr_female_2021_cc ) %>%
  mutate( estimate_type = "Prevalence Ratio" )

pd_female_2002_cc <- read_xlsx( here( 'results_output/results_cc/pd_female_2002_cc.xlsx' ) )
pd_female_2006_cc <- read_xlsx( here( 'results_output/results_cc/pd_female_2006_cc.xlsx' ) )
pd_female_2010_cc <- read_xlsx( here( 'results_output/results_cc/pd_female_2010_cc.xlsx' ) )
pd_female_2014_cc <- read_xlsx( here( 'results_output/results_cc/pd_female_2014_cc.xlsx' ) )
pd_female_2021_cc <- read_xlsx( here( 'results_output/results_cc/pd_female_2021_cc.xlsx' ) )

pd_female_cc <- bind_rows( pd_female_2002_cc,
                           pd_female_2006_cc,
                           pd_female_2010_cc,
                           pd_female_2014_cc,
                           pd_female_2021_cc ) %>%
  mutate( estimate_type = "Prevalence Difference" )

# among males
pr_male_2002_cc <- read_xlsx( here( 'results_output/results_cc/pr_male_2002_cc.xlsx' ) )
pr_male_2006_cc <- read_xlsx( here( 'results_output/results_cc/pr_male_2006_cc.xlsx' ) )
pr_male_2010_cc <- read_xlsx( here( 'results_output/results_cc/pr_male_2010_cc.xlsx' ) )
pr_male_2014_cc <- read_xlsx( here( 'results_output/results_cc/pr_male_2014_cc.xlsx' ) )
pr_male_2021_cc <- read_xlsx( here( 'results_output/results_cc/pr_male_2021_cc.xlsx' ) )

pr_male_cc <- bind_rows( pr_male_2002_cc,
                         pr_male_2006_cc,
                         pr_male_2010_cc,
                         pr_male_2014_cc,
                         pr_male_2021_cc ) %>%
  mutate( estimate_type = "Prevalence Ratio" )

pd_male_2002_cc <- read_xlsx( here( 'results_output/results_cc/pd_male_2002_cc.xlsx' ) )
pd_male_2006_cc <- read_xlsx( here( 'results_output/results_cc/pd_male_2006_cc.xlsx' ) )
pd_male_2010_cc <- read_xlsx( here( 'results_output/results_cc/pd_male_2010_cc.xlsx' ) )
pd_male_2014_cc <- read_xlsx( here( 'results_output/results_cc/pd_male_2014_cc.xlsx' ) )
pd_male_2021_cc <- read_xlsx( here( 'results_output/results_cc/pd_male_2021_cc.xlsx' ) )

pd_male_cc <- bind_rows( pd_male_2002_cc,
                         pd_male_2006_cc,
                         pd_male_2010_cc,
                         pd_male_2014_cc,
                         pd_male_2021_cc ) %>%
  mutate( estimate_type = "Prevalence Difference" )

# merge data
pr_pd_by_sex_cc <- bind_rows( pr_female_cc, pd_female_cc, pr_male_cc, pd_male_cc ) %>%
  filter( exposure_level != "Other" ) %>%
  mutate( outcome = as.factor( outcome ),
          year = as.factor( year ),
          sex = as.factor( sex ),
          exposure_level = as.factor( exposure_level ),
          model_type = recode_factor( model_type, "crude" = "Crude", "adjusted" = "Adjusted" ),
          estimate_type = factor( estimate_type, levels = c( "Prevalence Ratio", "Prevalence Difference" ) ),
          exposure_model = interaction( exposure_level, model_type, sep = "_" ),
          exposure_model = factor( exposure_model, levels = c(
            "Bisexual_Crude",
            "Homosexual_Crude",
            "Bisexual_Adjusted",
            "Homosexual_Adjusted" ) ) )

pr_pd_by_sex_cc <- pr_pd_by_sex_cc %>%
  mutate(
    across(
      c( estimate, lower_ci, upper_ci ),
      ~ ifelse(
        outcome == "suicide_attempts" &
          sex == "Male" &
          (
            ( year == 2002 & exposure_level == "Bisexual" ) | # four PR data points were not estimable due to zero events
            ( year == 2014 & exposure_level == "Homosexual" )
            ),
        NA_real_,
          .
        )
      )
    )

# sanity check
pr_pd_by_sex_cc %>%
  filter( is.na( estimate ) )
summary( pr_pd_by_sex_cc )
```

###### 2.2.2.2. Suicidal thoughts
```{r}
pr_pd_by_sex_cc %>% 
  filter( outcome %in% c( "suicidal_thoughts" ),
          estimate_type == "Prevalence Difference" ) %>%
  summary()

pr_pd_by_sex_cc %>% 
  filter( outcome %in% c( "suicidal_thoughts" ),
          estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd_by_sex <- ggplot(
  pr_pd_by_sex_cc %>%
    filter( outcome %in% c( "suicidal_thoughts" ) ),
  
  aes( x = year, y = estimate, color = exposure_model, group = exposure_model ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = 0.1 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.05, 0.03 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  labs( x = "Survey Year",
        y = "Suicidal Thoughts (95% CI)",
        color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ sex,
              switch = "y",
              scales = "free_y" ) +
  
  ggh4x::facetted_pos_scales( y = list(
    estimate_type == "Prevalence Ratio" ~ scale_y_continuous( limits = c( 0, 5.1 ), 
                                                              breaks = c( seq( 0, 5, 1 ) ), 
                                                              expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    estimate_type == "Prevalence Difference" ~ scale_y_continuous( limits = c( -0.2, 0.6 ), 
                                                                   breaks = c( seq( -0.2, 0.6, 0.1 ) ), 
                                                                   labels = scales::percent_format( accuracy = 1 ), 
                                                                   expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd_by_sex
ggsave( "results_output/plots_cc/p_pr_pd_suicidal_thoughts_by_sex_cc.svg", plot = p_pr_pd_by_sex, width = 9, height = 7.5 )
```

###### 2.2.2.3. Suicide attempts
```{r}
pr_pd_by_sex_cc %>% 
  filter( outcome %in% c( "suicide_attempts" ),
          estimate_type == "Prevalence Difference" ) %>%
  summary()

pr_pd_by_sex_cc %>% 
  filter( outcome %in% c( "suicide_attempts" ),
          estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd_by_sex <- ggplot(
  pr_pd_by_sex_cc %>%
    filter( outcome %in% c( "suicide_attempts" ) ),
  aes( x = year, y = estimate, color = exposure_model, group = exposure_model ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = 0.1 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.05, 0.03 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  labs( x = "Survey Year",
        y = "Suicide Attempts (95% CI)",
        color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ sex,
              switch = "y",
              scales = "free_y" ) +
  
  ggh4x::facetted_pos_scales( y = list(
    estimate_type == "Prevalence Ratio" ~ scale_y_continuous( limits = c( 0, 20 ), 
                                                              breaks = c( seq( 0, 20, 5 ) ), 
                                                              expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    estimate_type == "Prevalence Difference" ~ scale_y_continuous( limits = c( -0.2, 0.4 ), 
                                                                   breaks = c( seq( -0.2, 0.4, 0.1 ) ), 
                                                                   labels = scales::percent_format( accuracy = 1 ), 
                                                                   expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd_by_sex
ggsave( "results_output/plots_cc/p_pr_pd_suicide_attempts_by_sex_cc.svg", plot = p_pr_pd_by_sex, width = 9, height = 7.5 )
```

###### 2.2.2.4. Psychological distress
```{r}
pr_pd_by_sex_cc %>% 
  filter( outcome %in% c( "psychological_distress" ),
          estimate_type == "Prevalence Difference" ) %>%
  summary()

pr_pd_by_sex_cc %>% 
  filter( outcome %in% c( "psychological_distress" ),
          estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd_by_sex <- ggplot(
  pr_pd_by_sex_cc %>%
    filter( outcome %in% c( "psychological_distress" ) ),
  
  aes( x = year, y = estimate, color = exposure_model, group = exposure_model ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = 0.1 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.05, 0.03 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 2 ) ) +
  
  labs( x = "Survey Year",
        y = "Psychological Distress (95% CI)",
        color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ sex,
              switch = "y",
              scales = "free_y" ) +
  
  ggh4x::facetted_pos_scales( y = list(
    estimate_type == "Prevalence Ratio" ~ scale_y_continuous( limits = c( 0, 4 ), 
                                                              breaks = c( seq( 0, 4, 1 ) ), 
                                                              expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    estimate_type == "Prevalence Difference" ~ scale_y_continuous( limits = c( -0.3, 0.5 ), 
                                                                   breaks = c( seq( -0.3, 0.5, 0.1 ) ), 
                                                                   labels = scales::percent_format( accuracy = 1 ), 
                                                                   expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd_by_sex
ggsave( "results_output/plots_cc/p_pr_pd_psychological_distress_by_sex_cc.svg", plot = p_pr_pd_by_sex, width = 9, height = 7.5 )
```

### 3. Series of Cross-Sectional Analysis
#### 3.1. Prevalence
##### 3.1.1. By sexual identity
###### 3.1.1.1. Prepare data
```{r}

prevalence_poo_cs_cc <- read_xlsx( here( "results_output/results_cc/prevalence_poo_cs_cc.xlsx" ) ) %>%
  rename( sexual_identity = sexual_identity_baseline ) %>%
  mutate( sample_type = "pooled",
          year = as.character( year ),
          outcome = recode( outcome,
                            antidepressant_use = "antidepressant",
                            anxiolytic_use = "anxiolytic" 
                            ) 
          )

summary( prevalence_poo_cs_cc )

# by sexual identity
prevalence_poo_cs_cc <- read_xlsx( here( "results_output/results_cc/prevalence_poo_cs_cc.xlsx" ) ) %>%
  rename( 
    sexual_identity = sexual_identity_baseline 
    ) %>%
  
  mutate( 
    sexual_identity = factor( 
      sexual_identity,
      levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other" ) ),
    
    outcome = factor( 
      outcome,
      levels = c( "depression", "antidepressant_use", "anxiety", "anxiolytic_use", "stress_related" ) ) 
    ) %>%
  
  filter( sexual_identity != "Other" )

prevalence_poo_cs_cc <- prevalence_poo_cs_cc %>%
  mutate(
    segment = case_when(
      outcome %in% c( "depression", "anxiety", "stress_related" ) & year <= 2002 ~ "incomplete_1",
      outcome %in% c( "depression", "anxiety", "stress_related" ) & year >= 2020 ~ "incomplete_2",
      outcome %in% c( "antidepressant_use", "anxiolytic_use" ) & year == 2005 ~ "incomplete_3",
      TRUE ~ "complete"
    )
  )

summary( prevalence_poo_cs_cc )
```

###### 3.1.1.2. Register-based
```{r}
prevalence_poo_cs_cc %>%
  filter( outcome %in% c( "depression" ) ) %>%
  summary()

prevalence_poo_cs_cc %>%
  filter( outcome %in% c( "antidepressant_use" ) ) %>%
  summary()

prevalence_poo_cs_cc %>%
  filter( outcome %in% c( "anxiety" ) ) %>%
  summary()

prevalence_poo_cs_cc %>%
  filter( outcome %in% c( "anxiolytic_use" ) ) %>%
  summary()

prevalence_poo_cs_cc %>%
  filter( outcome %in% c( "stress_related" ) ) %>%
  summary()

p_prevalence <- ggplot( 
  prevalence_poo_cs_cc,
  aes( x = year, y = point_estimate, color = sexual_identity, linetype = segment, group = interaction( sexual_identity, segment ) ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  scale_linetype_manual( 
    values = c( 
      "complete" = "solid",
      "incomplete_1" = "solid",
      "incomplete_2" = "solid",
      "incomplete_3" = "solid" ),
    guide = "none" ) +
  
  labs(
    x = NULL,
    y = "Prevalence",
    color = NULL,
    linetype = NULL ) +
  
  facet_wrap( ~ outcome, 
              ncol = 2,
              axes = "all",
              scales = "free",
              labeller = labeller(
                outcome = c(
                  "depression" = "Depression",
                  "antidepressant_use" = "Antidepressant Use",
                  "anxiety" = "Anxiety Disorders",
                  "anxiolytic_use" = "Anxiolytic Use",
                  "stress_related" = "Stress-Related Disorders" ) ) ) +
  
  ggh4x::facetted_pos_scales( 
    x = list(
      outcome %in% c( "depression", "anxiety", "stress_related" ) ~
        scale_x_continuous( breaks = seq( 2001, 2021, 2 ),
                            limits = c( 2001, 2021 ),
                            expand = expansion( mult = c( 0.05, 0.02 ) ) ),
      
      outcome %in% c( "antidepressant_use", "anxiolytic_use" ) ~
        scale_x_continuous( breaks = seq( 2005, 2021, 2 ),
                            limits = c( 2005, 2021 ),
                            expand = expansion( mult = c( 0.05, 0.02 ) ) ) ),
    
    y = list(
      outcome == "depression" ~ 
        scale_y_continuous( limits = c( 0, 0.25 ),
                            breaks = c( seq( 0, 0.25, 0.05 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
    
      outcome == "antidepressant_use" ~ 
        scale_y_continuous( limits = c( 0, 0.25 ),
                            breaks = c( seq( 0, 0.25, 0.05 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
    
      outcome == "anxiety" ~ 
        scale_y_continuous( limits = c( 0, 0.15 ),
                            breaks = c( seq( 0, 0.15, 0.05 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
    
      outcome == "anxiolytic_use" ~ 
        scale_y_continuous( limits = c( 0, 0.15 ),
                            breaks = c( seq( 0, 0.15, 0.05 ) ),
                            labels = scales::percent_format( accuracy = 1 ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ),
    
      outcome == "stress_related" ~ 
        scale_y_continuous( limits = c( 0, 0.05 ),
                            breaks = c( seq( 0, 0.05, 0.025 ) ),
                            labels = c( "0%", "2.5%", "5%" ),
                            expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_cc/p_prevalence_poo_cs_cc.svg", plot = p_prevalence, width = 14, height = 9 )
```

##### 3.1.2. By sex
###### 3.1.2.1. Prepare data
```{r}
prevalence_poo_cs_by_sex_cc <- read_xlsx( here( "results_output/results_cc/prevalence_poo_cs_by_sex_cc.xlsx" ) ) %>%
  rename( 
    sexual_identity = sexual_identity_baseline 
    ) %>%
  
  mutate( 
    sexual_identity = factor( 
      sexual_identity,
      levels = c( "Heterosexual", "Homosexual", "Bisexual", "Other" ) ),
    
    outcome = factor( 
      outcome,
      levels = c( "depression", "antidepressant_use", "anxiety", "anxiolytic_use", "stress_related" ) ) 
    ) %>%
  
  filter( sexual_identity != "Other" )

prevalence_poo_cs_by_sex_cc <- prevalence_poo_cs_by_sex_cc %>%
  mutate(
    segment = case_when(
      outcome %in% c( "depression", "anxiety", "stress_related" ) & year <= 2002 ~ "incomplete_1",
      outcome %in% c( "depression", "anxiety", "stress_related" ) & year >= 2020 ~ "incomplete_2",
      outcome %in% c( "antidepressant_use", "anxiolytic_use" ) & year == 2005 ~ "incomplete_3",
      TRUE ~ "complete" )
    )

summary( prevalence_poo_cs_by_sex_cc )
```

###### 3.1.2.2. Depression
```{r}
prevalence_poo_cs_by_sex_cc %>%
  filter( outcome %in% c( "depression" ) ) %>%
  summary()

p_prevalence <- ggplot( 
  prevalence_poo_cs_by_sex_cc %>%
    filter( outcome == "depression" ),
  
  aes( x = year, y = point_estimate, color = sexual_identity, linetype = segment, group = interaction( sexual_identity, segment ) ) ) +
  
  geom_line( linewidth = 0.8 ) +
  geom_point( size = 1.2 ) +
  
  scale_x_continuous( breaks = seq( 2001, 2021, 2 ),
                      limits = c( 2001, 2021 ),
                      expand = expansion( mult = c( 0.05, 0.02 ) ) ) +
  
  scale_y_continuous( limits = c( 0, 0.15 ),
                      breaks = c( seq( 0, 0.15, 0.05 ) ),
                      labels = scales::percent_format( accuracy = 1 ),
                      expand = expansion( mult = c( 0.05, 0 ) ) ) +
  
  scale_color_manual( 
    values = c(
      "Heterosexual" = "#F8766D",
      "Homosexual"   = "#00BFC4",
      "Bisexual"     = "#C77CFF" ) ) +
  
  scale_linetype_manual( 
    values = c( 
      "complete" = "solid",
      "incomplete_1" = "solid",
      "incomplete_2" = "solid",
      "incomplete_3" = "solid" ),
    guide = "none" ) +
  
  labs(
    x = NULL,
    y = "Prevalence of Depression",
    color = NULL,
    linetype = NULL ) +
  
  facet_wrap( ~ sex ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 2, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' ) 

p_prevalence
ggsave( "results_output/plots_cc/p_prevalence_poo_cs_depression_by_sex_cc.svg", plot = p_prevalence, width = 12, height = 6 )
```

#### 3.2. Prevalence ratio and difference
##### 3.2.1. By sexual identity
###### 3.2.1.1. Prepare data
```{r}
pr_poo_cs_cc <- read_xlsx( here( 'results_output/results_cc/pr_poo_cs_cc.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Ratio" )

pd_poo_cs_cc <- read_xlsx( here( 'results_output/results_cc/pd_poo_cs_cc.xlsx' ) ) %>%
  mutate( estimate_type = "Prevalence Difference" )

pr_pd_poo_cs_cc <- bind_rows( pr_poo_cs_cc, pd_poo_cs_cc ) %>%
  filter( exposure_level != "Other" ) %>%
  mutate( outcome = as.factor( outcome ),
          year = as.factor( year ),
          exposure_level = as.factor( exposure_level ),
          model_type = recode_factor( model_type, "crude" = "Crude", "adjusted" = "Adjusted" ),
          estimate_type = factor( estimate_type, levels = c( "Prevalence Ratio", "Prevalence Difference" ) ),
          exposure_model = interaction( exposure_level, model_type, sep = "_" ),
          exposure_model = factor( exposure_model, levels = c(
            "Bisexual_Crude",
            "Homosexual_Crude",
            "Bisexual_Adjusted",
            "Homosexual_Adjusted" ) ) )
summary( pr_pd_poo_cs_cc )
```

###### 3.2.1.2. Register-based
```{r}
pr_pd_cc %>% 
  filter( outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ),
          estimate_type == "Prevalence Difference" ) %>%
  summary()

pr_pd_cc %>% 
  filter( outcome %in% c( "psychological_distress", "suicidal_thoughts", "suicide_attempts" ),
          estimate_type == "Prevalence Ratio" ) %>%
  summary()

p_pr_pd <- ggplot(
  pr_pd_poo_cs_cc,
  
  aes( x = year, y = estimate, color = exposure_model, group = exposure_model ) ) +
  
  geom_errorbar( aes( ymin = lower_ci, ymax = upper_ci ), width = 0.1 ) +
  
  geom_line( linewidth = 0.8 ) + 
  geom_point( size = 1.2 ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Ratio" ),
              aes( yintercept = 1 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  geom_hline( data = data.frame( estimate_type = "Prevalence Difference" ),
              aes( yintercept = 0 ),
              linetype = "dashed",
              color = "grey40" ) +
  
  scale_x_discrete( expand = expansion( mult = c( 0.05, 0.02 ) ) ) +
  
  scale_color_manual( values = c(
    "Bisexual_Adjusted"   = "#C77CFF",
    "Bisexual_Crude"      = lighten( "#C77CFF", 0.4 ),
    "Homosexual_Adjusted" = "#00BFC4",
    "Homosexual_Crude"    = lighten( "#00BFC4", 0.4 ) ),
    
    labels = c(
      "Bisexual_Adjusted"   = "Bisexual (Adjusted)",
      "Bisexual_Crude"      = "Bisexual (Crude)",
      "Homosexual_Adjusted" = "Homosexual (Adjusted)",
      "Homosexual_Crude"    = "Homosexual (Crude)" ),
    
    guide = guide_legend( nrow = 1 ) ) +
  
  labs( x = "Survey Year",
        y = "Estimate (95% CI)",
        color = NULL ) +
  
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text( family = "Arial", size = 11 ),
    panel.spacing = unit( 1.5, "lines" ),
    axis.title = element_text( family = "Arial", size = 11 ),
    axis.text = element_text( family = "Arial", size = 11 ),
    legend.title = element_blank(),
    legend.text = element_text( family = "Arial", size = 10 ),
    legend.position = "bottom" ) +
  
  facet_grid( estimate_type ~ outcome,
              switch = "y",
              scales = "free_y" ) +
  
  ggh4x::facetted_pos_scales( y = list(
    estimate_type == "Prevalence Ratio" ~ scale_y_continuous( limits = c( 0, 8 ), 
                                                              breaks = c( seq( 0, 8, 1 ) ), 
                                                              expand = expansion( mult = c( 0.05, 0 ) ) ),
    
    estimate_type == "Prevalence Difference" ~ scale_y_continuous( limits = c( -0.2, 0.5 ), 
                                                                   breaks = c( seq( -0.2, 0.5, 0.1 ) ), 
                                                                   labels = scales::percent_format( accuracy = 1 ), 
                                                                   expand = expansion( mult = c( 0.05, 0 ) ) ) ) ) +
  
  coord_capped_cart( left = 'both', bottom = 'both' )

p_pr_pd
ggsave( "results_output/plots_cc/p_pr_pd_self_report_cc.svg", plot = p_pr_pd, width = 12, height = 7.5 )
```

